### 2024-10-04 alt_energy_herding.qmd
Initial commit

---
format:
  pdf:
    tbl-cap-location: top
    dpi: 500
    fig-pos: "H"
    number-sections: true
    cite-method: natbib
    include-in-header: 
      - text: |
          \usepackage{lscape}
          \newcommand{\blandscape}{\begin{landscape}}
          \newcommand{\elandscape}{\end{landscape}}
          \usepackage{rotating}
          \newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
          \newcommand{\esideways}{\end{sidewaystable}}
      - file: preamble.tex 
    include-before-body: title.tex
    keep-tex: TRUE
  docx:
    reference-doc: new_template_no_numbering.docx
pdf-engine: lualatex
# monofont: "DejaVu Sans Mono"
# mainfont: "Times New Roman"
execute: 
  echo: false
  warning: false
editor: source
bibliography: references.bib
biblio-style: apalike
natbiboptions: round
link-citations: true
linkcolor: blue!100!black
urlcolor: blue!100!black
citecolor: blue!100!black
linestretch: 1.5
indent: TRUE
title-block-banner: false
title-block-style: none
---

```{r setup}
#| include=FALSE
options(scipen=999)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 500, 
                      fig.pos = "H", 
                      fig.env= 'figure', 
                      tab.topcaption = TRUE,
                      ft.align = "left",
                      ft.arraystretch = 0.5
                      )
library(tidyverse)
library(readr)
library(readxl)
library(zoo)
library(magick)
library(stringi)
library(patchwork)
library(xtable)
library(scales)
library(rvest)
library(rebus)
library(PNWColors)
library(lubridate)
library(here)
library(flextable)
library(gt)
library(officer)
library(officedown)
library(modelsummary)
library(sandwich)
library(lmtest)

set_flextable_defaults(
  font.size = 7,
  digits = 2,
  font.family = "Arial",
  border.color = "black",
  border.width = 0.5,
  fp_border = fp_border(color = "black", width = 0.5, style = "solid")
)

```

```{r functions}
source(here("Functions","flextable_word.R" ))
source(here("Functions","modelsummary_word.R" ))
source(here("Functions","modelplot_word.R" ))
source(here("Functions","borderlines.R" ))
```

# Introduction

Argument: Investment interest on green ETFs has been explosive mainly by climate risks faced by the global economy and the actions of policy makers, goverments and organizations towards a sustainable future.

Derived from @decclesia2024: Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs.
The clean energy transition represents one of the largest multi-decade secular growth opportunities.

From @naqvi2022: After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormousl

# Literature review

# Data and methodology

## Data

The sample consists of alternative energy equity ETFs (green ETFs) that are traded in the US markets. The number of available alternative energy ETFs in our sample varied from 10 in the beginning of analysis to 30 at the most. The period of analysis runs from May 1st of 2016 through 19th June of 2024. The starting date was selected on the basis of the COP Paris agreement.
Daily logarithmic returns were computed from the closing prices of ETFs for a total of 2122 observations.

\newpage

```{r}
#| label: data
#| tbl-cap: "List of used alternative energy equity ETFs"
#| cache: false

tribble(
  ~"ETF", ~"Source",
  "ALPS CLEAN ENERGY ETF", "",
  "BLUE HORIZON BNE ETF", " ",
  "SPDR S&P KENSHO CLEAN POWER ETF", " ",
  "GLOBAL X CLEANTECH ETF", " ",
  "PROSHARES S&P KENSHO CLEANTECH ETF", " ",
  "INVESCO MSCI SUSTAINABLE FUTURE ETF", " ",
  "FIRST TRUST GLOBAL WIND ENERGY ETF", " ",
  "FIDELITY CLEAN ENERGY ETF", " ",
  "GLDS.BLOOMBERG CN. EN. EQ.ETF", " ",
  "FST.NQ.CN.EDGE SMRT.GRID INFRA IDX ETF", " ",
  "DEFIANCE NEXT GEN H2 ETF", " ",
  "DIREXION HYDROGEN ETF", " ",
  "GLOBAL X HYDROGEN ETF", " ",
  "ISHARES GLOBAL CLEAN EN. ETF", " ",
  "BLACKR.WLD.EXUS CRBN TSTN.READINESS", " ",
  "NUB.CBN.TSTN.& INFRA", " ",
  "TCW TRANSFORM SYSTEMS ETF", " ",
  "VANECK URANIUM AND NUCLEAR ENERGY", " ",
  "NUVEEN GLOBAL NET ZERO TRANSITION ETF", " ",
  "SPDR MSCI USA CIM. PA. ALIGNED ETF", " ", 
  "INVESCO GLOBAL CLEAN ENERGY ETF", " ", 
  "FST.NQ.CN.EDGE GREY.ETF", " ",
  "GLOBAL X SOLAR ETF", " ", 
  "GLOBAL X RENEWABLE ENERGY PRODUCERS", " ",
  "TRUESHARES EAG.GLB. RENWEN.ETF", " ",
  "VANECK LOW CARBON ENERGY ETF", " ",
  "SMARTETFS SUST.EN. II ETF", " ",
  "INVESCO SOLAR ETF", " ", 
  "VIRTUS DUFF & PHELPS CLEAN ENERGY ETF", " ",
  "GLOBAL X WIND ENERGY ETF", " "
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1,  part = "all") %>%
  autofit(add_w = 1.5)

```

Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.

## Methodology

Following the relevant literature we calculate the Cross Sectional Absolute Deviation  (CSAD) measure for each day in the following manner. We compute the difference of the ith ETF and market return where market return is proxied by the cross sectional average of returns for sample of our ETFs available for each day using equation (1):

$$
CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|
$$ {#eq-csad}

The behavior of the CSAD measure for US Alternative Energy ETFs is presented in Figue 1.

```{r}
#| label: cross_sectional_deviation
#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
#| fig.height: 4
#| fig.width: 6
#| cache: false

```

At a later stage we estimate a non-linear regression as in @galariotis2015.

$$
CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t
$$ {#eq-herding}

The testing procedure of herding relies on the above Equation (2). Rational asset pricing models predict a linear relationship between return dispersion and market returns under normal conditions, a relationship that is no longer valid in the presence of herding. Herding behavior leads to an increasing or decreasing cross sectional dispersion with respect to market returns. In other words, herding is captured by a non-linear term in the standard pricing equation indicating a decreasing or an increasing returns’ dispersion.

# Results

## General herding behaviour

Stated differently, as @chang2000 argue, in the case of herding the coefficient on the non-linear term (γ2) will be negative and statistically significant.
Table 2 presens the results of herding for the full sample employing the non-linear equation (2). The estimated coefficient on market return is positive and highly significant as expected.The estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behavior is present and robust in the US alternative energy ETFs.

```{r}
#| label: herding
#| tbl-cap: "Estimation results of herding in the U.S. equity alternative energy ETFs"
#| cache: false
#| ft.arraystretch: 0.9

estimates <- c(
  "\\gamma_0",
  "\\gamma_1 ",
  "\\gamma_2"
)

tribble(
  ~ "gamma_0", ~ "gamma_1", ~ "gamma_2",
  "0.0038**", "0.2883***", " -1.2773***",
  "(47.09)", "(33.333)", "(-9.71)"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, part = "header", value = as_paragraph(as_equation(estimates))) %>% 
  autofit(add_w = 0.8)

```

There is ample evidence in the relevant literature that herding behavior in various asset markets [see @pochea2017] exhibits asymmetry and time-varying characteristics. To this end, we proceed to estimate Equation (2) using the quantile regression (QR) proposed by @koenker1978 and Table 3 presents the results of estimating Equation (2) across various quantiles of the returns dispersion. Our focus is on the herding coefficient γ2, as a significant negative value of γ2 is indicative of herding. Such a finding is observed at two quantiles namely 25% and 50% with a value of -1.1056 and -1.165 which are highly significant. It is worth mentioning that the sign of the herding coefficient remains negative for almost all quantiles while the significance changes from significant to insifnificant while we move from low and middle to upper quantiles (75 and 90%).

```{r}
#| label: quantile_herding
#| tbl-cap: "Estimation results of herding across various quantiles"
#| cache: false

headings <- c(
  "\\gamma_0",
  "\\gamma_1 ",
  "\\gamma_2"
)

quantiles <- c(
  "\\tau = 10\\%",
  "\\tau = 25\\%",
  "\\tau = 50\\%",
  "\\tau = 75\\%",
  "\\tau = 90\\%"
)

tribble(
  ~ "Quantile", ~ "gamma_0", ~ "gamma_1", ~ "gamma_2",
  "10%", "0.0016***", "0.2536***", " -1.3736",
  "25%", "0.0026***", "0.2461***", " -1.1056***",
  "50%", "0.0037***", "0.2648***", " -1.165***",
  "75%", "0.0048***", "0.3011***", " -1.1473***",
  "90%", "0.0064***", "0.2999***", " 0.2314"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, j = c(2, 3, 4), part = "header", value = as_paragraph(as_equation(headings))) %>% 
  mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
  autofit(add_w = 0.2)

```

## Herding behaviour during extreme market periods

It is widely accepted that asset returns are characterized by asymmetry, that is, return dispersion tend to behave differently in rising and falling markets [see @geert2000; @zhou2013; @longin2001]. Based on the above and in order to provide additional insight on the herding phenomenon we examine whether herding presents an asymmetric response on days when the market is up vis-à-vis days when the market is down. To this end, we augment Eq. 2 as follows:

$$
CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
$$
where D is a dummy variable that takes the value of 1 when the market return is negative and 0 otherwise.

Therefore, our exploration of asymmetric behavior of herding phenomenon is carried through the inspection of the statistical significance and the sign of the two estimated coefficients γ3 vs γ4 (up vs down markets). It should be noted, that examining the relationship between returns dispersion and market-wide returns across various quantiles of the returns distribution allows us to make more robust inference regarding the true behavior of the phenomenon.

Table 4 reports the estimation results of herding in the up and down markets
based on Eq. 3. In general, we find that herding is more likely to occur in down markets than in up markets, which is indicative of the asymmetry of herding behavior.

```{r}
#| label: asymmetry_herding
#| tbl-cap: "Estimation results of herding in up and down markets"
#| cache: false

headings <- c(
  "\\gamma_0",
  "\\gamma_1 ",
  "\\gamma_2",
  "\\gamma_3",
  "\\gamma_4"
)

quantiles <- c(
  "\\tau = 10\\%",
  "\\tau = 25\\%",
  "\\tau = 50\\%",
  "\\tau = 75\\%",
  "\\tau = 90\\%"
)

tribble(
  ~ "Quantile", ~ "gamma_0", ~ "gamma_1", ~ "gamma_2", ~ "gamma_3", ~ "gamma_4",
  "10%", "0.0016***", "0.2532***", " -1.3669***", " -0.2522***", " -1.1522",
  "25%", "0.0026***", "0.2475***", " -1.2383**", " -0.2477***", " -1.1171***",
  "50%", "0.0038***", "0.2247***", " 0.3838", " -0.2634***", " -1.3144***",
  "75%", "0.0050***", "0.2500***", " 1.3135", " -0.2785***", " -0.9721***",
  "90%", "0.0065***", "0.2788***", " 1.0169", " -0.2942***", " -1.2003***"
) %>% 
  flextable_pdf() %>% 
  mk_par(i = 1, j = c(2, 3, 4, 5, 6), part = "header", value = as_paragraph(as_equation(headings))) %>% 
  mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
  autofit(add_w = -0.2)

```

Herding is present at low quantiles when markets are rising with an estimated coefficient γ3 of -1.3669 and -1.2383 and highly significant respectively. However, when markets are declining, investors seem to neglect their own information set and imitate the actions of others resulting in a highly significant coefficient of herding ( γ4) across four out of five quantiles. Furthermore, we find that in high quantiles (75% & 90%) and when markets are rising the coefficient of interest ( γ3) turns positive but insignificant.

## Rolling window analysis

There is ample evidence that herding might be time dependent [see @babalos2015; @klein2013; @stavroyiannis2019]. In order to gain further insight on the time varying nature of herding we conducted a rolling window analysis. The size of the rolling window is related to the timescales of the system (response times), and the aim of the research [@babalos2015]. There is no golden rule for the right size of the rolling window, there is a trade-off between having a long enough window to estimate the metrics, and short enough to have a sufficient number of windows in order to be able to derive a trend. In light of the above discussion we set off to conduct a rolling window analysis of 50 observations.
Figure 2 plots the time evolution of the value of the estimated significance of the herding coefficient  (γ2) using the rolling window analysis.

We observe several periods of herding behavior as reflected in the troughs in Figure 2. The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 and the period of February-March of 2023. On the other side, we derive significant moments of anti-herding behavior in the clean energy ETFs by observing the spikes in Figure 2. Cross sectional dispersion appears to increase with respect to market-wide returns which is a sign of anti-herding behavior on behalf of investors around December of 2016 and later during September of 2022.

```{r}
#| label: rolling_window
#| fig.cap: "Estimated significance of herding coefficient in a rolling window analysis"
#| cache: false

```

## Probit analysis

The behavior of participants in energy markets is closely related to the developments in the field of climate risks, carbon emmissions  and environmentally friendly policies. There are a few studies that attempt to quantify the effects of unceretainty related to climate on the economy and financial markets (see inter alia….). @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.  It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets. Therefore, in the context of our study and following previous studies that study the determinants of herding behavior [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market. Given this, we define a dummy variable, which takes a value of 1 during periods of statistically significant herding (i.e., for days when the rolling t-statistic on γ2 < −1.96) and zero otherwise, and then, we use a Probit model to relate this dummy to the two climate risk indexes developed by @bua2024. It should be noted that due to availability issues the probit analysis ends in December of 2023. The results from the Probit model are reported in Table 2, where only the physical risk index significantly decreases the probability of herding. In other words, climate risks is good news for clean energy stocks or firms resulting in anti herding behavior.

This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products. As a result, the cross sectional dispersion of clean energy ETFs tends to increase.

```{r}
#| label: probit_analysis
#| tbl-cap: "Estimation results of the probit model"
#| cache: false

tribble(
  ~ "Variable", ~ "Coefficient",
  "Transition Risk", "-4.607***",
  "Physical Risk", "-1.318", 
  "Constant", " -1.506***",
  "LogL", "-484.7",
  "Observations with Dependent Variable (Dep) = 0", "1816",
  "Observations with Dependent Variable (Dep) = 1", "134"
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  autofit(add_w = 1.5)

```

Furthermore, suppose we get the median values of these two series. then we define values above median as high and below median as low.

We define a dummy =1 if values>median and 0 otherwise and in this way we will have PRI values that are bigger than median and 0 otherwise. We also define a dummy which is lower than median, i.e., 1 and 0 otherwise, then we use these high PRI and high TRI in one probit regression and low TRI and low PRI in another. Results are presented in the following table.

We observe higher uncertainty that stems from physical or transition risk causes antiherding which is in line with the logic we discussed earlier.

\newpage
```{r}
#| label: probit_analysis2
#| tbl-cap: "Estimation results of the probit model with high and low climate risk indexes (above or below median)"
#| cache: false

tribble(
  ~" ", ~ "High", ~ "Low",
  "Physical Risk", "-6.736*", "-6.118",
  "Transition Risk", "-1.798", "-2.581",
) %>% 
  flextable_pdf() %>% 
  align(align = "left", j = 1, part = "all") %>%
  autofit(add_w = 1.5)

```

# Conclusion

This study offers novel and valuable insights on herding behavior in clean energy ETFs.

\newpage 
# References {.unnumbered}
::: {#refs}
:::

<!-- \setcounter{section}{0} -->
<!-- \renewcommand{\thesection}{\Alph{section}} -->

<!-- \setcounter{table}{0} -->
<!-- \renewcommand{\thetable}{A\arabic{table}} -->

<!-- \setcounter{figure}{0} -->
<!-- \renewcommand{\thefigure}{A\arabic{figure}} -->

<!-- \newpage -->

<!-- # Appendix -->

<!-- ## Data -->

### 2024-10-04 alt_energy_herding.tex
Initial commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
% \usepackage{hyperref}
% \hypersetup{
%     colorlinks,
%     linkcolor={blue!100!black},
%     citecolor={blue!100!black},
%     urlcolor={blue!100!black}
% }
% \usepackage{apacite}
% \usepackage[round]{natbib} 
% \usepackage{graphicx}
% \usepackage{float}
% \usepackage{caption}
% \usepackage[toc,page]{appendix}
% \usepackage{booktabs,caption}
% \usepackage[flushleft]{threeparttable}
% \usepackage{tabularx}
\usepackage{sfmath}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{amsmath}
% \usepackage{xcolor}
% \usepackage{scrextend}
% \deffootnote[2em]{2em}{1em}{\textsuperscript{\thefootnotemark}\,}
% \newcolumntype{Y}{>{\centering\arraybackslash}X}
% \usepackage[a4paper]{geometry}
% \usepackage{caption}
% \usepackage[bottom,flushmargin,hang,multiple]{footmisc}
% \usepackage{pdflscape}
% \usepackage[paper=portrait,pagesize]{typearea}
% \usepackage{rotating}
% \usepackage{fullpage}
% \usepackage{tabu}
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{rotating}
\newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
\newcommand{\esideways}{\end{sidewaystable}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[round]{natbib}
\bibliographystyle{apalike}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={blue!100!black},
  filecolor={Maroon},
  citecolor={blue!100!black},
  urlcolor={blue!100!black},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\title{Do investors in clean energy ETFs herd?}

\author { 
Vassilios Babalos\footnote{Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
Xolani Sibande\footnote{Corresponding Author. Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com. Economic Research Department, South African Reserve Bank, Pretoria, South Africa.} \,\, 
Riza Demirer\footnote{Department of Economics and Finance, Southern Illinois University Edwardsville, Edwardsville, IL 62026-1102, USA; Email: rdemire@siue.edu} \,\,
Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.}
}
\date{\today}
\maketitle

\begin{abstract}

ipsum

\end{abstract}

\noindent\textbf{Keywords}: Herding Behaviour, Financial Crises, Market Efficiency
\\
\textbf{JEL Codes}: G01, G14, G15, G41
\newpage

\setstretch{1.5}
\section{Introduction}\label{introduction}

Argument: Investment interest on green ETFs has been explosive mainly by
climate risks faced by the global economy and the actions of policy
makers, goverments and organizations towards a sustainable future.

Derived from \citet{decclesia2024}: Among the ESG ETFs, the Clean Energy
(CE) ETFs have been the best-performing ones in 2022, followed by the
Cybersecurity and Artificial Intelligence (AI) ETFs. The clean energy
transition represents one of the largest multi-decade secular growth
opportunities.

From \citet{naqvi2022}: After the inclusion of Green energy financing in
the list of United Nations Sustainability Goals (SDGs) as SDG 7, the
role, importance, and visibility of green financial products; all have
escalated enormousl

\section{Literature review}\label{literature-review}

\section{Data and methodology}\label{data-and-methodology}

\subsection{Data}\label{data}

The sample consists of alternative energy equity ETFs (green ETFs) that
are traded in the US markets. The number of available alternative energy
ETFs in our sample varied from 10 in the beginning of analysis to 30 at
the most. The period of analysis runs from May 1st of 2016 through 19th
June of 2024. The starting date was selected on the basis of the COP
Paris agreement. Daily logarithmic returns were computed from the
closing prices of ETFs for a total of 2122 observations.

\newpage

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{3.89in}|p{1.99in}}
\caption{List of used alternative energy equity ETFs}\tabularnewline

\ascline{1pt}{000000}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Source}}}} \\

\ascline{1pt}{000000}{1-2}\endfirsthead

\ascline{1pt}{000000}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Source}}}} \\

\ascline{1pt}{000000}{1-2}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ALPS\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{}}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLUE\ HORIZON\ BNE\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ S\&P\ KENSHO\ CLEAN\ POWER\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ CLEANTECH\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{PROSHARES\ S\&P\ KENSHO\ CLEANTECH\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ MSCI\ SUSTAINABLE\ FUTURE\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIRST\ TRUST\ GLOBAL\ WIND\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIDELITY\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLDS.BLOOMBERG\ CN.\ EN.\ EQ.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ SMRT.GRID\ INFRA\ IDX\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DEFIANCE\ NEXT\ GEN\ H2\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DIREXION\ HYDROGEN\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ HYDROGEN\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ISHARES\ GLOBAL\ CLEAN\ EN.\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLACKR.WLD.EXUS\ CRBN\ TSTN.READINESS}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUB.CBN.TSTN.\&\ INFRA}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TCW\ TRANSFORM\ SYSTEMS\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ URANIUM\ AND\ NUCLEAR\ ENERGY}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUVEEN\ GLOBAL\ NET\ ZERO\ TRANSITION\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ MSCI\ USA\ CIM.\ PA.\ ALIGNED\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ GLOBAL\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ GREY.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ SOLAR\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ RENEWABLE\ ENERGY\ PRODUCERS}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TRUESHARES\ EAG.GLB.\ RENWEN.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ LOW\ CARBON\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SMARTETFS\ SUST.EN.\ II\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ SOLAR\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VIRTUS\ DUFF\ \&\ PHELPS\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ WIND\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\

\ascline{1pt}{000000}{1-2}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

Results of baseline and rolling window analysis points to significant
herding for the whole period and in various instances.

\subsection{Methodology}\label{methodology}

Following the relevant literature we calculate the Cross Sectional
Absolute Deviation (CSAD) measure for each day in the following manner.
We compute the difference of the ith ETF and market return where market
return is proxied by the cross sectional average of returns for sample
of our ETFs available for each day using equation (1):

\begin{equation}\phantomsection\label{eq-csad}{
CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|
}\end{equation}

The behavior of the CSAD measure for US Alternative Energy ETFs is
presented in Figue 1.

At a later stage we estimate a non-linear regression as in
\citet{galariotis2015}.

\begin{equation}\phantomsection\label{eq-herding}{
CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t
}\end{equation}

The testing procedure of herding relies on the above Equation (2).
Rational asset pricing models predict a linear relationship between
return dispersion and market returns under normal conditions, a
relationship that is no longer valid in the presence of herding. Herding
behavior leads to an increasing or decreasing cross sectional dispersion
with respect to market returns. In other words, herding is captured by a
non-linear term in the standard pricing equation indicating a decreasing
or an increasing returns' dispersion.

\section{Results}\label{results}

\subsection{General herding behaviour}\label{general-herding-behaviour}

Stated differently, as \citet{chang2000} argue, in the case of herding
the coefficient on the non-linear term (γ2) will be negative and
statistically significant. Table 2 presens the results of herding for
the full sample employing the non-linear equation (2). The estimated
coefficient on market return is positive and highly significant as
expected.The estimated coefficient on the non-linear term is negative
(-1.2773) and statistically significant with a t-statistic of -9.71
suggesting that herd behavior is present and robust in the US
alternative energy ETFs.

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.9}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{1.99in}|p{1.99in}|p{1.99in}}
\caption{Estimation results of herding in the U.S. equity alternative energy ETFs}\tabularnewline

\ascline{1pt}{000000}{1-3}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\

\ascline{1pt}{000000}{1-3}\endfirsthead

\ascline{1pt}{000000}{1-3}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\

\ascline{1pt}{000000}{1-3}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2883***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2773***}}}} \\

\ascline{1pt}{FFFFFF}{1-3}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(47.09)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(33.333)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(-9.71)}}}} \\

\ascline{1pt}{000000}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

There is ample evidence in the relevant literature that herding behavior
in various asset markets \citep[see][]{pochea2017} exhibits asymmetry
and time-varying characteristics. To this end, we proceed to estimate
Equation (2) using the quantile regression (QR) proposed by
\citet{koenker1978} and Table 3 presents the results of estimating
Equation (2) across various quantiles of the returns dispersion. Our
focus is on the herding coefficient γ2, as a significant negative value
of γ2 is indicative of herding. Such a finding is observed at two
quantiles namely 25\% and 50\% with a value of -1.1056 and -1.165 which
are highly significant. It is worth mentioning that the sign of the
herding coefficient remains negative for almost all quantiles while the
significance changes from significant to insifnificant while we move
from low and middle to upper quantiles (75 and 90\%).

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{1.39in}|p{1.39in}|p{1.39in}|p{1.39in}}
\caption{Estimation results of herding across various quantiles}\tabularnewline

\ascline{1pt}{000000}{1-4}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\

\ascline{1pt}{000000}{1-4}\endfirsthead

\ascline{1pt}{000000}{1-4}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\

\ascline{1pt}{000000}{1-4}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2536***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3736}}}} \\

\ascline{1pt}{FFFFFF}{1-4}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2461***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1056***}}}} \\

\ascline{1pt}{FFFFFF}{1-4}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0037***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2648***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.165***}}}} \\

\ascline{1pt}{FFFFFF}{1-4}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0048***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.3011***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1473***}}}} \\

\ascline{1pt}{FFFFFF}{1-4}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0064***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2999***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.2314}}}} \\

\ascline{1pt}{000000}{1-4}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\subsection{Herding behaviour during extreme market
periods}\label{herding-behaviour-during-extreme-market-periods}

It is widely accepted that asset returns are characterized by asymmetry,
that is, return dispersion tend to behave differently in rising and
falling markets \citep[see][]{geert2000, zhou2013, longin2001}. Based on
the above and in order to provide additional insight on the herding
phenomenon we examine whether herding presents an asymmetric response on
days when the market is up vis-à-vis days when the market is down. To
this end, we augment Eq. 2 as follows:

\[
CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
\] where D is a dummy variable that takes the value of 1 when the market
return is negative and 0 otherwise.

Therefore, our exploration of asymmetric behavior of herding phenomenon
is carried through the inspection of the statistical significance and
the sign of the two estimated coefficients γ3 vs γ4 (up vs down
markets). It should be noted, that examining the relationship between
returns dispersion and market-wide returns across various quantiles of
the returns distribution allows us to make more robust inference
regarding the true behavior of the phenomenon.

Table 4 reports the estimation results of herding in the up and down
markets based on Eq. 3. In general, we find that herding is more likely
to occur in down markets than in up markets, which is indicative of the
asymmetry of herding behavior.

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}}
\caption{Estimation results of herding in up and down markets}\tabularnewline

\ascline{1pt}{000000}{1-6}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\

\ascline{1pt}{000000}{1-6}\endfirsthead

\ascline{1pt}{000000}{1-6}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\

\ascline{1pt}{000000}{1-6}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2532***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3669***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2522***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1522}}}} \\

\ascline{1pt}{FFFFFF}{1-6}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2475***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2383**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2477***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1171***}}}} \\

\ascline{1pt}{FFFFFF}{1-6}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2247***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.3838}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2634***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3144***}}}} \\

\ascline{1pt}{FFFFFF}{1-6}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0050***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2500***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.3135}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2785***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.9721***}}}} \\

\ascline{1pt}{FFFFFF}{1-6}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0065***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2788***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.0169}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2942***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2003***}}}} \\

\ascline{1pt}{000000}{1-6}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

Herding is present at low quantiles when markets are rising with an
estimated coefficient γ3 of -1.3669 and -1.2383 and highly significant
respectively. However, when markets are declining, investors seem to
neglect their own information set and imitate the actions of others
resulting in a highly significant coefficient of herding ( γ4) across
four out of five quantiles. Furthermore, we find that in high quantiles
(75\% \& 90\%) and when markets are rising the coefficient of interest (
γ3) turns positive but insignificant.

\subsection{Rolling window analysis}\label{rolling-window-analysis}

There is ample evidence that herding might be time dependent
\citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In order to
gain further insight on the time varying nature of herding we conducted
a rolling window analysis. The size of the rolling window is related to
the timescales of the system (response times), and the aim of the
research \citep{babalos2015}. There is no golden rule for the right size
of the rolling window, there is a trade-off between having a long enough
window to estimate the metrics, and short enough to have a sufficient
number of windows in order to be able to derive a trend. In light of the
above discussion we set off to conduct a rolling window analysis of 50
observations. Figure 2 plots the time evolution of the value of the
estimated significance of the herding coefficient (γ2) using the rolling
window analysis.

We observe several periods of herding behavior as reflected in the
troughs in Figure 2. The most prominent cases of herding occur between
March and May of 2020 followed by several instances of herding in the
period that extends from March through April of 2017 and the period of
February-March of 2023. On the other side, we derive significant moments
of anti-herding behavior in the clean energy ETFs by observing the
spikes in Figure 2. Cross sectional dispersion appears to increase with
respect to market-wide returns which is a sign of anti-herding behavior
on behalf of investors around December of 2016 and later during
September of 2022.

\subsection{Probit analysis}\label{probit-analysis}

The behavior of participants in energy markets is closely related to the
developments in the field of climate risks, carbon emmissions and
environmentally friendly policies. There are a few studies that attempt
to quantify the effects of unceretainty related to climate on the
economy and financial markets (see inter alia\ldots.). \citet{bua2024}
developed two climate risk related indexes namely transition and
physical risk using a text-based approach in order to study the effect
of these risks in financial markets. It is expected that investors would
prefer to hold assets that perform well in the face of increasing
climate change risks, even if this entails accepting lower returns for
such climate-hedging assets. Therefore, in the context of our study and
following previous studies that study the determinants of herding
behavior \citep[see][]{bouri2019, demirer2018}, we attempt to study the
effect of climate-related uncertainty on the formation of herding
behavior in the clean energy market. Given this, we define a dummy
variable, which takes a value of 1 during periods of statistically
significant herding (i.e., for days when the rolling t-statistic on γ2
\textless{} −1.96) and zero otherwise, and then, we use a Probit model
to relate this dummy to the two climate risk indexes developed by
\citet{bua2024}. It should be noted that due to availability issues the
probit analysis ends in December of 2023. The results from the Probit
model are reported in Table 2, where only the physical risk index
significantly decreases the probability of herding. In other words,
climate risks is good news for clean energy stocks or firms resulting in
anti herding behavior.

This implies that in the presence of higher physical risk with respect
to the climate, clean energy ETFs become a more attractive investment
option for investors that allocate their money to the various
alternative energy investment products. As a result, the cross sectional
dispersion of clean energy ETFs tends to increase.

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{3.78in}|p{2.14in}}
\caption{Estimation results of the probit model}\tabularnewline

\ascline{1pt}{000000}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\

\ascline{1pt}{000000}{1-2}\endfirsthead

\ascline{1pt}{000000}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\

\ascline{1pt}{000000}{1-2}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Constant}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{LogL}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\

\ascline{1pt}{FFFFFF}{1-2}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\

\ascline{1pt}{000000}{1-2}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

Furthermore, suppose we get the median values of these two series. then
we define values above median as high and below median as low.

We define a dummy =1 if values\textgreater median and 0 otherwise and in
this way we will have PRI values that are bigger than median and 0
otherwise. We also define a dummy which is lower than median, i.e., 1
and 0 otherwise, then we use these high PRI and high TRI in one probit
regression and low TRI and low PRI in another. Results are presented in
the following table.

We observe higher uncertainty that stems from physical or transition
risk causes antiherding which is in line with the logic we discussed
earlier.

\newpage

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{0.5}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[l]{|p{2.33in}|p{2.00in}|p{1.96in}}
\caption{Estimation results of the probit model with high and low climate risk
indexes (above or below median)}\tabularnewline

\ascline{1pt}{000000}{1-3}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\

\ascline{1pt}{000000}{1-3}\endfirsthead

\ascline{1pt}{000000}{1-3}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\

\ascline{1pt}{000000}{1-3}\endhead

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\

\ascline{1pt}{FFFFFF}{1-3}

\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\

\ascline{1pt}{000000}{1-3}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\section{Conclusion}\label{conclusion}

This study offers novel and valuable insights on herding behavior in
clean energy ETFs.

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\renewcommand{\bibsection}{}
\bibliography{references.bib}

\end{document}

### 2024-10-04 title.tex
Initial commit

--- 2024-10-04 alt_energy_herding.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
-%
-\documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
-
-\usepackage{amsmath,amssymb}
-\usepackage{setspace}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else  
-    % xetex/luatex font selection
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\usepackage{fontspec}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\newlength\Oldarrayrulewidth
-\newlength\Oldtabcolsep
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage{wrapfig}
-% \usepackage{hyperref}
-% \hypersetup{
-%     colorlinks,
-%     linkcolor={blue!100!black},
-%     citecolor={blue!100!black},
-%     urlcolor={blue!100!black}
-% }
-% \usepackage{apacite}
-% \usepackage[round]{natbib} 
-% \usepackage{graphicx}
-% \usepackage{float}
-% \usepackage{caption}
-% \usepackage[toc,page]{appendix}
-% \usepackage{booktabs,caption}
-% \usepackage[flushleft]{threeparttable}
-% \usepackage{tabularx}
-\usepackage{sfmath}
-\usepackage{fontspec}
-\usepackage[utf8]{inputenc}
-\usepackage{siunitx}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-% \usepackage{xcolor}
-% \usepackage{scrextend}
-% \deffootnote[2em]{2em}{1em}{\textsuperscript{\thefootnotemark}\,}
-% \newcolumntype{Y}{>{\centering\arraybackslash}X}
-% \usepackage[a4paper]{geometry}
-% \usepackage{caption}
-% \usepackage[bottom,flushmargin,hang,multiple]{footmisc}
-% \usepackage{pdflscape}
-% \usepackage[paper=portrait,pagesize]{typearea}
-% \usepackage{rotating}
-% \usepackage{fullpage}
-% \usepackage{tabu}
-\usepackage{lscape}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcommand{\elandscape}{\end{landscape}}
-\usepackage{rotating}
-\newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
-\newcommand{\esideways}{\end{sidewaystable}}
-\KOMAoption{captions}{tableheading}
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\usepackage[round]{natbib}
-\bibliographystyle{apalike}
-\usepackage{bookmark}
-
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  colorlinks=true,
-  linkcolor={blue!100!black},
-  filecolor={Maroon},
-  citecolor={blue!100!black},
-  urlcolor={blue!100!black},
-  pdfcreator={LaTeX via pandoc}}
-
-\author{}
-\date{}
-
-\begin{document}
-
 \title{Do investors in clean energy ETFs herd?}
@@
 \newpage
-
-\setstretch{1.5}
-\section{Introduction}\label{introduction}
-
-Argument: Investment interest on green ETFs has been explosive mainly by
-climate risks faced by the global economy and the actions of policy
-makers, goverments and organizations towards a sustainable future.
-
-Derived from \citet{decclesia2024}: Among the ESG ETFs, the Clean Energy
-(CE) ETFs have been the best-performing ones in 2022, followed by the
-Cybersecurity and Artificial Intelligence (AI) ETFs. The clean energy
-transition represents one of the largest multi-decade secular growth
-opportunities.
-
-From \citet{naqvi2022}: After the inclusion of Green energy financing in
-the list of United Nations Sustainability Goals (SDGs) as SDG 7, the
-role, importance, and visibility of green financial products; all have
-escalated enormousl
-
-\section{Literature review}\label{literature-review}
-
-\section{Data and methodology}\label{data-and-methodology}
-
-\subsection{Data}\label{data}
-
-The sample consists of alternative energy equity ETFs (green ETFs) that
-are traded in the US markets. The number of available alternative energy
-ETFs in our sample varied from 10 in the beginning of analysis to 30 at
-the most. The period of analysis runs from May 1st of 2016 through 19th
-June of 2024. The starting date was selected on the basis of the COP
-Paris agreement. Daily logarithmic returns were computed from the
-closing prices of ETFs for a total of 2122 observations.
-
-\newpage
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{3.89in}|p{1.99in}}
-\caption{List of used alternative energy equity ETFs}\tabularnewline
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Source}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endfirsthead
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Source}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ALPS\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLUE\ HORIZON\ BNE\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ S\&P\ KENSHO\ CLEAN\ POWER\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ CLEANTECH\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{PROSHARES\ S\&P\ KENSHO\ CLEANTECH\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ MSCI\ SUSTAINABLE\ FUTURE\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIRST\ TRUST\ GLOBAL\ WIND\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIDELITY\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLDS.BLOOMBERG\ CN.\ EN.\ EQ.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ SMRT.GRID\ INFRA\ IDX\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DEFIANCE\ NEXT\ GEN\ H2\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DIREXION\ HYDROGEN\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ HYDROGEN\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ISHARES\ GLOBAL\ CLEAN\ EN.\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLACKR.WLD.EXUS\ CRBN\ TSTN.READINESS}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUB.CBN.TSTN.\&\ INFRA}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TCW\ TRANSFORM\ SYSTEMS\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ URANIUM\ AND\ NUCLEAR\ ENERGY}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUVEEN\ GLOBAL\ NET\ ZERO\ TRANSITION\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ MSCI\ USA\ CIM.\ PA.\ ALIGNED\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ GLOBAL\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ GREY.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ SOLAR\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ RENEWABLE\ ENERGY\ PRODUCERS}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TRUESHARES\ EAG.GLB.\ RENWEN.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ LOW\ CARBON\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SMARTETFS\ SUST.EN.\ II\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ SOLAR\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VIRTUS\ DUFF\ \&\ PHELPS\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ WIND\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Results of baseline and rolling window analysis points to significant
-herding for the whole period and in various instances.
-
-\subsection{Methodology}\label{methodology}
-
-Following the relevant literature we calculate the Cross Sectional
-Absolute Deviation (CSAD) measure for each day in the following manner.
-We compute the difference of the ith ETF and market return where market
-return is proxied by the cross sectional average of returns for sample
-of our ETFs available for each day using equation (1):
-
-\begin{equation}\phantomsection\label{eq-csad}{
-CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|
-}\end{equation}
-
-The behavior of the CSAD measure for US Alternative Energy ETFs is
-presented in Figue 1.
-
-At a later stage we estimate a non-linear regression as in
-\citet{galariotis2015}.
-
-\begin{equation}\phantomsection\label{eq-herding}{
-CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t
-}\end{equation}
-
-The testing procedure of herding relies on the above Equation (2).
-Rational asset pricing models predict a linear relationship between
-return dispersion and market returns under normal conditions, a
-relationship that is no longer valid in the presence of herding. Herding
-behavior leads to an increasing or decreasing cross sectional dispersion
-with respect to market returns. In other words, herding is captured by a
-non-linear term in the standard pricing equation indicating a decreasing
-or an increasing returns' dispersion.
-
-\section{Results}\label{results}
-
-\subsection{General herding behaviour}\label{general-herding-behaviour}
-
-Stated differently, as \citet{chang2000} argue, in the case of herding
-the coefficient on the non-linear term (γ2) will be negative and
-statistically significant. Table 2 presens the results of herding for
-the full sample employing the non-linear equation (2). The estimated
-coefficient on market return is positive and highly significant as
-expected.The estimated coefficient on the non-linear term is negative
-(-1.2773) and statistically significant with a t-statistic of -9.71
-suggesting that herd behavior is present and robust in the US
-alternative energy ETFs.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.9}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.99in}|p{1.99in}|p{1.99in}}
-\caption{Estimation results of herding in the U.S. equity alternative energy ETFs}\tabularnewline
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endfirsthead
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2883***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2773***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(47.09)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(33.333)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(-9.71)}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-There is ample evidence in the relevant literature that herding behavior
-in various asset markets \citep[see][]{pochea2017} exhibits asymmetry
-and time-varying characteristics. To this end, we proceed to estimate
-Equation (2) using the quantile regression (QR) proposed by
-\citet{koenker1978} and Table 3 presents the results of estimating
-Equation (2) across various quantiles of the returns dispersion. Our
-focus is on the herding coefficient γ2, as a significant negative value
-of γ2 is indicative of herding. Such a finding is observed at two
-quantiles namely 25\% and 50\% with a value of -1.1056 and -1.165 which
-are highly significant. It is worth mentioning that the sign of the
-herding coefficient remains negative for almost all quantiles while the
-significance changes from significant to insifnificant while we move
-from low and middle to upper quantiles (75 and 90\%).
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.39in}|p{1.39in}|p{1.39in}|p{1.39in}}
-\caption{Estimation results of herding across various quantiles}\tabularnewline
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-4}\endfirsthead
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-4}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2536***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3736}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2461***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1056***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0037***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2648***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.165***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0048***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.3011***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1473***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0064***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2999***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.2314}}}} \\
-
-\ascline{1pt}{000000}{1-4}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-\subsection{Herding behaviour during extreme market
-periods}\label{herding-behaviour-during-extreme-market-periods}
-
-It is widely accepted that asset returns are characterized by asymmetry,
-that is, return dispersion tend to behave differently in rising and
-falling markets \citep[see][]{geert2000, zhou2013, longin2001}. Based on
-the above and in order to provide additional insight on the herding
-phenomenon we examine whether herding presents an asymmetric response on
-days when the market is up vis-à-vis days when the market is down. To
-this end, we augment Eq. 2 as follows:
-
-\[
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
-\] where D is a dummy variable that takes the value of 1 when the market
-return is negative and 0 otherwise.
-
-Therefore, our exploration of asymmetric behavior of herding phenomenon
-is carried through the inspection of the statistical significance and
-the sign of the two estimated coefficients γ3 vs γ4 (up vs down
-markets). It should be noted, that examining the relationship between
-returns dispersion and market-wide returns across various quantiles of
-the returns distribution allows us to make more robust inference
-regarding the true behavior of the phenomenon.
-
-Table 4 reports the estimation results of herding in the up and down
-markets based on Eq. 3. In general, we find that herding is more likely
-to occur in down markets than in up markets, which is indicative of the
-asymmetry of herding behavior.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}}
-\caption{Estimation results of herding in up and down markets}\tabularnewline
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\
-
-\ascline{1pt}{000000}{1-6}\endfirsthead
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\
-
-\ascline{1pt}{000000}{1-6}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2532***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3669***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2522***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1522}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2475***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2383**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2477***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1171***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2247***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.3838}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2634***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3144***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0050***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2500***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.3135}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2785***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.9721***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0065***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2788***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.0169}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2942***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2003***}}}} \\
-
-\ascline{1pt}{000000}{1-6}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Herding is present at low quantiles when markets are rising with an
-estimated coefficient γ3 of -1.3669 and -1.2383 and highly significant
-respectively. However, when markets are declining, investors seem to
-neglect their own information set and imitate the actions of others
-resulting in a highly significant coefficient of herding ( γ4) across
-four out of five quantiles. Furthermore, we find that in high quantiles
-(75\% \& 90\%) and when markets are rising the coefficient of interest (
-γ3) turns positive but insignificant.
-
-\subsection{Rolling window analysis}\label{rolling-window-analysis}
-
-There is ample evidence that herding might be time dependent
-\citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In order to
-gain further insight on the time varying nature of herding we conducted
-a rolling window analysis. The size of the rolling window is related to
-the timescales of the system (response times), and the aim of the
-research \citep{babalos2015}. There is no golden rule for the right size
-of the rolling window, there is a trade-off between having a long enough
-window to estimate the metrics, and short enough to have a sufficient
-number of windows in order to be able to derive a trend. In light of the
-above discussion we set off to conduct a rolling window analysis of 50
-observations. Figure 2 plots the time evolution of the value of the
-estimated significance of the herding coefficient (γ2) using the rolling
-window analysis.
-
-We observe several periods of herding behavior as reflected in the
-troughs in Figure 2. The most prominent cases of herding occur between
-March and May of 2020 followed by several instances of herding in the
-period that extends from March through April of 2017 and the period of
-February-March of 2023. On the other side, we derive significant moments
-of anti-herding behavior in the clean energy ETFs by observing the
-spikes in Figure 2. Cross sectional dispersion appears to increase with
-respect to market-wide returns which is a sign of anti-herding behavior
-on behalf of investors around December of 2016 and later during
-September of 2022.
-
-\subsection{Probit analysis}\label{probit-analysis}
-
-The behavior of participants in energy markets is closely related to the
-developments in the field of climate risks, carbon emmissions and
-environmentally friendly policies. There are a few studies that attempt
-to quantify the effects of unceretainty related to climate on the
-economy and financial markets (see inter alia\ldots.). \citet{bua2024}
-developed two climate risk related indexes namely transition and
-physical risk using a text-based approach in order to study the effect
-of these risks in financial markets. It is expected that investors would
-prefer to hold assets that perform well in the face of increasing
-climate change risks, even if this entails accepting lower returns for
-such climate-hedging assets. Therefore, in the context of our study and
-following previous studies that study the determinants of herding
-behavior \citep[see][]{bouri2019, demirer2018}, we attempt to study the
-effect of climate-related uncertainty on the formation of herding
-behavior in the clean energy market. Given this, we define a dummy
-variable, which takes a value of 1 during periods of statistically
-significant herding (i.e., for days when the rolling t-statistic on γ2
-\textless{} −1.96) and zero otherwise, and then, we use a Probit model
-to relate this dummy to the two climate risk indexes developed by
-\citet{bua2024}. It should be noted that due to availability issues the
-probit analysis ends in December of 2023. The results from the Probit
-model are reported in Table 2, where only the physical risk index
-significantly decreases the probability of herding. In other words,
-climate risks is good news for clean energy stocks or firms resulting in
-anti herding behavior.
-
-This implies that in the presence of higher physical risk with respect
-to the climate, clean energy ETFs become a more attractive investment
-option for investors that allocate their money to the various
-alternative energy investment products. As a result, the cross sectional
-dispersion of clean energy ETFs tends to increase.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{3.78in}|p{2.14in}}
-\caption{Estimation results of the probit model}\tabularnewline
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endfirsthead
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Constant}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{LogL}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Furthermore, suppose we get the median values of these two series. then
-we define values above median as high and below median as low.
-
-We define a dummy =1 if values\textgreater median and 0 otherwise and in
-this way we will have PRI values that are bigger than median and 0
-otherwise. We also define a dummy which is lower than median, i.e., 1
-and 0 otherwise, then we use these high PRI and high TRI in one probit
-regression and low TRI and low PRI in another. Results are presented in
-the following table.
-
-We observe higher uncertainty that stems from physical or transition
-risk causes antiherding which is in line with the logic we discussed
-earlier.
-
-\newpage
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{2.33in}|p{2.00in}|p{1.96in}}
-\caption{Estimation results of the probit model with high and low climate risk
-indexes (above or below median)}\tabularnewline
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endfirsthead
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-\section{Conclusion}\label{conclusion}
-
-This study offers novel and valuable insights on herding behavior in
-clean energy ETFs.
-
-\newpage
-
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\renewcommand{\bibsection}{}
-\bibliography{references.bib}
-
-\end{document}

### 2024-10-04 Functions/flextable_word.R

@@ -1,0 +1,31 @@
+flextable_word <- function(data,
+                           caption = "Add title",
+                           caption_style = "normal",
+                           width_add = 0,
+                           heigth_add = 0) {
+  flextable(data = data, theme_fun = theme_booktabs) %>%
+    colformat_double() %>% 
+    set_caption(caption = caption, style = caption_style) %>%
+    border_inner(border = fp_border(color = "white"), part = "all") %>%
+    vline_left(border = fp_border(color = "white"), part = "all") %>%
+    vline_right(border = fp_border(color = "white"), part = "all") %>%
+    autofit(add_w =  width_add , add_h = heigth_add, unit = "cm") %>% 
+    align(align = "center", part = "all")
+}
+
+flextable_pdf <- function(data,
+                          caption = "Add title",
+                          caption_style = "normal",
+                          width_add = 0,
+                          heigth_add = 0) {
+  flextable(data = data) %>%
+    colformat_double() %>% 
+    set_caption(caption = caption, style = caption_style) %>%
+    border_inner(border = fp_border(color = "white"), part = "all") %>%
+    vline_left(border = fp_border(color = "white"), part = "all") %>%
+    vline_right(border = fp_border(color = "white"), part = "all") %>%
+    autofit(add_w =  width_add , add_h = heigth_add, unit = "cm") %>% 
+    align(align = "center", part = "all") %>% 
+    align(align = "center", j = 1)
+}
+

### 2024-10-04 alt_energy_herding.qmd
updated footnotes

@@
 
-From @naqvi2022: After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormousl
+From @naqvi2022: After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously.
 
@@
   mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
+  add_footer_lines(values = as_paragraph(
+    "This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (2) in various quantiles 10, 25, 50, 75 and 90% of the returns distribution.
+*,**,*** denotes significance at 10%,5% and 1% respectively."
+  )) %>% 
   autofit(add_w = 0.2)
@@
   mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
+  add_footer_lines(
+    values = as_paragraph(
+     "This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (3). *,**,***denotes significance at 10%,5% and 1% respectively."
+    )
+  ) %>%
   autofit(add_w = -0.2)
@@
   align(align = "left", j = 1, part = "all") %>%
+  add_footer_lines(
+    values = as_paragraph(
+      "Notes: **,*** denotes statistically significant at 5% and 1%"
+    )
+  ) %>% 
   autofit(add_w = 1.5)
@@
   align(align = "left", j = 1, part = "all") %>%
-  autofit(add_w = 1.5)
+  add_footer_lines(
+    values = as_paragraph(
+      "Notes: *, denotes statistically significant at 10%"
+    )
+  ) %>%
+  autofit(add_w = 1.4)
 

### 2024-10-04 alt_energy_herding.tex
updated footnotes

@@
 role, importance, and visibility of green financial products; all have
-escalated enormousl
+escalated enormously.
 
@@
 
+\multicolumn{4}{>{\raggedright}m{\dimexpr 5.54in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (2)\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+
 \end{longtable}
@@
 \ascline{1pt}{000000}{1-6}
+
+\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
 
@@
 
+\multicolumn{2}{>{\raggedright}m{\dimexpr 5.92in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\
+
 \end{longtable}
@@
 
-\begin{longtable}[l]{|p{2.33in}|p{2.00in}|p{1.96in}}
+\begin{longtable}[l]{|p{2.23in}|p{1.90in}|p{1.86in}}
 \caption{Estimation results of the probit model with high and low climate risk
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.33in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.96in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
 
 \ascline{1pt}{000000}{1-3}
+
+\multicolumn{3}{>{\raggedright}m{\dimexpr 5.99in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ *,\ denotes\ statistically\ significant\ at\ 10\%}}}} \\
 

### 2024-10-10 alt_energy_herding.qmd
added graphs. worked on cross-references

@@
 source(here("Functions","borderlines.R" ))
+source(here("Functions","fx_plot.R" ))
 ```
@@
 
-The sample consists of alternative energy equity ETFs (green ETFs) that are traded in the US markets.
-The number of available alternative energy ETFs in our sample varied from 10 in the beginning of analysis to 30 at the most.
-The period of analysis runs from May 1st of 2016 through 19th June of 2024.
+The sample consists of alternative energy equity ETFs (green ETFs) that are traded in the US markets (see @tbl-data in the Appendix).^[The data were sourced from \url{https://datastream.org/en-ca/}] The number of available alternative energy ETFs in our sample varied from 10 in the beginning of analysis to 30 at the most.
+The period of analysis runs from May 1^st^ of 2016 through 19^th^ June of 2024.
 The starting date was selected on the basis of the COP Paris agreement.
 Daily logarithmic returns were computed from the closing prices of ETFs for a total of 2122 observations.
-
-\newpage
-
-```{r}
-#| label: data
-#| tbl-cap: "List of used alternative energy equity ETFs"
-#| cache: false
-
-tribble(
-  ~"ETF", ~"Source",
-  "ALPS CLEAN ENERGY ETF", "",
-  "BLUE HORIZON BNE ETF", " ",
-  "SPDR S&P KENSHO CLEAN POWER ETF", " ",
-  "GLOBAL X CLEANTECH ETF", " ",
-  "PROSHARES S&P KENSHO CLEANTECH ETF", " ",
-  "INVESCO MSCI SUSTAINABLE FUTURE ETF", " ",
-  "FIRST TRUST GLOBAL WIND ENERGY ETF", " ",
-  "FIDELITY CLEAN ENERGY ETF", " ",
-  "GLDS.BLOOMBERG CN. EN. EQ.ETF", " ",
-  "FST.NQ.CN.EDGE SMRT.GRID INFRA IDX ETF", " ",
-  "DEFIANCE NEXT GEN H2 ETF", " ",
-  "DIREXION HYDROGEN ETF", " ",
-  "GLOBAL X HYDROGEN ETF", " ",
-  "ISHARES GLOBAL CLEAN EN. ETF", " ",
-  "BLACKR.WLD.EXUS CRBN TSTN.READINESS", " ",
-  "NUB.CBN.TSTN.& INFRA", " ",
-  "TCW TRANSFORM SYSTEMS ETF", " ",
-  "VANECK URANIUM AND NUCLEAR ENERGY", " ",
-  "NUVEEN GLOBAL NET ZERO TRANSITION ETF", " ",
-  "SPDR MSCI USA CIM. PA. ALIGNED ETF", " ", 
-  "INVESCO GLOBAL CLEAN ENERGY ETF", " ", 
-  "FST.NQ.CN.EDGE GREY.ETF", " ",
-  "GLOBAL X SOLAR ETF", " ", 
-  "GLOBAL X RENEWABLE ENERGY PRODUCERS", " ",
-  "TRUESHARES EAG.GLB. RENWEN.ETF", " ",
-  "VANECK LOW CARBON ENERGY ETF", " ",
-  "SMARTETFS SUST.EN. II ETF", " ",
-  "INVESCO SOLAR ETF", " ", 
-  "VIRTUS DUFF & PHELPS CLEAN ENERGY ETF", " ",
-  "GLOBAL X WIND ENERGY ETF", " "
-) %>% 
-  flextable_pdf() %>% 
-  align(align = "left", j = 1,  part = "all") %>%
-  autofit(add_w = 1.5)
-
-```
-
-Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.
 
@@
 Following the relevant literature we calculate the Cross Sectional Absolute Deviation  (CSAD) measure for each day in the following manner.
-We compute the difference of the ith ETF and market return where market return is proxied by the cross sectional average of returns for sample of our ETFs available for each day using equation (1):
+We compute the difference of the ith ETF and market return where market return is proxied by the cross sectional average of returns for sample of our ETFs available for each day using @eq-csad:
 
@@
 $$ {#eq-csad}
-
-The behavior of the CSAD measure for US Alternative Energy ETFs is presented in Figue 1.
 
@@
 
-At a later stage we estimate a non-linear regression as in @galariotis2015.
+At a later stage we estimate a non-linear regression as in @galariotis2015:
 
@@
 
-The testing procedure of herding relies on the above Equation (2).
+The testing procedure of herding relies on the above @eq-herding.
 Rational asset pricing models predict a linear relationship between return dispersion and market returns under normal conditions, a relationship that is no longer valid in the presence of herding.
-Herding behavior leads to an increasing or decreasing cross sectional dispersion with respect to market returns.
+Herding behaviour leads to an increasing or decreasing cross sectional dispersion with respect to market returns.
 In other words, herding is captured by a non-linear term in the standard pricing equation indicating a decreasing or an increasing returns’ dispersion.
+
+Based on the above and in order to provide additional insight on the herding phenomenon we examine whether herding presents an asymmetric response on days when the market is up vis-à-vis days when the market is down.
+To this end, we augment @eq-herding as follows:
+
+$$
+CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
+$$ {#eq-asymmetry}
+
+where $D$ is a dummy variable that takes the value of 1 when the market return is negative and 0 otherwise.
+Therefore, our exploration of asymmetric behavior of herding phenomenon is carried through the inspection of the statistical significance and the sign of the two estimated coefficients $\gamma_3$ vs $\gamma_4$ (up vs down markets).
+
+\newpage
 
@@
 
-Stated differently, as @chang2000 argue, in the case of herding the coefficient on the non-linear term (γ2) will be negative and statistically significant.
-Table 2 presens the results of herding for the full sample employing the non-linear equation (2).
-The estimated coefficient on market return is positive and highly significant as expected.The estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behavior is present and robust in the US alternative energy ETFs.
+The behaviour of the CSAD measure for US Alternative Energy ETFs is presented in @fig-csad.
 
 ```{r}
-#| label: herding
+#| label: fig-csad
+#| cache: false
+#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
+#| fig.height: 3
+#| fig.width: 8
+
+read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 1) %>% 
+  rename(Date = date,
+         "Cross Sectional Absolute Deviations" = CSAD) %>% 
+  dplyr::select(Date, `Cross Sectional Absolute Deviations`) %>% 
+  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
+  fx_plot() +
+  theme(
+    # change plot text size
+    text = element_text(size = 10),
+    plot.tag = element_text(size = 10)
+  )
+
+```
+
+Stated differently, as @chang2000 argue, in the case of herding the coefficient on the non-linear term ($\gamma_2$) will be negative and statistically significant.
+@tbl-herding presents the results of herding for the full sample employing the non-linear @eq-herding.
+The estimated coefficient on market return is positive and highly significant as expected.The estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behaviour is present and robust in the US alternative energy ETFs.
+
+```{r}
+#| label: tbl-herding
 #| tbl-cap: "Estimation results of herding in the U.S. equity alternative energy ETFs"
@@
 
-There is ample evidence in the relevant literature that herding behavior in various asset markets [see @pochea2017] exhibits asymmetry and time-varying characteristics.
-To this end, we proceed to estimate Equation (2) using the quantile regression (QR) proposed by @koenker1978 and Table 3 presents the results of estimating Equation (2) across various quantiles of the returns dispersion.
-Our focus is on the herding coefficient γ2, as a significant negative value of γ2 is indicative of herding.
+There is ample evidence in the relevant literature that herding behaviour in various asset markets [see @pochea2017] exhibits asymmetry and time-varying characteristics.
+To this end, we proceed to estimate @eq-herding using the quantile regression (QR) proposed by @koenker1978 and @tbl-quantile_herding presents the results of estimating @eq-herding across various quantiles of the returns dispersion.
+Our focus is on the herding coefficient $\gamma_2$, as a significant negative value of $\gamma_2$ is indicative of herding.
 Such a finding is observed at two quantiles namely 25% and 50% with a value of -1.1056 and -1.165 which are highly significant.
-It is worth mentioning that the sign of the herding coefficient remains negative for almost all quantiles while the significance changes from significant to insifnificant while we move from low and middle to upper quantiles (75 and 90%).
+It is worth mentioning that the sign of the herding coefficient remains negative for almost all quantiles while the significance changes from significant to insignificant while we move from low and middle to upper quantiles (75\% and 90\%).
 
 ```{r}
-#| label: quantile_herding
+#| label: tbl-quantile_herding
 #| tbl-cap: "Estimation results of herding across various quantiles"
@@
 It is widely accepted that asset returns are characterized by asymmetry, that is, return dispersion tend to behave differently in rising and falling markets [see @geert2000; @zhou2013; @longin2001]. 
-Based on the above and in order to provide additional insight on the herding phenomenon we examine whether herding presents an asymmetric response on days when the market is up vis-à-vis days when the market is down.
-To this end, we augment Eq.
-2 as follows:
+It should be noted, that examining the relationship between returns dispersion and market-wide returns across various quantiles of the returns distribution allows us to make more robust inference regarding the true behaviour of the phenomenon.
+@tbl-asymmetry_herding reports the estimation results of herding in the up and down markets based on @eq-asymmetry.
+In general, we find that herding is more likely to occur in down markets than in up markets, which is indicative of the asymmetry of herding behaviour.
 
-$$
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
-$$
-where D is a dummy variable that takes the value of 1 when the market return is negative and 0 otherwise.
-
-Therefore, our exploration of asymmetric behavior of herding phenomenon is carried through the inspection of the statistical significance and the sign of the two estimated coefficients γ3 vs γ4 (up vs down markets).
-It should be noted, that examining the relationship between returns dispersion and market-wide returns across various quantiles of the returns distribution allows us to make more robust inference regarding the true behavior of the phenomenon.
-
-Table 4 reports the estimation results of herding in the up and down markets
-based on Eq. 3. In general, we find that herding is more likely to occur in down markets than in up markets, which is indicative of the asymmetry of herding behavior.
+\newpage
 
 ```{r}
-#| label: asymmetry_herding
+#| label: tbl-asymmetry_herding
 #| tbl-cap: "Estimation results of herding in up and down markets"
@@
 
-Herding is present at low quantiles when markets are rising with an estimated coefficient γ3 of -1.3669 and -1.2383 and highly significant respectively.
-However, when markets are declining, investors seem to neglect their own information set and imitate the actions of others resulting in a highly significant coefficient of herding ( γ4) across four out of five quantiles.
-Furthermore, we find that in high quantiles (75% & 90%) and when markets are rising the coefficient of interest ( γ3) turns positive but insignificant.
+Herding is present at low quantiles when markets are rising with an estimated coefficient $\gamma_3$ of -1.3669 and -1.2383 and highly significant respectively.
+However, when markets are declining, investors seem to neglect their own information set and imitate the actions of others resulting in a highly significant coefficient of herding ($\gamma_4$) across four out of five quantiles.
+Furthermore, we find that in high quantiles (75\% and 90\%) and when markets are rising the coefficient of interest ($\gamma_3$) turns positive but insignificant.
 
@@
 In order to gain further insight on the time varying nature of herding we conducted a rolling window analysis.
-The size of the rolling window is related to the timescales of the system (response times), and the aim of the research [@babalos2015].
+The size of the rolling window is related to the time-scales of the system (response times), and the aim of the research [@babalos2015].
 There is no golden rule for the right size of the rolling window, there is a trade-off between having a long enough window to estimate the metrics, and short enough to have a sufficient number of windows in order to be able to derive a trend.
 In light of the above discussion we set off to conduct a rolling window analysis of 50 observations.
-Figure 2 plots the time evolution of the value of the estimated significance of the herding coefficient  (γ2) using the rolling window analysis.
-
-We observe several periods of herding behavior as reflected in the troughs in Figure 2.
-The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 and the period of February-March of 2023.
-On the other side, we derive significant moments of anti-herding behavior in the clean energy ETFs by observing the spikes in Figure 2.
-Cross sectional dispersion appears to increase with respect to market-wide returns which is a sign of anti-herding behavior on behalf of investors around December of 2016 and later during September of 2022.
+@fig-rolling_window plots the time evolution of the value of the estimated significance of the herding coefficient ($\gamma_2$) using the rolling window analysis.
 
 ```{r}
-#| label: rolling_window
-#| fig.cap: "Estimated significance of herding coefficient in a rolling window analysis"
+#| label: fig-rolling_window
+#| fig.cap: "Rolling window herding estimates"
 #| cache: false
+#| fig.width: 8
+#| fig.height: 6
+
+herding_gg <- 
+  read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 4) %>% 
+  rename(Date = DATE) %>% 
+  dplyr::select(Date, `_b_abscsar`, `_b_csar2`) %>% 
+  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
+  mutate(
+    Series =  recode(
+      Series,
+      `_b_abscsar` = "gamma[1]",
+      `_b_csar2` = "gamma[2]",
+    )
+  ) %>% 
+  fx_recode_plot(variables_color = 2) +
+  # add horizontal line at 0
+  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
+  theme(
+    # change plot text size
+    text = element_text(size = 10),
+    plot.tag = element_text(size = 10)
+  )
+
+tstat_gg <- 
+  read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 4) %>% 
+  rename(Date = DATE) %>% 
+  dplyr::select(Date, `tstat abscsar`, `tstat csar2`) %>% 
+  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
+  mutate(
+    Series =  recode(
+      Series,
+      `tstat abscsar` = "t-statistic~gamma[1]",
+      `tstat csar2` = "t-statistic~gamma[2]"
+    )
+  ) %>% 
+  fx_recode_plot(variables_color = 2) +
+  # add perforated horizontal lines at 1.96 and -1.96
+  geom_hline(yintercept = c(1.96, -1.96), linetype = "dashed", color = "red", size = 0.4) +
+  theme(
+    # change plot text size
+    text = element_text(size = 10),
+    plot.tag = element_text(size = 10)
+  )
+
+herding_gg / tstat_gg
 
@@
 
+We observe several periods of herding behaviour as reflected in the troughs in @fig-rolling_window.
+The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 and the period of February-March of 2023.
+On the other side, we derive significant moments of anti-herding behaviour in the clean energy ETFs by observing the spikes in @fig-rolling_window.
+Cross sectional dispersion appears to increase with respect to market-wide returns which is a sign of anti-herding behaviour on behalf of investors around December of 2016 and later during September of 2022.
+
 ## Probit analysis
 
-The behavior of participants in energy markets is closely related to the developments in the field of climate risks, carbon emmissions  and environmentally friendly policies.
-There are a few studies that attempt to quantify the effects of unceretainty related to climate on the economy and financial markets (see inter alia….).
+The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies.
+There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets \textcolor{red}{(see inter alia….)}.
 @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.
 It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets.
-Therefore, in the context of our study and following previous studies that study the determinants of herding behavior [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.
-Given this, we define a dummy variable, which takes a value of 1 during periods of statistically significant herding (i.e., for days when the rolling t-statistic on γ2 < −1.96) and zero otherwise, and then, we use a Probit model to relate this dummy to the two climate risk indexes developed by @bua2024.
+Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.
+Given this, we define a dummy variable, which takes a value of 1 during periods of statistically significant herding (i.e., for days when the rolling t-statistic on $\gamma_2 < −1.96$) and zero otherwise, and then, we use a Probit model to relate this dummy to the two climate risk indexes developed by @bua2024.
 It should be noted that due to availability issues the probit analysis ends in December of 2023.
-The results from the Probit model are reported in Table 2, where only the physical risk index significantly decreases the probability of herding.
-In other words, climate risks is good news for clean energy stocks or firms resulting in anti herding behavior.
+The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.
+In other words, climate risks is good news for clean energy stocks or firms resulting in anti herding behaviour.
 
@@
 ```{r}
-#| label: probit_analysis
+#| label: tbl-probit_analysis
 #| tbl-cap: "Estimation results of the probit model"
@@
 
-Furthermore, suppose we get the median values of these two series. then we define values above median as high and below median as low.
-
+Furthermore, suppose we get the median values of these two series.
+then we define values above median as high and below median as low.
 We define a dummy =1 if values>median and 0 otherwise and in this way we will have PRI values that are bigger than median and 0 otherwise.
@@
 Results are presented in the following table.
+We observe higher uncertainty that stems from physical or transition risk causes anti-herding which is in line with the logic we discussed earlier.
 
-We observe higher uncertainty that stems from physical or transition risk causes antiherding which is in line with the logic we discussed earlier.
-
-\newpage
 ```{r}
-#| label: probit_analysis2
+#| label: tbl-probit_analysis2
 #| tbl-cap: "Estimation results of the probit model with high and low climate risk indexes (above or below median)"
@@
 
+Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.
 \newpage
+
 # References {.unnumbered}
@@
 
-<!-- \setcounter{section}{0} -->
-<!-- \renewcommand{\thesection}{\Alph{section}} -->
+\setcounter{section}{0}
+\renewcommand{\thesection}{\Alph{section}}
 
-<!-- \setcounter{table}{0} -->
-<!-- \renewcommand{\thetable}{A\arabic{table}} -->
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
 
-<!-- \setcounter{figure}{0} -->
-<!-- \renewcommand{\thefigure}{A\arabic{figure}} -->
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
 
-<!-- \newpage -->
+\newpage
 
-<!-- # Appendix -->
+# Appendix
 
-<!-- ## Data -->
+## Data
+
+```{r}
+#| label: tbl-data
+#| tbl-cap: "List of used alternative energy equity ETFs"
+#| cache: false
+
+tribble(
+  ~"ETF",
+  "ALPS CLEAN ENERGY ETF",
+  "BLUE HORIZON BNE ETF",
+  "SPDR S&P KENSHO CLEAN POWER ETF",
+  "GLOBAL X CLEANTECH ETF",
+  "PROSHARES S&P KENSHO CLEANTECH ETF",
+  "INVESCO MSCI SUSTAINABLE FUTURE ETF",
+  "FIRST TRUST GLOBAL WIND ENERGY ETF",
+  "FIDELITY CLEAN ENERGY ETF",
+  "GLDS.BLOOMBERG CN. EN. EQ.ETF",
+  "FST.NQ.CN.EDGE SMRT.GRID INFRA IDX ETF",
+  "DEFIANCE NEXT GEN H2 ETF",
+  "DIREXION HYDROGEN ETF",
+  "GLOBAL X HYDROGEN ETF",
+  "ISHARES GLOBAL CLEAN EN. ETF",
+  "BLACKR.WLD.EXUS CRBN TSTN.READINESS",
+  "NUB.CBN.TSTN.& INFRA",
+  "TCW TRANSFORM SYSTEMS ETF",
+  "VANECK URANIUM AND NUCLEAR ENERGY",
+  "NUVEEN GLOBAL NET ZERO TRANSITION ETF",
+  "SPDR MSCI USA CIM. PA. ALIGNED ETF", 
+  "INVESCO GLOBAL CLEAN ENERGY ETF", 
+  "FST.NQ.CN.EDGE GREY.ETF",
+  "GLOBAL X SOLAR ETF", 
+  "GLOBAL X RENEWABLE ENERGY PRODUCERS",
+  "TRUESHARES EAG.GLB. RENWEN.ETF",
+  "VANECK LOW CARBON ENERGY ETF",
+  "SMARTETFS SUST.EN. II ETF",
+  "INVESCO SOLAR ETF", 
+  "VIRTUS DUFF & PHELPS CLEAN ENERGY ETF",
+  "GLOBAL X WIND ENERGY ETF"
+) %>% 
+  flextable_pdf() %>% 
+  align(align = "left", j = 1,  part = "all") %>%
+  autofit(add_w = 3)
+
+```

### 2024-10-10 alt_energy_herding.tex
added graphs. worked on cross-references

@@
 Economic Research Department, South African Reserve Bank, Pretoria, South Africa.} \,\,
-Riza Demirer\footnote{Department of Economics and Finance, Southern Illinois University Edwardsville, Edwardsville, IL 62026-1102, USA; Email: rdemire@siue.edu} \,\,
+% Riza Demirer\footnote{Department of Economics and Finance, Southern Illinois University Edwardsville, Edwardsville, IL 62026-1102, USA; Email: rdemire@siue.edu} \,\,
 Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.}
@@
 The sample consists of alternative energy equity ETFs (green ETFs) that
-are traded in the US markets. The number of available alternative energy
-ETFs in our sample varied from 10 in the beginning of analysis to 30 at
-the most. The period of analysis runs from May 1st of 2016 through 19th
-June of 2024. The starting date was selected on the basis of the COP
-Paris agreement. Daily logarithmic returns were computed from the
-closing prices of ETFs for a total of 2122 observations.
-
-\newpage
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.5}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{3.89in}|p{1.99in}}
-\caption{List of used alternative energy equity ETFs}\tabularnewline
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Source}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endfirsthead
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Source}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ALPS\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLUE\ HORIZON\ BNE\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ S\&P\ KENSHO\ CLEAN\ POWER\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ CLEANTECH\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{PROSHARES\ S\&P\ KENSHO\ CLEANTECH\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ MSCI\ SUSTAINABLE\ FUTURE\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIRST\ TRUST\ GLOBAL\ WIND\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIDELITY\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLDS.BLOOMBERG\ CN.\ EN.\ EQ.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ SMRT.GRID\ INFRA\ IDX\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DEFIANCE\ NEXT\ GEN\ H2\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DIREXION\ HYDROGEN\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ HYDROGEN\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ISHARES\ GLOBAL\ CLEAN\ EN.\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLACKR.WLD.EXUS\ CRBN\ TSTN.READINESS}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUB.CBN.TSTN.\&\ INFRA}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TCW\ TRANSFORM\ SYSTEMS\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ URANIUM\ AND\ NUCLEAR\ ENERGY}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUVEEN\ GLOBAL\ NET\ ZERO\ TRANSITION\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ MSCI\ USA\ CIM.\ PA.\ ALIGNED\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ GLOBAL\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ GREY.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ SOLAR\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ RENEWABLE\ ENERGY\ PRODUCERS}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TRUESHARES\ EAG.GLB.\ RENWEN.ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ LOW\ CARBON\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SMARTETFS\ SUST.EN.\ II\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ SOLAR\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VIRTUS\ DUFF\ \&\ PHELPS\ CLEAN\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.89in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ WIND\ ENERGY\ ETF}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Results of baseline and rolling window analysis points to significant
-herding for the whole period and in various instances.
+are traded in the US markets (see Table~\ref{tbl-data} in the
+Appendix).\footnote{The data were sourced from
+  \url{https://datastream.org/en-ca/}} The number of available
+alternative energy ETFs in our sample varied from 10 in the beginning of
+analysis to 30 at the most. The period of analysis runs from May
+1\textsuperscript{st} of 2016 through 19\textsuperscript{th} June of
+2024. The starting date was selected on the basis of the COP Paris
+agreement. Daily logarithmic returns were computed from the closing
+prices of ETFs for a total of 2122 observations.
 
@@
 return is proxied by the cross sectional average of returns for sample
-of our ETFs available for each day using equation (1):
+of our ETFs available for each day using Equation~\ref{eq-csad}:
 
@@
 
-The behavior of the CSAD measure for US Alternative Energy ETFs is
-presented in Figue 1.
-
 At a later stage we estimate a non-linear regression as in
-\citet{galariotis2015}.
+\citet{galariotis2015}:
 
@@
 
-The testing procedure of herding relies on the above Equation (2).
-Rational asset pricing models predict a linear relationship between
-return dispersion and market returns under normal conditions, a
-relationship that is no longer valid in the presence of herding. Herding
-behavior leads to an increasing or decreasing cross sectional dispersion
-with respect to market returns. In other words, herding is captured by a
-non-linear term in the standard pricing equation indicating a decreasing
-or an increasing returns' dispersion.
+The testing procedure of herding relies on the above
+Equation~\ref{eq-herding}. Rational asset pricing models predict a
+linear relationship between return dispersion and market returns under
+normal conditions, a relationship that is no longer valid in the
+presence of herding. Herding behaviour leads to an increasing or
+decreasing cross sectional dispersion with respect to market returns. In
+other words, herding is captured by a non-linear term in the standard
+pricing equation indicating a decreasing or an increasing returns'
+dispersion.
+
+Based on the above and in order to provide additional insight on the
+herding phenomenon we examine whether herding presents an asymmetric
+response on days when the market is up vis-à-vis days when the market is
+down. To this end, we augment Equation~\ref{eq-herding} as follows:
+
+\begin{equation}\phantomsection\label{eq-asymmetry}{
+CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
+}\end{equation}
+
+where \(D\) is a dummy variable that takes the value of 1 when the
+market return is negative and 0 otherwise. Therefore, our exploration of
+asymmetric behavior of herding phenomenon is carried through the
+inspection of the statistical significance and the sign of the two
+estimated coefficients \(\gamma_3\) vs \(\gamma_4\) (up vs down
+markets).
+
+\newpage
 
@@
 
+The behaviour of the CSAD measure for US Alternative Energy ETFs is
+presented in Figure~\ref{fig-csad}.
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
+
+}
+
+\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
+US Alternative Energy ETFs}
+
+\end{figure}%
+
 Stated differently, as \citet{chang2000} argue, in the case of herding
-the coefficient on the non-linear term (γ2) will be negative and
-statistically significant. Table 2 presens the results of herding for
-the full sample employing the non-linear equation (2). The estimated
-coefficient on market return is positive and highly significant as
-expected.The estimated coefficient on the non-linear term is negative
-(-1.2773) and statistically significant with a t-statistic of -9.71
-suggesting that herd behavior is present and robust in the US
-alternative energy ETFs.
+the coefficient on the non-linear term (\(\gamma_2\)) will be negative
+and statistically significant. Table~\ref{tbl-herding} presents the
+results of herding for the full sample employing the non-linear
+Equation~\ref{eq-herding}. The estimated coefficient on market return is
+positive and highly significant as expected.The estimated coefficient on
+the non-linear term is negative (-1.2773) and statistically significant
+with a t-statistic of -9.71 suggesting that herd behaviour is present
+and robust in the US alternative energy ETFs.
 
@@
 \begin{longtable}[l]{|p{1.99in}|p{1.99in}|p{1.99in}}
-\caption{Estimation results of herding in the U.S. equity alternative energy ETFs}\tabularnewline
+
+\caption{\label{tbl-herding}Estimation results of herding in the U.S.
+equity alternative energy ETFs}
+
+\tabularnewline
 
@@
 
-There is ample evidence in the relevant literature that herding behavior
-in various asset markets \citep[see][]{pochea2017} exhibits asymmetry
-and time-varying characteristics. To this end, we proceed to estimate
-Equation (2) using the quantile regression (QR) proposed by
-\citet{koenker1978} and Table 3 presents the results of estimating
-Equation (2) across various quantiles of the returns dispersion. Our
-focus is on the herding coefficient γ2, as a significant negative value
-of γ2 is indicative of herding. Such a finding is observed at two
+There is ample evidence in the relevant literature that herding
+behaviour in various asset markets \citep[see][]{pochea2017} exhibits
+asymmetry and time-varying characteristics. To this end, we proceed to
+estimate Equation~\ref{eq-herding} using the quantile regression (QR)
+proposed by \citet{koenker1978} and Table~\ref{tbl-quantile_herding}
+presents the results of estimating Equation~\ref{eq-herding} across
+various quantiles of the returns dispersion. Our focus is on the herding
+coefficient \(\gamma_2\), as a significant negative value of
+\(\gamma_2\) is indicative of herding. Such a finding is observed at two
 quantiles namely 25\% and 50\% with a value of -1.1056 and -1.165 which
@@
 herding coefficient remains negative for almost all quantiles while the
-significance changes from significant to insifnificant while we move
-from low and middle to upper quantiles (75 and 90\%).
+significance changes from significant to insignificant while we move
+from low and middle to upper quantiles (75\% and 90\%).
 
@@
 \begin{longtable}[l]{|p{1.39in}|p{1.39in}|p{1.39in}|p{1.39in}}
-\caption{Estimation results of herding across various quantiles}\tabularnewline
+
+\caption{\label{tbl-quantile_herding}Estimation results of herding
+across various quantiles}
+
+\tabularnewline
 
@@
 that is, return dispersion tend to behave differently in rising and
-falling markets \citep[see][]{geert2000, zhou2013, longin2001}. Based on
-the above and in order to provide additional insight on the herding
-phenomenon we examine whether herding presents an asymmetric response on
-days when the market is up vis-à-vis days when the market is down. To
-this end, we augment Eq. 2 as follows:
+falling markets \citep[see][]{geert2000, zhou2013, longin2001}. It
+should be noted, that examining the relationship between returns
+dispersion and market-wide returns across various quantiles of the
+returns distribution allows us to make more robust inference regarding
+the true behaviour of the phenomenon. Table~\ref{tbl-asymmetry_herding}
+reports the estimation results of herding in the up and down markets
+based on Equation~\ref{eq-asymmetry}. In general, we find that herding
+is more likely to occur in down markets than in up markets, which is
+indicative of the asymmetry of herding behaviour.
 
-\[
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
-\] where D is a dummy variable that takes the value of 1 when the market
-return is negative and 0 otherwise.
-
-Therefore, our exploration of asymmetric behavior of herding phenomenon
-is carried through the inspection of the statistical significance and
-the sign of the two estimated coefficients γ3 vs γ4 (up vs down
-markets). It should be noted, that examining the relationship between
-returns dispersion and market-wide returns across various quantiles of
-the returns distribution allows us to make more robust inference
-regarding the true behavior of the phenomenon.
-
-Table 4 reports the estimation results of herding in the up and down
-markets based on Eq. 3. In general, we find that herding is more likely
-to occur in down markets than in up markets, which is indicative of the
-asymmetry of herding behavior.
+\newpage
 
@@
 \begin{longtable}[l]{|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}}
-\caption{Estimation results of herding in up and down markets}\tabularnewline
+
+\caption{\label{tbl-asymmetry_herding}Estimation results of herding in
+up and down markets}
+
+\tabularnewline
 
@@
 Herding is present at low quantiles when markets are rising with an
-estimated coefficient γ3 of -1.3669 and -1.2383 and highly significant
-respectively. However, when markets are declining, investors seem to
-neglect their own information set and imitate the actions of others
-resulting in a highly significant coefficient of herding ( γ4) across
-four out of five quantiles. Furthermore, we find that in high quantiles
-(75\% \& 90\%) and when markets are rising the coefficient of interest (
-γ3) turns positive but insignificant.
+estimated coefficient \(\gamma_3\) of -1.3669 and -1.2383 and highly
+significant respectively. However, when markets are declining, investors
+seem to neglect their own information set and imitate the actions of
+others resulting in a highly significant coefficient of herding
+(\(\gamma_4\)) across four out of five quantiles. Furthermore, we find
+that in high quantiles (75\% and 90\%) and when markets are rising the
+coefficient of interest (\(\gamma_3\)) turns positive but insignificant.
 
@@
 a rolling window analysis. The size of the rolling window is related to
-the timescales of the system (response times), and the aim of the
+the time-scales of the system (response times), and the aim of the
 research \citep{babalos2015}. There is no golden rule for the right size
@@
 above discussion we set off to conduct a rolling window analysis of 50
-observations. Figure 2 plots the time evolution of the value of the
-estimated significance of the herding coefficient (γ2) using the rolling
-window analysis.
+observations. Figure~\ref{fig-rolling_window} plots the time evolution
+of the value of the estimated significance of the herding coefficient
+(\(\gamma_2\)) using the rolling window analysis.
 
-We observe several periods of herding behavior as reflected in the
-troughs in Figure 2. The most prominent cases of herding occur between
-March and May of 2020 followed by several instances of herding in the
-period that extends from March through April of 2017 and the period of
-February-March of 2023. On the other side, we derive significant moments
-of anti-herding behavior in the clean energy ETFs by observing the
-spikes in Figure 2. Cross sectional dispersion appears to increase with
-respect to market-wide returns which is a sign of anti-herding behavior
-on behalf of investors around December of 2016 and later during
-September of 2022.
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}
+
+}
+
+\caption{\label{fig-rolling_window}Rolling window herding estimates}
+
+\end{figure}%
+
+We observe several periods of herding behaviour as reflected in the
+troughs in Figure~\ref{fig-rolling_window}. The most prominent cases of
+herding occur between March and May of 2020 followed by several
+instances of herding in the period that extends from March through April
+of 2017 and the period of February-March of 2023. On the other side, we
+derive significant moments of anti-herding behaviour in the clean energy
+ETFs by observing the spikes in Figure~\ref{fig-rolling_window}. Cross
+sectional dispersion appears to increase with respect to market-wide
+returns which is a sign of anti-herding behaviour on behalf of investors
+around December of 2016 and later during September of 2022.
 
@@
 
-The behavior of participants in energy markets is closely related to the
-developments in the field of climate risks, carbon emmissions and
+The behaviour of participants in energy markets is closely related to
+the developments in the field of climate risks, carbon emissions and
 environmentally friendly policies. There are a few studies that attempt
-to quantify the effects of unceretainty related to climate on the
-economy and financial markets (see inter alia\ldots.). \citet{bua2024}
-developed two climate risk related indexes namely transition and
-physical risk using a text-based approach in order to study the effect
-of these risks in financial markets. It is expected that investors would
-prefer to hold assets that perform well in the face of increasing
-climate change risks, even if this entails accepting lower returns for
-such climate-hedging assets. Therefore, in the context of our study and
-following previous studies that study the determinants of herding
-behavior \citep[see][]{bouri2019, demirer2018}, we attempt to study the
-effect of climate-related uncertainty on the formation of herding
-behavior in the clean energy market. Given this, we define a dummy
-variable, which takes a value of 1 during periods of statistically
-significant herding (i.e., for days when the rolling t-statistic on γ2
-\textless{} −1.96) and zero otherwise, and then, we use a Probit model
-to relate this dummy to the two climate risk indexes developed by
+to quantify the effects of uncertainty related to climate on the economy
+and financial markets \textcolor{red}{(see inter alia….)}.
+\citet{bua2024} developed two climate risk related indexes namely
+transition and physical risk using a text-based approach in order to
+study the effect of these risks in financial markets. It is expected
+that investors would prefer to hold assets that perform well in the face
+of increasing climate change risks, even if this entails accepting lower
+returns for such climate-hedging assets. Therefore, in the context of
+our study and following previous studies that study the determinants of
+herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
+study the effect of climate-related uncertainty on the formation of
+herding behavior in the clean energy market. Given this, we define a
+dummy variable, which takes a value of 1 during periods of statistically
+significant herding (i.e., for days when the rolling t-statistic on
+\(\gamma_2 < −1.96\)) and zero otherwise, and then, we use a Probit
+model to relate this dummy to the two climate risk indexes developed by
 \citet{bua2024}. It should be noted that due to availability issues the
 probit analysis ends in December of 2023. The results from the Probit
-model are reported in Table 2, where only the physical risk index
-significantly decreases the probability of herding. In other words,
-climate risks is good news for clean energy stocks or firms resulting in
-anti herding behavior.
+model are reported in Table~\ref{tbl-probit_analysis}, where only the
+physical risk index significantly decreases the probability of herding.
+In other words, climate risks is good news for clean energy stocks or
+firms resulting in anti herding behaviour.
 
@@
 \begin{longtable}[l]{|p{3.78in}|p{2.14in}}
-\caption{Estimation results of the probit model}\tabularnewline
+
+\caption{\label{tbl-probit_analysis}Estimation results of the probit
+model}
+
+\tabularnewline
 
@@
 Furthermore, suppose we get the median values of these two series. then
-we define values above median as high and below median as low.
-
-We define a dummy =1 if values\textgreater median and 0 otherwise and in
-this way we will have PRI values that are bigger than median and 0
-otherwise. We also define a dummy which is lower than median, i.e., 1
-and 0 otherwise, then we use these high PRI and high TRI in one probit
-regression and low TRI and low PRI in another. Results are presented in
-the following table.
-
-We observe higher uncertainty that stems from physical or transition
-risk causes antiherding which is in line with the logic we discussed
-earlier.
-
-\newpage
+we define values above median as high and below median as low. We define
+a dummy =1 if values\textgreater median and 0 otherwise and in this way
+we will have PRI values that are bigger than median and 0 otherwise. We
+also define a dummy which is lower than median, i.e., 1 and 0 otherwise,
+then we use these high PRI and high TRI in one probit regression and low
+TRI and low PRI in another. Results are presented in the following
+table. We observe higher uncertainty that stems from physical or
+transition risk causes anti-herding which is in line with the logic we
+discussed earlier.
 
@@
 \begin{longtable}[l]{|p{2.23in}|p{1.90in}|p{1.86in}}
-\caption{Estimation results of the probit model with high and low climate risk
-indexes (above or below median)}\tabularnewline
+
+\caption{\label{tbl-probit_analysis2}Estimation results of the probit
+model with high and low climate risk indexes (above or below median)}
+
+\tabularnewline
 
@@
 
-\newpage
+Results of baseline and rolling window analysis points to significant
+herding for the whole period and in various instances. \newpage
 
@@
 
+\setcounter{section}{0}
+\renewcommand{\thesection}{\Alph{section}}
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\newpage
+
+\section{Appendix}\label{appendix}
+
+\subsection{Data}\label{data-1}
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{0.5}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[l]{|p{5.39in}}
+
+\caption{\label{tbl-data}List of used alternative energy equity ETFs}
+
+\tabularnewline
+
+\ascline{1pt}{000000}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} \\
+
+\ascline{1pt}{000000}{1-1}\endfirsthead
+
+\ascline{1pt}{000000}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} \\
+
+\ascline{1pt}{000000}{1-1}\endhead
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ALPS\ CLEAN\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLUE\ HORIZON\ BNE\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ S\&P\ KENSHO\ CLEAN\ POWER\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ CLEANTECH\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{PROSHARES\ S\&P\ KENSHO\ CLEANTECH\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ MSCI\ SUSTAINABLE\ FUTURE\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIRST\ TRUST\ GLOBAL\ WIND\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIDELITY\ CLEAN\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLDS.BLOOMBERG\ CN.\ EN.\ EQ.ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ SMRT.GRID\ INFRA\ IDX\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DEFIANCE\ NEXT\ GEN\ H2\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DIREXION\ HYDROGEN\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ HYDROGEN\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ISHARES\ GLOBAL\ CLEAN\ EN.\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLACKR.WLD.EXUS\ CRBN\ TSTN.READINESS}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUB.CBN.TSTN.\&\ INFRA}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TCW\ TRANSFORM\ SYSTEMS\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ URANIUM\ AND\ NUCLEAR\ ENERGY}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUVEEN\ GLOBAL\ NET\ ZERO\ TRANSITION\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ MSCI\ USA\ CIM.\ PA.\ ALIGNED\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ GLOBAL\ CLEAN\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ GREY.ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ SOLAR\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ RENEWABLE\ ENERGY\ PRODUCERS}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TRUESHARES\ EAG.GLB.\ RENWEN.ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ LOW\ CARBON\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SMARTETFS\ SUST.EN.\ II\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ SOLAR\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VIRTUS\ DUFF\ \&\ PHELPS\ CLEAN\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-1}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ WIND\ ENERGY\ ETF}}}} \\
+
+\ascline{1pt}{000000}{1-1}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
 \end{document}

### 2024-10-10 alt_energy_herding.qmd
fixed table footers

@@
                       ft.align = "left",
-                      ft.arraystretch = 0.5
+                      ft.arraystretch = 0.7
                       )
@@
 #| tbl-cap: "Estimation results of herding in the U.S. equity alternative energy ETFs"
-#| cache: false
+#| cache: true
 #| ft.arraystretch: 0.9
@@
   mk_par(i = 1, part = "header", value = as_paragraph(as_equation(estimates))) %>% 
+    add_footer_lines(values = as_paragraph(
+    "Note: *,**,*** denotes significance at 10%,5% and 1% respectively."
+  )) %>% 
+  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
   autofit(add_w = 0.8)
@@
   mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
-  add_footer_lines(values = as_paragraph(
-    "This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (2) in various quantiles 10, 25, 50, 75 and 90% of the returns distribution.
-*,**,*** denotes significance at 10%,5% and 1% respectively."
-  )) %>% 
+  add_footer_row(values = as_paragraph("Note: This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation 2 in various quantiles 10, 25, 50, 75 and 90% of the returns distribution.", " ", "*,**,*** denotes significance at 10%,5% and 1% respectively."
+  ), colwidths = 4) %>% 
+  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
   autofit(add_w = 0.2)
@@
   mk_par(j = 1, part = "body", value = as_paragraph(as_equation(quantiles))) %>%
-  add_footer_lines(
-    values = as_paragraph(
-     "This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (3). *,**,***denotes significance at 10%,5% and 1% respectively."
-    )
+  add_footer_row(
+    values = as_paragraph("Note: This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (3).
+*,**,***denotes significance at 10%,5% and 1% respectively."
+    ),
+    colwidths = 6
   ) %>%
+   hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
   autofit(add_w = -0.2)
@@
 #| fig.cap: "Rolling window herding estimates"
-#| cache: false
+#| cache: true
 #| fig.width: 8
@@
 
+\newpage
+
 ```{r}
@@
   ) %>% 
+  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
   autofit(add_w = 1.5)
@@
   ) %>%
+  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
   autofit(add_w = 1.4)

### 2024-10-10 alt_energy_herding.tex
fixed table footers

@@
 
+\multicolumn{3}{>{\raggedright}m{\dimexpr 5.96in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+
+\ascline{1pt}{000000}{1-3}
+
 \end{longtable}
@@
 
-\renewcommand*{\arraystretch}{0.5}
+\renewcommand*{\arraystretch}{0.7}
 
@@
 
-\multicolumn{4}{>{\raggedright}m{\dimexpr 5.54in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (2)\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+\multicolumn{4}{>{\raggedright}m{\dimexpr 5.54in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ 2\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{*,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+
+\ascline{1pt}{000000}{1-4}
 
@@
 
-\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+
+\ascline{1pt}{000000}{1-6}
 
@@
 
+\newpage
+
 \global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
@@
 
+\ascline{1pt}{000000}{1-2}
+
 \end{longtable}
@@
 \multicolumn{3}{>{\raggedright}m{\dimexpr 5.99in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ *,\ denotes\ statistically\ significant\ at\ 10\%}}}} \\
+
+\ascline{1pt}{000000}{1-3}
 

### 2024-12-09 alt_energy_herding.qmd
cleaning up references

@@
 
-Argument: Investment interest on green ETFs has been explosive mainly by climate risks faced by the global economy and the actions of policy makers, goverments and organizations towards a sustainable future.
-
-Derived from @decclesia2024: Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs.
+Investment interest on green ETFs has been explosive mainly by climate risks faced by the global economy and the actions of policy makers, governments and organizations towards a sustainable future.
+Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024].
 The clean energy transition represents one of the largest multi-decade secular growth opportunities.
-
-From @naqvi2022: After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously.
+After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously [@naqvi2022].
 
@@
 The period of analysis runs from May 1^st^ of 2016 through 19^th^ June of 2024.
-The starting date was selected on the basis of the COP Paris agreement.
+The starting date was selected on the basis of the UN Climate Change Conference (COP) Paris agreement.
 Daily logarithmic returns were computed from the closing prices of ETFs for a total of 2122 observations.
@@
 
-Following the relevant literature we calculate the Cross Sectional Absolute Deviation  (CSAD) measure for each day in the following manner.
-We compute the difference of the ith ETF and market return where market return is proxied by the cross sectional average of returns for sample of our ETFs available for each day using @eq-csad:
+Following the relevant literature [@christie1995; and @chang2000], we compute dispersion of the $ith$ ETF from the market return.
+This is known as the Cross Sectional Absolute Deviation  ($CSAD_t$) measure.
+Empirically the $CSAD_t$ is defined in the following manner:
 
 $$
-CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|
+CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|,
 $$ {#eq-csad}
 
-```{r}
-#| label: cross_sectional_deviation
-#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
-#| fig.height: 4
-#| fig.width: 6
-#| cache: false
-
-```
-
-At a later stage we estimate a non-linear regression as in @galariotis2015:
+where $R_{i,t}$ is the return and $R_{m,t}$ is the cross sectional average of returns for the sample of ETFs available for each day.
+The return dispersion measures the directional similarity of ETF returns to the market return.
+This return similarity forms the basis for the herding behaviour tests.
+The CSAD measure for US Alternative Energy ETFs is presented in @fig-csad.
+Following @galariotis2015 we estimate @eq-herding:
 
 $$
-CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t
+CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
 $$ {#eq-herding}
 
-The testing procedure of herding relies on the above @eq-herding.
-Rational asset pricing models predict a linear relationship between return dispersion and market returns under normal conditions, a relationship that is no longer valid in the presence of herding.
-Herding behaviour leads to an increasing or decreasing cross sectional dispersion with respect to market returns.
-In other words, herding is captured by a non-linear term in the standard pricing equation indicating a decreasing or an increasing returns’ dispersion.
+where $\gamma_0$ is the intercept, $\gamma_1$ is the coefficient of the linear term, $\gamma_2$ is the coefficient of the quadratic term or the herding behaviour term, and $\epsilon_t$ is the error term.
+The coefficient $\gamma_2 <0$ when herding is present, and $\gamma_2 >0$  when anti-herding is present.
+To ensure the robustness of the estimate, we estimate $CSAD_{t}$ with Newey-West standard errors [See @newey1987].
 
@@
 $$
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
+CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}^2  + \gamma_4D R_{m,t}^2 + \epsilon_t,
 $$ {#eq-asymmetry}
@@
 where $D$ is a dummy variable that takes the value of 1 when the market return is negative and 0 otherwise.
-Therefore, our exploration of asymmetric behavior of herding phenomenon is carried through the inspection of the statistical significance and the sign of the two estimated coefficients $\gamma_3$ vs $\gamma_4$ (up vs down markets).
-
-\newpage
+Therefore, our exploration of asymmetric behaviour of herding phenomenon is carried through the inspection of the statistical significance and the sign of the two estimated coefficients $\gamma_3$ versus $\gamma_4$ (up versus down markets).
 
@@
 
-## General herding behaviour
-
-The behaviour of the CSAD measure for US Alternative Energy ETFs is presented in @fig-csad.
-
-```{r}
-#| label: fig-csad
-#| cache: false
-#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
-#| fig.height: 3
-#| fig.width: 8
-
-read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 1) %>% 
-  rename(Date = date,
-         "Cross Sectional Absolute Deviations" = CSAD) %>% 
-  dplyr::select(Date, `Cross Sectional Absolute Deviations`) %>% 
-  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
-  fx_plot() +
-  theme(
-    # change plot text size
-    text = element_text(size = 10),
-    plot.tag = element_text(size = 10)
-  )
-
-```
+## Herding behaviour
+Rational asset pricing models [for example, @black1972] predict a linear relationship between return dispersion and market returns under normal conditions, a relationship that is no longer valid in the presence of herding.
+Herding behaviour leads to an increasing or decreasing cross sectional dispersion with respect to market returns.
+In other words, herding is captured by a non-linear term in the standard pricing equation indicating a decreasing or an increasing returns’ dispersion.
 
@@
   hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
-  autofit(add_w = 0.2)
+  autofit(add_w = 0.3)
 
@@
 In general, we find that herding is more likely to occur in down markets than in up markets, which is indicative of the asymmetry of herding behaviour.
-
-\newpage
 
@@
 
-## Rolling window analysis
+## Herding behaviour over-time
 
@@
 #| label: fig-rolling_window
-#| fig.cap: "Rolling window herding estimates"
+#| fig.cap: "Rolling window herding estimates. Note: The red perforated lines indicates the 95% confidence interval."
 #| cache: true
@@
 
-## Probit analysis
+## Climate-related uncertainty and herding behaviour
 
@@
 Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.
-Given this, we define a dummy variable, which takes a value of 1 during periods of statistically significant herding (i.e., for days when the rolling t-statistic on $\gamma_2 < −1.96$) and zero otherwise, and then, we use a Probit model to relate this dummy to the two climate risk indexes developed by @bua2024.
-It should be noted that due to availability issues the probit analysis ends in December of 2023.
-The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.
-In other words, climate risks is good news for clean energy stocks or firms resulting in anti herding behaviour.
 
+We use a probit model to relate herding to the two climate risk indexes developed by @bua2024 in the following manner:
+
+$$
+Pr(D^{herd} = 1 |\lambda_0 +  \lambda_1TRI  + \lambda_2PRI) = \lambda_0 +  \lambda_1TRI  + \lambda_2PRI,
+$$ {#eq-climate}
+
+where $D^{herd}$ takes a value of 1 during periods of statistically significant herding (i.e., for days when the rolling t-statistic on $\gamma_2 < −1.96$ in @fig-rolling_window) and zero otherwise.
+$TRI$ is the transitional risk index and $PRI$ is the physical risk index.
+
+The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.^[It should be noted that due to availability issues the probit analysis ends in December of 2023.] In other words, climate risks is good news for clean energy stocks or firms resulting in anti-herding behaviour.
 This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products.
 As a result, the cross sectional dispersion of clean energy ETFs tends to increase.
-
-\newpage
 
@@
 
+lambda <- c(
+"\\lambda_0",
+"\\lambda_1",
+"\\lambda_2"
+)
+
 tribble(
   ~ "Variable", ~ "Coefficient",
-  "Transition Risk", "-4.607***",
-  "Physical Risk", "-1.318", 
-  "Constant", " -1.506***",
-  "LogL", "-484.7",
+  "lambda_0", " -1.506***",
+  "lambda_1", "-4.607***",
+  "lambda_2", "-1.318", 
+  "Log Likelihood", "-484.7",
   "Observations with Dependent Variable (Dep) = 0", "1816",
@@
   align(align = "left", j = 1, part = "all") %>%
+  mk_par(j = 1, i = c(1, 2, 3), part = "body", value = as_paragraph(as_equation(lambda))) %>% 
   add_footer_lines(
@@
   ) %>% 
+  hline(part = "body", i = 3, border = fp_border(color = "black", style = "solid", width = 1)) %>% 
   hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
@@
 
-Furthermore, suppose we get the median values of these two series.
-then we define values above median as high and below median as low.
-We define a dummy =1 if values>median and 0 otherwise and in this way we will have PRI values that are bigger than median and 0 otherwise.
-We also define a dummy which is lower than median, i.e., 1 and 0 otherwise, then we use these high PRI and high TRI in one probit regression and low TRI and low PRI in another.
-Results are presented in the following table.
-We observe higher uncertainty that stems from physical or transition risk causes anti-herding which is in line with the logic we discussed earlier.
+Furthermore, we develop two additional models to study the effect of climate risks on herding behaviour.
+We split the sample into two groups based on the median value of the TRI and PRI.
+We then estimate the following two models:
+
+$$
+Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI) = \lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI, and
+$$ {#eq-climate_high}
+
+$$
+Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI) = \lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI, 
+$$ {#eq-climate_low}
+
+where $D^{herd}$ is the same as in @eq-climate.
+$D^{TRI}_{high}$ and $D^{PRI}_{high}$ are dummy variables that take a value of 1 if the value of the TRI and PRI are above the median and zero otherwise.
+Similarly, $D^{TRI}_{low}$ and $D^{PRI}_{low}$ are dummy variables that take a value of 1 if the value of the TRI and PRI are below the median and zero otherwise.
+
+\newpage
 
@@
 #| cache: false
+
+lambda <- c(
+"\\lambda_1",
+"\\lambda_2"
+)
 
@@
   ) %>%
+  mk_par(j = 1, i = c(1, 2), part = "body", value = as_paragraph(as_equation(lambda))) %>% 
   hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
@@
 ```
+
+We use these high PRI and high TRI in one probit regression and low TRI and low PRI in another.
+Results are presented @tbl-probit_analysis2.
+We observe higher uncertainty that stems from physical or transition risk causes anti-herding which is in line with the logic we discussed earlier.
 
@@
 
-## Data
+## Cross-sectional average deviations
+
+```{r}
+#| label: fig-csad
+#| cache: false
+#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
+#| fig.height: 3
+#| fig.width: 8
+
+read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 1) %>% 
+  rename(Date = date,
+         "Cross Sectional Absolute Deviations" = CSAD) %>% 
+  dplyr::select(Date, `Cross Sectional Absolute Deviations`) %>% 
+  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
+  fx_plot() +
+  theme(
+    # change plot text size
+    text = element_text(size = 10),
+    plot.tag = element_text(size = 10)
+  )
+
+```
+
+## ETFs used in the study
 
@@
 #| label: tbl-data
-#| tbl-cap: "List of used alternative energy equity ETFs"
+#| tbl-cap: "List of green ETFs used in the study"
 #| cache: false
@@
   align(align = "left", j = 1,  part = "all") %>%
+  add_footer_row(values = as_paragraph("Note: Details on this funds can be found on Yahoo Finance."), colwidths = 1) %>% 
   autofit(add_w = 3)

### 2024-12-09 alt_energy_herding.tex
cleaning up references

@@
 \author { 
-Vassilios Babalos\footnote{Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
-Xolani Sibande\footnote{Corresponding Author.
-Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
+Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
+Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
 Economic Research Department, South African Reserve Bank, Pretoria, South Africa.} \,\,
-% Riza Demirer\footnote{Department of Economics and Finance, Southern Illinois University Edwardsville, Edwardsville, IL 62026-1102, USA; Email: rdemire@siue.edu} \,\,
+Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
 Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
@@
 
-Argument: Investment interest on green ETFs has been explosive mainly by
-climate risks faced by the global economy and the actions of policy
-makers, goverments and organizations towards a sustainable future.
-
-Derived from \citet{decclesia2024}: Among the ESG ETFs, the Clean Energy
-(CE) ETFs have been the best-performing ones in 2022, followed by the
-Cybersecurity and Artificial Intelligence (AI) ETFs. The clean energy
-transition represents one of the largest multi-decade secular growth
-opportunities.
-
-From \citet{naqvi2022}: After the inclusion of Green energy financing in
-the list of United Nations Sustainability Goals (SDGs) as SDG 7, the
-role, importance, and visibility of green financial products; all have
-escalated enormously.
+Investment interest on green ETFs has been explosive mainly by climate
+risks faced by the global economy and the actions of policy makers,
+governments and organizations towards a sustainable future. Among the
+ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones
+in 2022, followed by the Cybersecurity and Artificial Intelligence (AI)
+ETFs \citep{decclesia2024}. The clean energy transition represents one
+of the largest multi-decade secular growth opportunities. After the
+inclusion of Green energy financing in the list of United Nations
+Sustainability Goals (SDGs) as SDG 7, the role, importance, and
+visibility of green financial products; all have escalated enormously
+\citep{naqvi2022}.
 
@@
 1\textsuperscript{st} of 2016 through 19\textsuperscript{th} June of
-2024. The starting date was selected on the basis of the COP Paris
-agreement. Daily logarithmic returns were computed from the closing
-prices of ETFs for a total of 2122 observations.
+2024. The starting date was selected on the basis of the UN Climate
+Change Conference (COP) Paris agreement. Daily logarithmic returns were
+computed from the closing prices of ETFs for a total of 2122
+observations.
 
@@
 
-Following the relevant literature we calculate the Cross Sectional
-Absolute Deviation (CSAD) measure for each day in the following manner.
-We compute the difference of the ith ETF and market return where market
-return is proxied by the cross sectional average of returns for sample
-of our ETFs available for each day using Equation~\ref{eq-csad}:
+Following the relevant literature
+\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
+compute dispersion of the \(ith\) ETF from the market return. This is
+known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
+Empirically the \(CSAD_t\) is defined in the following manner:
 
 \begin{equation}\phantomsection\label{eq-csad}{
-CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|
+CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|,
 }\end{equation}
 
-At a later stage we estimate a non-linear regression as in
-\citet{galariotis2015}:
+where \(R_{i,t}\) is the return and \(R_{m,t}\) is the cross sectional
+average of returns for the sample of ETFs available for each day. The
+return dispersion measures the directional similarity of ETF returns to
+the market return. This return similarity forms the basis for the
+herding behaviour tests. The CSAD measure for US Alternative Energy ETFs
+is presented in Figure~\ref{fig-csad}. Following \citet{galariotis2015}
+we estimate Equation~\ref{eq-herding}:
 
 \begin{equation}\phantomsection\label{eq-herding}{
-CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t
+CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
 }\end{equation}
 
-The testing procedure of herding relies on the above
-Equation~\ref{eq-herding}. Rational asset pricing models predict a
-linear relationship between return dispersion and market returns under
-normal conditions, a relationship that is no longer valid in the
-presence of herding. Herding behaviour leads to an increasing or
-decreasing cross sectional dispersion with respect to market returns. In
-other words, herding is captured by a non-linear term in the standard
-pricing equation indicating a decreasing or an increasing returns'
-dispersion.
+where \(\gamma_0\) is the intercept, \(\gamma_1\) is the coefficient of
+the linear term, \(\gamma_2\) is the coefficient of the quadratic term
+or the herding behaviour term, and \(\epsilon_t\) is the error term. The
+coefficient \(\gamma_2 <0\) when herding is present, and \(\gamma_2 >0\)
+when anti-herding is present. To ensure the robustness of the estimate,
+we estimate \(CSAD_{t}\) with Newey-West standard errors
+\citep[See][]{newey1987}.
 
@@
 \begin{equation}\phantomsection\label{eq-asymmetry}{
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}  + \gamma_4D R_{m,t}^2 \epsilon_t
+CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}^2  + \gamma_4D R_{m,t}^2 + \epsilon_t,
 }\end{equation}
@@
 market return is negative and 0 otherwise. Therefore, our exploration of
-asymmetric behavior of herding phenomenon is carried through the
+asymmetric behaviour of herding phenomenon is carried through the
 inspection of the statistical significance and the sign of the two
-estimated coefficients \(\gamma_3\) vs \(\gamma_4\) (up vs down
+estimated coefficients \(\gamma_3\) versus \(\gamma_4\) (up versus down
 markets).
-
-\newpage
 
@@
 
-\subsection{General herding behaviour}\label{general-herding-behaviour}
+\subsection{Herding behaviour}\label{herding-behaviour}
 
-The behaviour of the CSAD measure for US Alternative Energy ETFs is
-presented in Figure~\ref{fig-csad}.
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
-
-}
-
-\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
-US Alternative Energy ETFs}
-
-\end{figure}%
+Rational asset pricing models \citep[for example,][]{black1972} predict
+a linear relationship between return dispersion and market returns under
+normal conditions, a relationship that is no longer valid in the
+presence of herding. Herding behaviour leads to an increasing or
+decreasing cross sectional dispersion with respect to market returns. In
+other words, herding is captured by a non-linear term in the standard
+pricing equation indicating a decreasing or an increasing returns'
+dispersion.
 
@@
 
-\begin{longtable}[l]{|p{1.39in}|p{1.39in}|p{1.39in}|p{1.39in}}
+\begin{longtable}[l]{|p{1.49in}|p{1.49in}|p{1.49in}|p{1.49in}}
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2536***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3736}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2536***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3736}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2461***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1056***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2461***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1056***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0037***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2648***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.165***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0037***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2648***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.165***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0048***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.3011***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1473***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0048***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.3011***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1473***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0064***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2999***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.2314}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0064***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2999***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.2314}}}} \\
 
@@
 
-\multicolumn{4}{>{\raggedright}m{\dimexpr 5.54in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ 2\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{*,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+\multicolumn{4}{>{\raggedright}m{\dimexpr 5.94in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ 2\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{*,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
 
@@
 indicative of the asymmetry of herding behaviour.
-
-\newpage
 
@@
 
-\subsection{Rolling window analysis}\label{rolling-window-analysis}
+\subsection{Herding behaviour
+over-time}\label{herding-behaviour-over-time}
 
@@
 
-\caption{\label{fig-rolling_window}Rolling window herding estimates}
+\caption{\label{fig-rolling_window}Rolling window herding estimates.
+Note: The red perforated lines indicates the 95\% confidence interval.}
 
@@
 
-\subsection{Probit analysis}\label{probit-analysis}
+\subsection{Climate-related uncertainty and herding
+behaviour}\label{climate-related-uncertainty-and-herding-behaviour}
 
@@
 study the effect of climate-related uncertainty on the formation of
-herding behavior in the clean energy market. Given this, we define a
-dummy variable, which takes a value of 1 during periods of statistically
+herding behavior in the clean energy market.
+
+We use a probit model to relate herding to the two climate risk indexes
+developed by \citet{bua2024} in the following manner:
+
+\begin{equation}\phantomsection\label{eq-climate}{
+Pr(D^{herd} = 1 |\lambda_0 +  \lambda_1TRI  + \lambda_2PRI) = \lambda_0 +  \lambda_1TRI  + \lambda_2PRI,
+}\end{equation}
+
+where \(D^{herd}\) takes a value of 1 during periods of statistically
 significant herding (i.e., for days when the rolling t-statistic on
-\(\gamma_2 < −1.96\)) and zero otherwise, and then, we use a Probit
-model to relate this dummy to the two climate risk indexes developed by
-\citet{bua2024}. It should be noted that due to availability issues the
-probit analysis ends in December of 2023. The results from the Probit
-model are reported in Table~\ref{tbl-probit_analysis}, where only the
-physical risk index significantly decreases the probability of herding.
-In other words, climate risks is good news for clean energy stocks or
-firms resulting in anti herding behaviour.
+\(\gamma_2 < −1.96\) in Figure~\ref{fig-rolling_window}) and zero
+otherwise. \(TRI\) is the transitional risk index and \(PRI\) is the
+physical risk index.
 
-This implies that in the presence of higher physical risk with respect
-to the climate, clean energy ETFs become a more attractive investment
-option for investors that allocate their money to the various
-alternative energy investment products. As a result, the cross sectional
-dispersion of clean energy ETFs tends to increase.
-
-\newpage
+The results from the Probit model are reported in
+Table~\ref{tbl-probit_analysis}, where only the physical risk index
+significantly decreases the probability of herding.\footnote{It should
+  be noted that due to availability issues the probit analysis ends in
+  December of 2023.} In other words, climate risks is good news for
+clean energy stocks or firms resulting in anti-herding behaviour. This
+implies that in the presence of higher physical risk with respect to the
+climate, clean energy ETFs become a more attractive investment option
+for investors that allocate their money to the various alternative
+energy investment products. As a result, the cross sectional dispersion
+of clean energy ETFs tends to increase.
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Constant}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
 
-\ascline{1pt}{FFFFFF}{1-2}
+\ascline{1pt}{000000}{1-2}
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{LogL}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
 
@@
 
-Furthermore, suppose we get the median values of these two series. then
-we define values above median as high and below median as low. We define
-a dummy =1 if values\textgreater median and 0 otherwise and in this way
-we will have PRI values that are bigger than median and 0 otherwise. We
-also define a dummy which is lower than median, i.e., 1 and 0 otherwise,
-then we use these high PRI and high TRI in one probit regression and low
-TRI and low PRI in another. Results are presented in the following
-table. We observe higher uncertainty that stems from physical or
-transition risk causes anti-herding which is in line with the logic we
-discussed earlier.
+Furthermore, we develop two additional models to study the effect of
+climate risks on herding behaviour. We split the sample into two groups
+based on the median value of the TRI and PRI. We then estimate the
+following two models:
+
+\begin{equation}\phantomsection\label{eq-climate_high}{
+Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI) = \lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI, and
+}\end{equation}
+
+\begin{equation}\phantomsection\label{eq-climate_low}{
+Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI) = \lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI, 
+}\end{equation}
+
+where \(D^{herd}\) is the same as in Equation~\ref{eq-climate}.
+\(D^{TRI}_{high}\) and \(D^{PRI}_{high}\) are dummy variables that take
+a value of 1 if the value of the TRI and PRI are above the median and
+zero otherwise. Similarly, \(D^{TRI}_{low}\) and \(D^{PRI}_{low}\) are
+dummy variables that take a value of 1 if the value of the TRI and PRI
+are below the median and zero otherwise.
+
+\newpage
 
@@
 
-\begin{longtable}[l]{|p{2.23in}|p{1.90in}|p{1.86in}}
+\begin{longtable}[l]{|p{2.59in}|p{1.90in}|p{1.86in}}
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Physical\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Transition\ Risk}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
 
@@
 
-\multicolumn{3}{>{\raggedright}m{\dimexpr 5.99in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ *,\ denotes\ statistically\ significant\ at\ 10\%}}}} \\
+\multicolumn{3}{>{\raggedright}m{\dimexpr 6.34in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ *,\ denotes\ statistically\ significant\ at\ 10\%}}}} \\
 
@@
 \renewcommand*{\arraystretch}{1}
+
+We use these high PRI and high TRI in one probit regression and low TRI
+and low PRI in another. Results are presented
+Table~\ref{tbl-probit_analysis2}. We observe higher uncertainty that
+stems from physical or transition risk causes anti-herding which is in
+line with the logic we discussed earlier.
 
@@
 
-\subsection{Data}\label{data-1}
+\subsection{Cross-sectional average
+deviations}\label{cross-sectional-average-deviations}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
+
+}
+
+\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
+US Alternative Energy ETFs}
+
+\end{figure}%
+
+\subsection{ETFs used in the study}\label{etfs-used-in-the-study}
 
@@
 
-\caption{\label{tbl-data}List of used alternative energy equity ETFs}
+\caption{\label{tbl-data}List of green ETFs used in the study}
 
@@
 
+\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ this\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\
+
 \end{longtable}

### 2024-12-10 alt_energy_herding.qmd
first couple of paragraphs

@@
 
-Investment interest on green ETFs has been explosive mainly by climate risks faced by the global economy and the actions of policy makers, governments and organizations towards a sustainable future.
+Climate sustainability has become a major concern for financial markets and investors.
+This growing interest is primary driven by the increasing materialisation of climate risks, and the actions of governments, institutions and organizations towards a sustainable future [@giglio2021a].
+In order to ensure returns investors increasingly seek to herd against climate risks by investing in green financial products.
+Although the evidence is mixed, indications that returns from green financial products are comparable to traditional financial [see amongst other, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
+Therefore, the growth of green assets-under-management is likely to continue.
+
+A key feature of the green financial products is the exchange traded funds (ETFs).
+ETFs are a type of security that involves a collection of securities—such as stocks—that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies.
+In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in companies that are environmentally friendly [@briere2023].
+Thus, ESG ETFs exhibit environment friendly characteristics.
+
 Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024].
@@
 After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously [@naqvi2022].
-
-# Literature review
 

### 2024-12-10 alt_energy_herding.tex
first couple of paragraphs

@@
 
-Investment interest on green ETFs has been explosive mainly by climate
-risks faced by the global economy and the actions of policy makers,
-governments and organizations towards a sustainable future. Among the
-ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones
-in 2022, followed by the Cybersecurity and Artificial Intelligence (AI)
-ETFs \citep{decclesia2024}. The clean energy transition represents one
-of the largest multi-decade secular growth opportunities. After the
-inclusion of Green energy financing in the list of United Nations
-Sustainability Goals (SDGs) as SDG 7, the role, importance, and
-visibility of green financial products; all have escalated enormously
-\citep{naqvi2022}.
+Climate sustainability has become a major concern for financial markets
+and investors. This growing interest is primary driven by the increasing
+materialisation of climate risks, and the actions of governments,
+institutions and organizations towards a sustainable future
+\citep{giglio2021a}. In order to ensure returns investors increasingly
+seek to herd against climate risks by investing in green financial
+products. Although the evidence is mixed, indications that returns from
+green financial products are comparable to traditional financial
+\citetext{\citealp[see amongst
+other,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
+Therefore, the growth of green assets-under-management is likely to
+continue.
 
-\section{Literature review}\label{literature-review}
+A key feature of the green financial products is the exchange traded
+funds (ETFs). ETFs are a type of security that involves a collection of
+securities---such as stocks---that often tracks an underlying index,
+although they can invest in any number of industry sectors or use
+various strategies. In addition, environment, social, and governance
+(ESG) ETFs serve as a market discovery tool for investors to identify
+and invest in companies that are environmentally friendly
+\citep{briere2023}. Thus, ESG ETFs exhibit environment friendly
+characteristics.
+
+Among the ESG ETFs, the Clean Energy (CE) ETFs have been the
+best-performing ones in 2022, followed by the Cybersecurity and
+Artificial Intelligence (AI) ETFs \citep{decclesia2024}. The clean
+energy transition represents one of the largest multi-decade secular
+growth opportunities. After the inclusion of Green energy financing in
+the list of United Nations Sustainability Goals (SDGs) as SDG 7, the
+role, importance, and visibility of green financial products; all have
+escalated enormously \citep{naqvi2022}.
 

### 2024-12-22 alt_energy_herding.qmd
new lit

@@
 A key feature of the green financial products is the exchange traded funds (ETFs).
-ETFs are a type of security that involves a collection of securities—such as stocks—that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies.
+ETFs are a type of security that involves a collection of securities that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies.
 In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in companies that are environmentally friendly [@briere2023].
@@
 The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies.
-There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets \textcolor{red}{(see inter alia….)}.
+There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets.
 @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.
@@
 Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.
+
+@choi2023
+@kuang2021
+
 \newpage

### 2024-12-22 alt_energy_herding.tex
new lit

@@
 funds (ETFs). ETFs are a type of security that involves a collection of
-securities---such as stocks---that often tracks an underlying index,
-although they can invest in any number of industry sectors or use
-various strategies. In addition, environment, social, and governance
-(ESG) ETFs serve as a market discovery tool for investors to identify
-and invest in companies that are environmentally friendly
-\citep{briere2023}. Thus, ESG ETFs exhibit environment friendly
-characteristics.
+securities that often tracks an underlying index, although they can
+invest in any number of industry sectors or use various strategies. In
+addition, environment, social, and governance (ESG) ETFs serve as a
+market discovery tool for investors to identify and invest in companies
+that are environmentally friendly \citep{briere2023}. Thus, ESG ETFs
+exhibit environment friendly characteristics.
 
@@
 to quantify the effects of uncertainty related to climate on the economy
-and financial markets \textcolor{red}{(see inter alia….)}.
-\citet{bua2024} developed two climate risk related indexes namely
-transition and physical risk using a text-based approach in order to
-study the effect of these risks in financial markets. It is expected
-that investors would prefer to hold assets that perform well in the face
-of increasing climate change risks, even if this entails accepting lower
-returns for such climate-hedging assets. Therefore, in the context of
-our study and following previous studies that study the determinants of
-herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
-study the effect of climate-related uncertainty on the formation of
-herding behavior in the clean energy market.
+and financial markets. \citet{bua2024} developed two climate risk
+related indexes namely transition and physical risk using a text-based
+approach in order to study the effect of these risks in financial
+markets. It is expected that investors would prefer to hold assets that
+perform well in the face of increasing climate change risks, even if
+this entails accepting lower returns for such climate-hedging assets.
+Therefore, in the context of our study and following previous studies
+that study the determinants of herding behaviour
+\citep[see][]{bouri2019, demirer2018}, we attempt to study the effect of
+climate-related uncertainty on the formation of herding behavior in the
+clean energy market.
 
@@
 Results of baseline and rolling window analysis points to significant
-herding for the whole period and in various instances. \newpage
+herding for the whole period and in various instances.
+
+\citet{choi2023} \citet{kuang2021}
+
+\newpage
 

### 2025-01-02 alt_energy_herding.qmd
positron test
improved introduction and literature review

@@
 title-block-style: none
+render-on-save: true
 ---
@@
 
-# Introduction
+# Introduction and literature review
 
@@
 This growing interest is primary driven by the increasing materialisation of climate risks, and the actions of governments, institutions and organizations towards a sustainable future [@giglio2021a].
-In order to ensure returns investors increasingly seek to herd against climate risks by investing in green financial products.
-Although the evidence is mixed, indications that returns from green financial products are comparable to traditional financial [see amongst other, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
-Therefore, the growth of green assets-under-management is likely to continue.
+In order to ensure returns, investors increasingly seek to hedge against climate risks by investing in green financial products.
+Although there evidence is mixed, indications that returns from green financial products are comparable to traditional financial [see amongst others, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
 
-A key feature of the green financial products is the exchange traded funds (ETFs).
+Specifically, climate change present risk to investor portfolios through two primary sources, physical and transition risks.
+physical risks or direct impact refer to extreme climate events such as floods and droughts, which impact business operations and infrastructure; and transition risks are the policy, technological, and other costs that societies bear to achieve low carbon economies [@nguyen2025; and @giglio2021a amongst others].
+Investors, therefore, recognise these risk and seek to mitigate against them, as they seek return enhancing green financial products.
+
+Exchange traded funds (ETFs) are a key feature of green financial products.
 ETFs are a type of security that involves a collection of securities that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies.
 In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in companies that are environmentally friendly [@briere2023].
-Thus, ESG ETFs exhibit environment friendly characteristics.
-
 Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024].
@@
 After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously [@naqvi2022].
+Therefore, the growth of green assets-under-management is likely to continue.
+
+\newpage
+In this new climate sustainability paradigm, investors face many pressures that not only bear on returns, but also on the stability of financial markets.
+For example, resulting regulations aimed at reducing emissions can surprisingly reduce the profitability of fossil-fuel based companies, or the possible mispricing of assets from ignoring climate risks can lead to significant losses [@nguyen2025].
+In addition to these climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio leading to systemic risk.
+These pressures are not withstanding the possible contribution that financial markets can play in mitigating and reducing the negative effects of climate change [@giglio2021a].
+
+However, given how recent the inclusion of climate sustainability investment decisions is, it is not clear what the actual impact will be in the long run.
+In this study specifically, we ask whether the rapid adoption of CE ETFs could be driven a market fad driven by herding behaviour, or is a fundamental change in investor behaviour?
+Investors, for example, can believe that peers have information about climate risks that they do not, investors may herd to avoid losses compared to peers, or investors may be encouraged to herd by the desire to align to climate related social values [@ciciretti2021; @gavrilakis2023; @loang2023].
+Therefore, market volatility and crisis, financial performance, and investor sentiment can be drivers of herding in ESG markets
+
+Although the overall evidence is mixed, herding behaviour in ESG markets is not without precedent.
+Amongst others, @loang2023 found that compliance with SDG goals can introduce bias in investor sentiment, which lead to herding behaviour.
+Using a Twitter (or X) uncertainty index, @koutmos2024 found evidence of herding in US-based ESG index fund investors.
+@przychodzen2016 found herding behaviour amongst fund managers who incorporated ESG strategies in their portfolios.
+Lastly, @rubbaniy2021 highlight evidence of herding in the MSCI US ESG Leader Index during extreme periods (bear and bull periods).
 
@@
 
-Following the relevant literature [@christie1995; and @chang2000], we compute dispersion of the $ith$ ETF from the market return.
+Following the relevant literature [@christie1995; and @chang2000], we compute dispersion of the $i^{th}$ ETF from the market return.
 This is known as the Cross Sectional Absolute Deviation  ($CSAD_t$) measure.

### 2025-01-02 alt_energy_herding.tex
improved introduction and literature review

@@
 \setstretch{1.5}
-\section{Introduction}\label{introduction}
+\section{Introduction and literature
+review}\label{introduction-and-literature-review}
 
@@
 institutions and organizations towards a sustainable future
-\citep{giglio2021a}. In order to ensure returns investors increasingly
-seek to herd against climate risks by investing in green financial
-products. Although the evidence is mixed, indications that returns from
-green financial products are comparable to traditional financial
+\citep{giglio2021a}. In order to ensure returns, investors increasingly
+seek to hedge against climate risks by investing in green financial
+products. Although there evidence is mixed, indications that returns
+from green financial products are comparable to traditional financial
 \citetext{\citealp[see amongst
-other,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
-Therefore, the growth of green assets-under-management is likely to
-continue.
-
-A key feature of the green financial products is the exchange traded
-funds (ETFs). ETFs are a type of security that involves a collection of
+others,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
+
+Specifically, climate change present risk to investor portfolios through
+two primary sources, physical and transition risks. physical risks or
+direct impact refer to extreme climate events such as floods and
+droughts, which impact business operations and infrastructure; and
+transition risks are the policy, technological, and other costs that
+societies bear to achieve low carbon economies
+\citetext{\citealp{nguyen2025}; \citealp[and][ amongst
+others]{giglio2021a}}. Investors, therefore, recognise these risk and
+seek to mitigate against them, as they seek return enhancing green
+financial products.
+
+Exchange traded funds (ETFs) are a key feature of green financial
+products. ETFs are a type of security that involves a collection of
 securities that often tracks an underlying index, although they can
@@
 market discovery tool for investors to identify and invest in companies
-that are environmentally friendly \citep{briere2023}. Thus, ESG ETFs
-exhibit environment friendly characteristics.
-
-Among the ESG ETFs, the Clean Energy (CE) ETFs have been the
-best-performing ones in 2022, followed by the Cybersecurity and
-Artificial Intelligence (AI) ETFs \citep{decclesia2024}. The clean
-energy transition represents one of the largest multi-decade secular
-growth opportunities. After the inclusion of Green energy financing in
-the list of United Nations Sustainability Goals (SDGs) as SDG 7, the
-role, importance, and visibility of green financial products; all have
-escalated enormously \citep{naqvi2022}.
+that are environmentally friendly \citep{briere2023}. Among the ESG
+ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in
+2022, followed by the Cybersecurity and Artificial Intelligence (AI)
+ETFs \citep{decclesia2024}. The clean energy transition represents one
+of the largest multi-decade secular growth opportunities. After the
+inclusion of Green energy financing in the list of United Nations
+Sustainability Goals (SDGs) as SDG 7, the role, importance, and
+visibility of green financial products; all have escalated enormously
+\citep{naqvi2022}. Therefore, the growth of green
+assets-under-management is likely to continue.
+
+\newpage
+
+In this new climate sustainability paradigm, investors face many
+pressures that not only bear on returns, but also on the stability of
+financial markets. For example, resulting regulations aimed at reducing
+emissions can surprisingly reduce the profitability of fossil-fuel based
+companies, or the possible mispricing of assets from ignoring climate
+risks can lead to significant losses \citep{nguyen2025}. In addition to
+these climate risks, a general change in investor attitudes can drive
+the inclusion of green assets in their portfolio leading to systemic
+risk. These pressures are not withstanding the possible contribution
+that financial markets can play in mitigating and reducing the negative
+effects of climate change \citep{giglio2021a}.
+
+However, given how recent the inclusion of climate sustainability
+investment decisions is, it is not clear what the actual impact will be
+in the long run. In this study specifically, we ask whether the rapid
+adoption of CE ETFs could be driven a market fad driven by herding
+behaviour, or is a fundamental change in investor behaviour? Investors,
+for example, can believe that peers have information about climate risks
+that they do not, investors may herd to avoid losses compared to peers,
+or investors may be encouraged to herd by the desire to align to climate
+related social values \citep{ciciretti2021, gavrilakis2023, loang2023}.
+Therefore, market volatility and crisis, financial performance, and
+investor sentiment can be drivers of herding in ESG markets
+
+Although the overall evidence is mixed, herding behaviour in ESG markets
+is not without precedent. Amongst others, \citet{loang2023} found that
+compliance with SDG goals can introduce bias in investor sentiment,
+which lead to herding behaviour. Using a Twitter (or X) uncertainty
+index, \citet{koutmos2024} found evidence of herding in US-based ESG
+index fund investors. \citet{przychodzen2016} found herding behaviour
+amongst fund managers who incorporated ESG strategies in their
+portfolios. Lastly, \citet{rubbaniy2021} highlight evidence of herding
+in the MSCI US ESG Leader Index during extreme periods (bear and bull
+periods).
 
@@
 \citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
-compute dispersion of the \(ith\) ETF from the market return. This is
+compute dispersion of the \(i^{th}\) ETF from the market return. This is
 known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.

### 2025-01-03 alt_energy_herding.qmd
complete introduction and literature review.

--- 2024-12-22 alt_energy_herding.qmd
@@
 
-# Introduction
+# Introduction and literature review
 
-Climate sustainability has become a major concern for financial markets and investors.
-This growing interest is primary driven by the increasing materialisation of climate risks, and the actions of governments, institutions and organizations towards a sustainable future [@giglio2021a].
-In order to ensure returns investors increasingly seek to herd against climate risks by investing in green financial products.
-Although the evidence is mixed, indications that returns from green financial products are comparable to traditional financial [see amongst other, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
-Therefore, the growth of green assets-under-management is likely to continue.
+Climate sustainability is a major concern for financial markets and investors.
+The growing interest in climate sustainability is primarily driven by the increasing materialisation of climate risks, and the actions of governments, institutions and organizations towards a sustainable future [@giglio2021a].
+To ensure returns, investors increasingly seek to hedge against climate risks by investing in green financial products.
+Although the evidence is mixed, indications that returns from green financial products are comparable to traditional financial [see amongst others, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
 
-A key feature of the green financial products is the exchange traded funds (ETFs).
-ETFs are a type of security that involves a collection of securities that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies.
-In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in companies that are environmentally friendly [@briere2023].
-Thus, ESG ETFs exhibit environment friendly characteristics.
+In this new climate sustainability paradigm, investors face many pressures that not only bear on returns but also the stability of financial markets.
+For example, resulting regulations aimed at reducing emissions can surprisingly reduce the profitability of fossil-fuel-based companies, or the possible mispricing of assets from ignoring climate risks can lead to significant losses [@nguyen2025].
+In addition to these climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio leading to systemic risk.^[These pressures notwithstanding the possible contribution that financial markets can play in mitigating and reducing the negative effects of climate change [@giglio2021a].
 
+Specifically, climate change presents risks to investor portfolios through two primary sources - physical and transition risks.
+Physical risks or direct impact refer to extreme climate events such as floods and droughts, which impact business operations and infrastructure; and transition risks are the policy, technological, and other costs that societies bear to achieve low carbon economies [@nguyen2025; and @giglio2021a amongst others].
+Investors, therefore, recognise these risks and seek to mitigate them, as they seek return-enhancing green financial products.
+
+Exchange-traded funds (ETFs) are a key feature of green financial products.
+ETFs are a type of security that involves a collection of securities that often tracks an underlying index.
+However, they can invest in various industry sectors or strategies.
+In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in environmentally friendly companies [@briere2023].
 Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024].
@@
 After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously [@naqvi2022].
+Therefore, the growth of green assets under management is likely to continue.
+
+However, given how recent the inclusion of climate sustainability investment decisions is, it is not clear what the actual impact will be in the long run.
+In this study specifically, we ask whether the rapid adoption of CE ETFs could be driven by market fads, or is a fundamental change in investor behaviour.
+Investors, for example, can believe that peers have information about climate risks that they do not, investors may herd to avoid losses compared to peers, or investors may be encouraged to herd by the desire to align to climate-related social values [@ciciretti2021; @gavrilakis2023; @loang2023].
+Therefore, market volatility and crisis, financial performance, and investor sentiment can drive herding in ESG markets.
+
+Herding behaviour in ESG markets is not without precedent.
+Amongst others, @loang2023 found that compliance with SDG goals can introduce bias in investor sentiment, which leads to herding behaviour.
+Using a Twitter (or X) uncertainty index, @koutmos2024 found evidence of herding in US-based ESG index fund investors.
+@przychodzen2016 found herding behaviour amongst fund managers who incorporated ESG strategies in their portfolios.
+Lastly, @rubbaniy2021 highlight evidence of herding in the MSCI US ESG Leader Index during extreme periods (bear and bull periods).
+
+However, to the best of our knowledge, no studies exist that focus on herding behaviour in CE ESGs.
+This study, therefore, aims to extend the broader literature on herding behaviour in commodity and energy markets.
+Several studies in this area were conducted.
+For example, @demirer2013a conducted a sector study and found herding behaviour in grains but not in other sectors.
+Similarly, @gilbert2010 showed herding behaviour amongst speculators in non-ferrous commodities.
+Others did not find evidence of herding in similar markets.
+@babalos2015 found significant anti-herding behaviour in metal commodities futures after the global financial crisis.
+@pierdzioch2010 showed that forecasters in oil and metals markets deviated from the crowd, indicating a rational response to information.
+@steen2013 also found no herding behaviour in international commodity markets.
+Overall, the literature in this area is mixed, which indicates scope for further study.
+
+Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2019 and 2024.
+We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets.
+Methodologically, we follow the standard herding tests by @christie1995 and @chang2000.
+The traditional approach was supplemented by quantile regressions [@koenker1978 ] in order to capture the time-varying aspects of herding.
+Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour.
+The next section describes the data and methodology, followed by the results and conclusions.
 

### 2025-01-03 alt_energy_herding.tex
complete introduction and literature review.

--- 2024-12-22 alt_energy_herding.tex
@@
 \setstretch{1.5}
-\section{Introduction}\label{introduction}
-
-Climate sustainability has become a major concern for financial markets
-and investors. This growing interest is primary driven by the increasing
-materialisation of climate risks, and the actions of governments,
-institutions and organizations towards a sustainable future
-\citep{giglio2021a}. In order to ensure returns investors increasingly
-seek to herd against climate risks by investing in green financial
-products. Although the evidence is mixed, indications that returns from
-green financial products are comparable to traditional financial
-\citetext{\citealp[see amongst
-other,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
-Therefore, the growth of green assets-under-management is likely to
+\section{Introduction and literature
+review}\label{introduction-and-literature-review}
+
+Climate sustainability is a major concern for financial markets and
+investors. The growing interest in climate sustainability is primarily
+driven by the increasing materialisation of climate risks, and the
+actions of governments, institutions and organizations towards a
+sustainable future \citep{giglio2021a}. To ensure returns, investors
+increasingly seek to hedge against climate risks by investing in green
+financial products. Although the evidence is mixed, indications that
+returns from green financial products are comparable to traditional
+financial \citetext{\citealp[see amongst
+others,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
+
+In this new climate sustainability paradigm, investors face many
+pressures that not only bear on returns but also the stability of
+financial markets. For example, resulting regulations aimed at reducing
+emissions can surprisingly reduce the profitability of fossil-fuel-based
+companies, or the possible mispricing of assets from ignoring climate
+risks can lead to significant losses \citep{nguyen2025}. In addition to
+these climate risks, a general change in investor attitudes can drive
+the inclusion of green assets in their portfolio leading to systemic
+risk.\^{}{[}These pressures notwithstanding the possible contribution
+that financial markets can play in mitigating and reducing the negative
+effects of climate change \citep{giglio2021a}.
+
+Specifically, climate change presents risks to investor portfolios
+through two primary sources - physical and transition risks. Physical
+risks or direct impact refer to extreme climate events such as floods
+and droughts, which impact business operations and infrastructure; and
+transition risks are the policy, technological, and other costs that
+societies bear to achieve low carbon economies
+\citetext{\citealp{nguyen2025}; \citealp[and][ amongst
+others]{giglio2021a}}. Investors, therefore, recognise these risks and
+seek to mitigate them, as they seek return-enhancing green financial
+products.
+
+Exchange-traded funds (ETFs) are a key feature of green financial
+products. ETFs are a type of security that involves a collection of
+securities that often tracks an underlying index. However, they can
+invest in various industry sectors or strategies. In addition,
+environment, social, and governance (ESG) ETFs serve as a market
+discovery tool for investors to identify and invest in environmentally
+friendly companies \citep{briere2023}. Among the ESG ETFs, the Clean
+Energy (CE) ETFs have been the best-performing ones in 2022, followed by
+the Cybersecurity and Artificial Intelligence (AI) ETFs
+\citep{decclesia2024}. The clean energy transition represents one of the
+largest multi-decade secular growth opportunities. After the inclusion
+of Green energy financing in the list of United Nations Sustainability
+Goals (SDGs) as SDG 7, the role, importance, and visibility of green
+financial products; all have escalated enormously \citep{naqvi2022}.
+Therefore, the growth of green assets under management is likely to
 continue.
 
-A key feature of the green financial products is the exchange traded
-funds (ETFs). ETFs are a type of security that involves a collection of
-securities that often tracks an underlying index, although they can
-invest in any number of industry sectors or use various strategies. In
-addition, environment, social, and governance (ESG) ETFs serve as a
-market discovery tool for investors to identify and invest in companies
-that are environmentally friendly \citep{briere2023}. Thus, ESG ETFs
-exhibit environment friendly characteristics.
-
-Among the ESG ETFs, the Clean Energy (CE) ETFs have been the
-best-performing ones in 2022, followed by the Cybersecurity and
-Artificial Intelligence (AI) ETFs \citep{decclesia2024}. The clean
-energy transition represents one of the largest multi-decade secular
-growth opportunities. After the inclusion of Green energy financing in
-the list of United Nations Sustainability Goals (SDGs) as SDG 7, the
-role, importance, and visibility of green financial products; all have
-escalated enormously \citep{naqvi2022}.
+However, given how recent the inclusion of climate sustainability
+investment decisions is, it is not clear what the actual impact will be
+in the long run. In this study specifically, we ask whether the rapid
+adoption of CE ETFs could be driven by market fads, or is a fundamental
+change in investor behaviour. Investors, for example, can believe that
+peers have information about climate risks that they do not, investors
+may herd to avoid losses compared to peers, or investors may be
+encouraged to herd by the desire to align to climate-related social
+values \citep{ciciretti2021, gavrilakis2023, loang2023}. Therefore,
+market volatility and crisis, financial performance, and investor
+sentiment can drive herding in ESG markets.
+
+Herding behaviour in ESG markets is not without precedent. Amongst
+others, \citet{loang2023} found that compliance with SDG goals can
+introduce bias in investor sentiment, which leads to herding behaviour.
+Using a Twitter (or X) uncertainty index, \citet{koutmos2024} found
+evidence of herding in US-based ESG index fund investors.
+\citet{przychodzen2016} found herding behaviour amongst fund managers
+who incorporated ESG strategies in their portfolios. Lastly,
+\citet{rubbaniy2021} highlight evidence of herding in the MSCI US ESG
+Leader Index during extreme periods (bear and bull periods).
+
+However, to the best of our knowledge, no studies exist that focus on
+herding behaviour in CE ESGs. This study, therefore, aims to extend the
+broader literature on herding behaviour in commodity and energy markets.
+Several studies in this area were conducted. For example,
+\citet{demirer2013a} conducted a sector study and found herding
+behaviour in grains but not in other sectors. Similarly,
+\citet{gilbert2010} showed herding behaviour amongst speculators in
+non-ferrous commodities. Others did not find evidence of herding in
+similar markets. \citet{babalos2015} found significant anti-herding
+behaviour in metal commodities futures after the global financial
+crisis. \citet{pierdzioch2010} showed that forecasters in oil and metals
+markets deviated from the crowd, indicating a rational response to
+information. \citet{steen2013} also found no herding behaviour in
+international commodity markets. Overall, the literature in this area is
+mixed, which indicates scope for further study.
+
+Therefore, this study investigates herding behaviour in alternative
+energy ETFs in the US between 2019 and 2024. We then demonstrate how
+climate-related uncertainty can drive herding behaviour in these
+markets. Methodologically, we follow the standard herding tests by
+\citet{christie1995} and \citet{chang2000}. The traditional approach was
+supplemented by quantile regressions \citep[ ]{koenker1978} in order to
+capture the time-varying aspects of herding. Lastly, we extend recent
+approaches by \citet{bua2024} and others, which seek to establish a link
+between climate uncertainty and herding behaviour. The next section
+describes the data and methodology, followed by the results and
+conclusions.
 

### 2025-01-07 alt_energy_herding.qmd
complete draft

@@
 For example, resulting regulations aimed at reducing emissions can surprisingly reduce the profitability of fossil-fuel-based companies, or the possible mispricing of assets from ignoring climate risks can lead to significant losses [@nguyen2025].
-In addition to these climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio leading to systemic risk.^[These pressures notwithstanding the possible contribution that financial markets can play in mitigating and reducing the negative effects of climate change [@giglio2021a].
+In addition to these climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio can lead to systemic risk.^[These pressures notwithstanding the possible contribution that financial markets can play in mitigating and reducing the negative effects of climate change [@giglio2021a]]
 
@@
 The clean energy transition represents one of the largest multi-decade secular growth opportunities.
-After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products; all have escalated enormously [@naqvi2022].
-Therefore, the growth of green assets under management is likely to continue.
+After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products have escalated enormously [@naqvi2022].
+That is, the growth of green assets under management is likely to continue.
 
-However, given how recent the inclusion of climate sustainability investment decisions is, it is not clear what the actual impact will be in the long run.
+However, given how recent the inclusion of climate sustainability in investment decisions is, it is not clear what the actual impact will be in the long run.
 In this study specifically, we ask whether the rapid adoption of CE ETFs could be driven by market fads, or is a fundamental change in investor behaviour.
@@
 Several studies in this area were conducted.
-For example, @demirer2013a conducted a sector study and found herding behaviour in grains but not in other sectors.
+For example, @demirer2013a conducted a commodity sectoral study and found herding behaviour in grains but not in other sectors.
 Similarly, @gilbert2010 showed herding behaviour amongst speculators in non-ferrous commodities.
@@
 @babalos2015 found significant anti-herding behaviour in metal commodities futures after the global financial crisis.
-@pierdzioch2010 showed that forecasters in oil and metals markets deviated from the crowd, indicating a rational response to information.
+@pierdzioch2010 showed that forecasters in oil and metals markets deviated from the crowd, indicating a rational response to market information.
 @steen2013 also found no herding behaviour in international commodity markets.
@@
 @tbl-herding presents the results of herding for the full sample employing the non-linear @eq-herding.
-The estimated coefficient on market return is positive and highly significant as expected.The estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behaviour is present and robust in the US alternative energy ETFs.
+The estimated coefficient on market return is positive and highly significant as expected.
+The estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behaviour is present and robust in the US alternative energy ETFs.
 
@@
 There is ample evidence in the relevant literature that herding behaviour in various asset markets [see @pochea2017] exhibits asymmetry and time-varying characteristics.
-To this end, we proceed to estimate @eq-herding using the quantile regression (QR) proposed by @koenker1978 and @tbl-quantile_herding presents the results of estimating @eq-herding across various quantiles of the returns dispersion.
+To this end, we proceed to estimate @eq-herding using the quantile regression (QR) proposed by @koenker1978.
+@tbl-quantile_herding presents the results of estimating @eq-herding across various quantiles of the returns dispersion.
 Our focus is on the herding coefficient $\gamma_2$, as a significant negative value of $\gamma_2$ is indicative of herding.
@@
 
-Herding is present at low quantiles when markets are rising with an estimated coefficient $\gamma_3$ of -1.3669 and -1.2383 and highly significant respectively.
+Herding is present at all quantiles when markets are rising with an estimated coefficient $\gamma_3$ of -1.3669 and -1.2383 and highly significant respectively.
 However, when markets are declining, investors seem to neglect their own information set and imitate the actions of others resulting in a highly significant coefficient of herding ($\gamma_4$) across four out of five quantiles.
@@
 We use these high PRI and high TRI in one probit regression and low TRI and low PRI in another.
-Results are presented @tbl-probit_analysis2.
+Results are presented in @tbl-probit_analysis2.
 We observe higher uncertainty that stems from physical or transition risk causes anti-herding which is in line with the logic we discussed earlier.
@@
 
-This study offers novel and valuable insights on herding behavior in clean energy ETFs.
-
-Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.
-
-@choi2023
-@kuang2021
+This study offers novel and valuable insights into herding behaviour in clean energy ETFs.
+We used various herding behaviour tests to achieve this.
+First, the baseline herding tests revealed significant evidence of herding behaviour.
+Second, the asymmetric herding tests showed that herding behaviour was present in both bear and bull markets.
+Lastly, the results of the time-varying tests point to significant periodic herding.
+However, the results further indicate that herding in US clean energy ETFs was not mainly related to climate-related risks or uncertainty.
+The probit analysis showed that climate-related uncertainty reduced the probability of herding or led to investor anti-herding behaviour.
+We defer to the literature on the factors that drive herding in these ETFs [for example, @loang2023;  @koutmos2024; @przychodzen2016].
+Our results, similar to @bua2024, indicate that investors did not herd on climate-related uncertainty, and sought returns whilst hedging against climate-related risk.
+This is a positive for the financial stability of these growing alternative investment indices.
 

### 2025-01-07 alt_energy_herding/alt_energy_herding.tex
complete draft

--- 2025-01-03 alt_energy_herding.tex
@@
 
-\author { 
+\author{ 
 Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
@@
 
-ipsum
+This study offers novel and valuable insights into herding behaviour in US clean energy ETFs between 2016 and 2023. 
+The baseline herding tests by \cite{christie1995} and \cite{chang2000} revealed significant herding behaviour in this market. 
+This evidence was supported by asymmetric and time-varying herding tests. That is, investors herd both in bear and bullish markets, and periodically. 
+In addition, we found that climate risks (both physical and transition) reduced the probability of herding in US clean energy ETFs, 
+indicating that an increase in climate-related risk encouraged efficient or climate-hedging behaviour by investors. 
+Therefore, the results suggest that climate-related uncertainty did not drive herding behaviour in this market.
+The results suggest that investors are appropriately identifying opportunities that mitigate climate risk,
+thereby reducing the probability of herding-driven system risk.
 
@@
 
-\noindent\textbf{Keywords}: Herding Behaviour, Financial Crises, Market Efficiency
+\noindent\textbf{Keywords}: Herding Behaviour, Climate Change, Energy
 \\
-\textbf{JEL Codes}: G01, G14, G15, G41
+\textbf{JEL Codes}: G14, Q54, P18
 \newpage
@@
 these climate risks, a general change in investor attitudes can drive
-the inclusion of green assets in their portfolio leading to systemic
-risk.\^{}{[}These pressures notwithstanding the possible contribution
-that financial markets can play in mitigating and reducing the negative
-effects of climate change \citep{giglio2021a}.
+the inclusion of green assets in their portfolio can lead to systemic
+risk.\footnote{These pressures notwithstanding the possible contribution
+  that financial markets can play in mitigating and reducing the
+  negative effects of climate change \citep{giglio2021a}}
 
@@
 Goals (SDGs) as SDG 7, the role, importance, and visibility of green
-financial products; all have escalated enormously \citep{naqvi2022}.
-Therefore, the growth of green assets under management is likely to
-continue.
-
-However, given how recent the inclusion of climate sustainability
+financial products have escalated enormously \citep{naqvi2022}. That is,
+the growth of green assets under management is likely to continue.
+
+However, given how recent the inclusion of climate sustainability in
 investment decisions is, it is not clear what the actual impact will be
@@
 Several studies in this area were conducted. For example,
-\citet{demirer2013a} conducted a sector study and found herding
-behaviour in grains but not in other sectors. Similarly,
+\citet{demirer2013a} conducted a commodity sectoral study and found
+herding behaviour in grains but not in other sectors. Similarly,
 \citet{gilbert2010} showed herding behaviour amongst speculators in
@@
 markets deviated from the crowd, indicating a rational response to
-information. \citet{steen2013} also found no herding behaviour in
+market information. \citet{steen2013} also found no herding behaviour in
 international commodity markets. Overall, the literature in this area is
@@
 Equation~\ref{eq-herding}. The estimated coefficient on market return is
-positive and highly significant as expected.The estimated coefficient on
-the non-linear term is negative (-1.2773) and statistically significant
-with a t-statistic of -9.71 suggesting that herd behaviour is present
-and robust in the US alternative energy ETFs.
+positive and highly significant as expected. The estimated coefficient
+on the non-linear term is negative (-1.2773) and statistically
+significant with a t-statistic of -9.71 suggesting that herd behaviour
+is present and robust in the US alternative energy ETFs.
 
@@
 estimate Equation~\ref{eq-herding} using the quantile regression (QR)
-proposed by \citet{koenker1978} and Table~\ref{tbl-quantile_herding}
+proposed by \citet{koenker1978}. Table~\ref{tbl-quantile_herding}
 presents the results of estimating Equation~\ref{eq-herding} across
@@
 
-Herding is present at low quantiles when markets are rising with an
+Herding is present at all quantiles when markets are rising with an
 estimated coefficient \(\gamma_3\) of -1.3669 and -1.2383 and highly
@@
 We use these high PRI and high TRI in one probit regression and low TRI
-and low PRI in another. Results are presented
+and low PRI in another. Results are presented in
 Table~\ref{tbl-probit_analysis2}. We observe higher uncertainty that
@@
 
-This study offers novel and valuable insights on herding behavior in
-clean energy ETFs.
-
-Results of baseline and rolling window analysis points to significant
-herding for the whole period and in various instances.
-
-\citet{choi2023} \citet{kuang2021}
+This study offers novel and valuable insights into herding behaviour in
+clean energy ETFs. We used various herding behaviour tests to achieve
+this. First, the baseline herding tests revealed significant evidence of
+herding behaviour. Second, the asymmetric herding tests showed that
+herding behaviour was present in both bear and bull markets. Lastly, the
+results of the time-varying tests point to significant periodic herding.
+However, the results further indicate that herding in US clean energy
+ETFs was not mainly related to climate-related risks or uncertainty. The
+probit analysis showed that climate-related uncertainty reduced the
+probability of herding or led to investor anti-herding behaviour. We
+defer to the literature on the factors that drive herding in these ETFs
+\citep[for example,][]{loang2023, koutmos2024, przychodzen2016}. Our
+results, similar to \citet{bua2024}, indicate that investors did not
+herd on climate-related uncertainty, and sought returns whilst hedging
+against climate-related risk. This is a positive for the financial
+stability of these growing alternative investment indices.
 

### 2025-01-07 alt_energy_herding/title.tex
complete draft

--- 2025-01-02 alt_energy_herding.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
-%
-\documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
-
-\usepackage{amsmath,amssymb}
-\usepackage{setspace}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else  
-    % xetex/luatex font selection
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\usepackage{fontspec}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{colortbl}
-\usepackage{hhline}
-\newlength\Oldarrayrulewidth
-\newlength\Oldtabcolsep
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage{wrapfig}
-% \usepackage{hyperref}
-% \hypersetup{
-%     colorlinks,
-%     linkcolor={blue!100!black},
-%     citecolor={blue!100!black},
-%     urlcolor={blue!100!black}
-% }
-% \usepackage{apacite}
-% \usepackage[round]{natbib} 
-% \usepackage{graphicx}
-% \usepackage{float}
-% \usepackage{caption}
-% \usepackage[toc,page]{appendix}
-% \usepackage{booktabs,caption}
-% \usepackage[flushleft]{threeparttable}
-% \usepackage{tabularx}
-\usepackage{sfmath}
-\usepackage{fontspec}
-\usepackage[utf8]{inputenc}
-\usepackage{siunitx}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-% \usepackage{xcolor}
-% \usepackage{scrextend}
-% \deffootnote[2em]{2em}{1em}{\textsuperscript{\thefootnotemark}\,}
-% \newcolumntype{Y}{>{\centering\arraybackslash}X}
-% \usepackage[a4paper]{geometry}
-% \usepackage{caption}
-% \usepackage[bottom,flushmargin,hang,multiple]{footmisc}
-% \usepackage{pdflscape}
-% \usepackage[paper=portrait,pagesize]{typearea}
-% \usepackage{rotating}
-% \usepackage{fullpage}
-% \usepackage{tabu}
-\usepackage{lscape}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcommand{\elandscape}{\end{landscape}}
-\usepackage{rotating}
-\newcommand{\bsideways}{\begin{sidewaystable}[htbp]}
-\newcommand{\esideways}{\end{sidewaystable}}
-\KOMAoption{captions}{tableheading}
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\usepackage[round]{natbib}
-\bibliographystyle{apalike}
-\usepackage{bookmark}
-
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  colorlinks=true,
-  linkcolor={blue!100!black},
-  filecolor={Maroon},
-  citecolor={blue!100!black},
-  urlcolor={blue!100!black},
-  pdfcreator={LaTeX via pandoc}}
-
-\author{}
-\date{}
-
-\begin{document}
-
 \title{Do investors in clean energy ETFs herd?}
 
-\author { 
+\author{ 
 Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
@@
 
-\noindent\textbf{Keywords}: Herding Behaviour, Financial Crises, Market Efficiency
+\noindent\textbf{Keywords}: Herding Behaviour, Climate Change, Energy
 \\
-\textbf{JEL Codes}: G01, G14, G15, G41
+\textbf{JEL Codes}: G14, Q54, P18
 \newpage
-
-\setstretch{1.5}
-\section{Introduction and literature
-review}\label{introduction-and-literature-review}
-
-Climate sustainability has become a major concern for financial markets
-and investors. This growing interest is primary driven by the increasing
-materialisation of climate risks, and the actions of governments,
-institutions and organizations towards a sustainable future
-\citep{giglio2021a}. In order to ensure returns, investors increasingly
-seek to hedge against climate risks by investing in green financial
-products. Although there evidence is mixed, indications that returns
-from green financial products are comparable to traditional financial
-\citetext{\citealp[see amongst
-others,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
-
-Specifically, climate change present risk to investor portfolios through
-two primary sources, physical and transition risks. physical risks or
-direct impact refer to extreme climate events such as floods and
-droughts, which impact business operations and infrastructure; and
-transition risks are the policy, technological, and other costs that
-societies bear to achieve low carbon economies
-\citetext{\citealp{nguyen2025}; \citealp[and][ amongst
-others]{giglio2021a}}. Investors, therefore, recognise these risk and
-seek to mitigate against them, as they seek return enhancing green
-financial products.
-
-Exchange traded funds (ETFs) are a key feature of green financial
-products. ETFs are a type of security that involves a collection of
-securities that often tracks an underlying index, although they can
-invest in any number of industry sectors or use various strategies. In
-addition, environment, social, and governance (ESG) ETFs serve as a
-market discovery tool for investors to identify and invest in companies
-that are environmentally friendly \citep{briere2023}. Among the ESG
-ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in
-2022, followed by the Cybersecurity and Artificial Intelligence (AI)
-ETFs \citep{decclesia2024}. The clean energy transition represents one
-of the largest multi-decade secular growth opportunities. After the
-inclusion of Green energy financing in the list of United Nations
-Sustainability Goals (SDGs) as SDG 7, the role, importance, and
-visibility of green financial products; all have escalated enormously
-\citep{naqvi2022}. Therefore, the growth of green
-assets-under-management is likely to continue.
-
-\newpage
-
-In this new climate sustainability paradigm, investors face many
-pressures that not only bear on returns, but also on the stability of
-financial markets. For example, resulting regulations aimed at reducing
-emissions can surprisingly reduce the profitability of fossil-fuel based
-companies, or the possible mispricing of assets from ignoring climate
-risks can lead to significant losses \citep{nguyen2025}. In addition to
-these climate risks, a general change in investor attitudes can drive
-the inclusion of green assets in their portfolio leading to systemic
-risk. These pressures are not withstanding the possible contribution
-that financial markets can play in mitigating and reducing the negative
-effects of climate change \citep{giglio2021a}.
-
-However, given how recent the inclusion of climate sustainability
-investment decisions is, it is not clear what the actual impact will be
-in the long run. In this study specifically, we ask whether the rapid
-adoption of CE ETFs could be driven a market fad driven by herding
-behaviour, or is a fundamental change in investor behaviour? Investors,
-for example, can believe that peers have information about climate risks
-that they do not, investors may herd to avoid losses compared to peers,
-or investors may be encouraged to herd by the desire to align to climate
-related social values \citep{ciciretti2021, gavrilakis2023, loang2023}.
-Therefore, market volatility and crisis, financial performance, and
-investor sentiment can be drivers of herding in ESG markets
-
-Although the overall evidence is mixed, herding behaviour in ESG markets
-is not without precedent. Amongst others, \citet{loang2023} found that
-compliance with SDG goals can introduce bias in investor sentiment,
-which lead to herding behaviour. Using a Twitter (or X) uncertainty
-index, \citet{koutmos2024} found evidence of herding in US-based ESG
-index fund investors. \citet{przychodzen2016} found herding behaviour
-amongst fund managers who incorporated ESG strategies in their
-portfolios. Lastly, \citet{rubbaniy2021} highlight evidence of herding
-in the MSCI US ESG Leader Index during extreme periods (bear and bull
-periods).
-
-\section{Data and methodology}\label{data-and-methodology}
-
-\subsection{Data}\label{data}
-
-The sample consists of alternative energy equity ETFs (green ETFs) that
-are traded in the US markets (see Table~\ref{tbl-data} in the
-Appendix).\footnote{The data were sourced from
-  \url{https://datastream.org/en-ca/}} The number of available
-alternative energy ETFs in our sample varied from 10 in the beginning of
-analysis to 30 at the most. The period of analysis runs from May
-1\textsuperscript{st} of 2016 through 19\textsuperscript{th} June of
-2024. The starting date was selected on the basis of the UN Climate
-Change Conference (COP) Paris agreement. Daily logarithmic returns were
-computed from the closing prices of ETFs for a total of 2122
-observations.
-
-\subsection{Methodology}\label{methodology}
-
-Following the relevant literature
-\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
-compute dispersion of the \(i^{th}\) ETF from the market return. This is
-known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
-Empirically the \(CSAD_t\) is defined in the following manner:
-
-\begin{equation}\phantomsection\label{eq-csad}{
-CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|,
-}\end{equation}
-
-where \(R_{i,t}\) is the return and \(R_{m,t}\) is the cross sectional
-average of returns for the sample of ETFs available for each day. The
-return dispersion measures the directional similarity of ETF returns to
-the market return. This return similarity forms the basis for the
-herding behaviour tests. The CSAD measure for US Alternative Energy ETFs
-is presented in Figure~\ref{fig-csad}. Following \citet{galariotis2015}
-we estimate Equation~\ref{eq-herding}:
-
-\begin{equation}\phantomsection\label{eq-herding}{
-CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
-}\end{equation}
-
-where \(\gamma_0\) is the intercept, \(\gamma_1\) is the coefficient of
-the linear term, \(\gamma_2\) is the coefficient of the quadratic term
-or the herding behaviour term, and \(\epsilon_t\) is the error term. The
-coefficient \(\gamma_2 <0\) when herding is present, and \(\gamma_2 >0\)
-when anti-herding is present. To ensure the robustness of the estimate,
-we estimate \(CSAD_{t}\) with Newey-West standard errors
-\citep[See][]{newey1987}.
-
-Based on the above and in order to provide additional insight on the
-herding phenomenon we examine whether herding presents an asymmetric
-response on days when the market is up vis-à-vis days when the market is
-down. To this end, we augment Equation~\ref{eq-herding} as follows:
-
-\begin{equation}\phantomsection\label{eq-asymmetry}{
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}^2  + \gamma_4D R_{m,t}^2 + \epsilon_t,
-}\end{equation}
-
-where \(D\) is a dummy variable that takes the value of 1 when the
-market return is negative and 0 otherwise. Therefore, our exploration of
-asymmetric behaviour of herding phenomenon is carried through the
-inspection of the statistical significance and the sign of the two
-estimated coefficients \(\gamma_3\) versus \(\gamma_4\) (up versus down
-markets).
-
-\section{Results}\label{results}
-
-\subsection{Herding behaviour}\label{herding-behaviour}
-
-Rational asset pricing models \citep[for example,][]{black1972} predict
-a linear relationship between return dispersion and market returns under
-normal conditions, a relationship that is no longer valid in the
-presence of herding. Herding behaviour leads to an increasing or
-decreasing cross sectional dispersion with respect to market returns. In
-other words, herding is captured by a non-linear term in the standard
-pricing equation indicating a decreasing or an increasing returns'
-dispersion.
-
-Stated differently, as \citet{chang2000} argue, in the case of herding
-the coefficient on the non-linear term (\(\gamma_2\)) will be negative
-and statistically significant. Table~\ref{tbl-herding} presents the
-results of herding for the full sample employing the non-linear
-Equation~\ref{eq-herding}. The estimated coefficient on market return is
-positive and highly significant as expected.The estimated coefficient on
-the non-linear term is negative (-1.2773) and statistically significant
-with a t-statistic of -9.71 suggesting that herd behaviour is present
-and robust in the US alternative energy ETFs.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.9}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.99in}|p{1.99in}|p{1.99in}}
-
-\caption{\label{tbl-herding}Estimation results of herding in the U.S.
-equity alternative energy ETFs}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endfirsthead
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2883***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2773***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(47.09)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(33.333)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(-9.71)}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{3}{>{\raggedright}m{\dimexpr 5.96in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-There is ample evidence in the relevant literature that herding
-behaviour in various asset markets \citep[see][]{pochea2017} exhibits
-asymmetry and time-varying characteristics. To this end, we proceed to
-estimate Equation~\ref{eq-herding} using the quantile regression (QR)
-proposed by \citet{koenker1978} and Table~\ref{tbl-quantile_herding}
-presents the results of estimating Equation~\ref{eq-herding} across
-various quantiles of the returns dispersion. Our focus is on the herding
-coefficient \(\gamma_2\), as a significant negative value of
-\(\gamma_2\) is indicative of herding. Such a finding is observed at two
-quantiles namely 25\% and 50\% with a value of -1.1056 and -1.165 which
-are highly significant. It is worth mentioning that the sign of the
-herding coefficient remains negative for almost all quantiles while the
-significance changes from significant to insignificant while we move
-from low and middle to upper quantiles (75\% and 90\%).
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.49in}|p{1.49in}|p{1.49in}|p{1.49in}}
-
-\caption{\label{tbl-quantile_herding}Estimation results of herding
-across various quantiles}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-4}\endfirsthead
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-4}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2536***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3736}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2461***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1056***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0037***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2648***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.165***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0048***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.3011***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1473***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0064***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2999***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.2314}}}} \\
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{4}{>{\raggedright}m{\dimexpr 5.94in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ 2\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{*,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
-
-\ascline{1pt}{000000}{1-4}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-\subsection{Herding behaviour during extreme market
-periods}\label{herding-behaviour-during-extreme-market-periods}
-
-It is widely accepted that asset returns are characterized by asymmetry,
-that is, return dispersion tend to behave differently in rising and
-falling markets \citep[see][]{geert2000, zhou2013, longin2001}. It
-should be noted, that examining the relationship between returns
-dispersion and market-wide returns across various quantiles of the
-returns distribution allows us to make more robust inference regarding
-the true behaviour of the phenomenon. Table~\ref{tbl-asymmetry_herding}
-reports the estimation results of herding in the up and down markets
-based on Equation~\ref{eq-asymmetry}. In general, we find that herding
-is more likely to occur in down markets than in up markets, which is
-indicative of the asymmetry of herding behaviour.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}}
-
-\caption{\label{tbl-asymmetry_herding}Estimation results of herding in
-up and down markets}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\
-
-\ascline{1pt}{000000}{1-6}\endfirsthead
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\
-
-\ascline{1pt}{000000}{1-6}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2532***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3669***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2522***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1522}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2475***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2383**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2477***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1171***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2247***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.3838}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2634***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3144***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0050***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2500***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.3135}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2785***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.9721***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0065***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2788***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.0169}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2942***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2003***}}}} \\
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
-
-\ascline{1pt}{000000}{1-6}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Herding is present at low quantiles when markets are rising with an
-estimated coefficient \(\gamma_3\) of -1.3669 and -1.2383 and highly
-significant respectively. However, when markets are declining, investors
-seem to neglect their own information set and imitate the actions of
-others resulting in a highly significant coefficient of herding
-(\(\gamma_4\)) across four out of five quantiles. Furthermore, we find
-that in high quantiles (75\% and 90\%) and when markets are rising the
-coefficient of interest (\(\gamma_3\)) turns positive but insignificant.
-
-\subsection{Herding behaviour
-over-time}\label{herding-behaviour-over-time}
-
-There is ample evidence that herding might be time dependent
-\citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In order to
-gain further insight on the time varying nature of herding we conducted
-a rolling window analysis. The size of the rolling window is related to
-the time-scales of the system (response times), and the aim of the
-research \citep{babalos2015}. There is no golden rule for the right size
-of the rolling window, there is a trade-off between having a long enough
-window to estimate the metrics, and short enough to have a sufficient
-number of windows in order to be able to derive a trend. In light of the
-above discussion we set off to conduct a rolling window analysis of 50
-observations. Figure~\ref{fig-rolling_window} plots the time evolution
-of the value of the estimated significance of the herding coefficient
-(\(\gamma_2\)) using the rolling window analysis.
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}
-
-}
-
-\caption{\label{fig-rolling_window}Rolling window herding estimates.
-Note: The red perforated lines indicates the 95\% confidence interval.}
-
-\end{figure}%
-
-We observe several periods of herding behaviour as reflected in the
-troughs in Figure~\ref{fig-rolling_window}. The most prominent cases of
-herding occur between March and May of 2020 followed by several
-instances of herding in the period that extends from March through April
-of 2017 and the period of February-March of 2023. On the other side, we
-derive significant moments of anti-herding behaviour in the clean energy
-ETFs by observing the spikes in Figure~\ref{fig-rolling_window}. Cross
-sectional dispersion appears to increase with respect to market-wide
-returns which is a sign of anti-herding behaviour on behalf of investors
-around December of 2016 and later during September of 2022.
-
-\subsection{Climate-related uncertainty and herding
-behaviour}\label{climate-related-uncertainty-and-herding-behaviour}
-
-The behaviour of participants in energy markets is closely related to
-the developments in the field of climate risks, carbon emissions and
-environmentally friendly policies. There are a few studies that attempt
-to quantify the effects of uncertainty related to climate on the economy
-and financial markets. \citet{bua2024} developed two climate risk
-related indexes namely transition and physical risk using a text-based
-approach in order to study the effect of these risks in financial
-markets. It is expected that investors would prefer to hold assets that
-perform well in the face of increasing climate change risks, even if
-this entails accepting lower returns for such climate-hedging assets.
-Therefore, in the context of our study and following previous studies
-that study the determinants of herding behaviour
-\citep[see][]{bouri2019, demirer2018}, we attempt to study the effect of
-climate-related uncertainty on the formation of herding behavior in the
-clean energy market.
-
-We use a probit model to relate herding to the two climate risk indexes
-developed by \citet{bua2024} in the following manner:
-
-\begin{equation}\phantomsection\label{eq-climate}{
-Pr(D^{herd} = 1 |\lambda_0 +  \lambda_1TRI  + \lambda_2PRI) = \lambda_0 +  \lambda_1TRI  + \lambda_2PRI,
-}\end{equation}
-
-where \(D^{herd}\) takes a value of 1 during periods of statistically
-significant herding (i.e., for days when the rolling t-statistic on
-\(\gamma_2 < −1.96\) in Figure~\ref{fig-rolling_window}) and zero
-otherwise. \(TRI\) is the transitional risk index and \(PRI\) is the
-physical risk index.
-
-The results from the Probit model are reported in
-Table~\ref{tbl-probit_analysis}, where only the physical risk index
-significantly decreases the probability of herding.\footnote{It should
-  be noted that due to availability issues the probit analysis ends in
-  December of 2023.} In other words, climate risks is good news for
-clean energy stocks or firms resulting in anti-herding behaviour. This
-implies that in the presence of higher physical risk with respect to the
-climate, clean energy ETFs become a more attractive investment option
-for investors that allocate their money to the various alternative
-energy investment products. As a result, the cross sectional dispersion
-of clean energy ETFs tends to increase.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{3.78in}|p{2.14in}}
-
-\caption{\label{tbl-probit_analysis}Estimation results of the probit
-model}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endfirsthead
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{2}{>{\raggedright}m{\dimexpr 5.92in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Furthermore, we develop two additional models to study the effect of
-climate risks on herding behaviour. We split the sample into two groups
-based on the median value of the TRI and PRI. We then estimate the
-following two models:
-
-\begin{equation}\phantomsection\label{eq-climate_high}{
-Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI) = \lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI, and
-}\end{equation}
-
-\begin{equation}\phantomsection\label{eq-climate_low}{
-Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI) = \lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI, 
-}\end{equation}
-
-where \(D^{herd}\) is the same as in Equation~\ref{eq-climate}.
-\(D^{TRI}_{high}\) and \(D^{PRI}_{high}\) are dummy variables that take
-a value of 1 if the value of the TRI and PRI are above the median and
-zero otherwise. Similarly, \(D^{TRI}_{low}\) and \(D^{PRI}_{low}\) are
-dummy variables that take a value of 1 if the value of the TRI and PRI
-are below the median and zero otherwise.
-
-\newpage
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{2.59in}|p{1.90in}|p{1.86in}}
-
-\caption{\label{tbl-probit_analysis2}Estimation results of the probit
-model with high and low climate risk indexes (above or below median)}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endfirsthead
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{3}{>{\raggedright}m{\dimexpr 6.34in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ *,\ denotes\ statistically\ significant\ at\ 10\%}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-We use these high PRI and high TRI in one probit regression and low TRI
-and low PRI in another. Results are presented
-Table~\ref{tbl-probit_analysis2}. We observe higher uncertainty that
-stems from physical or transition risk causes anti-herding which is in
-line with the logic we discussed earlier.
-
-\section{Conclusion}\label{conclusion}
-
-This study offers novel and valuable insights on herding behavior in
-clean energy ETFs.
-
-Results of baseline and rolling window analysis points to significant
-herding for the whole period and in various instances.
-
-\citet{choi2023} \citet{kuang2021}
-
-\newpage
-
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\renewcommand{\bibsection}{}
-\bibliography{references.bib}
-
-\setcounter{section}{0}
-\renewcommand{\thesection}{\Alph{section}}
-
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
-
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
-
-\newpage
-
-\section{Appendix}\label{appendix}
-
-\subsection{Cross-sectional average
-deviations}\label{cross-sectional-average-deviations}
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
-
-}
-
-\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
-US Alternative Energy ETFs}
-
-\end{figure}%
-
-\subsection{ETFs used in the study}\label{etfs-used-in-the-study}
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{5.39in}}
-
-\caption{\label{tbl-data}List of green ETFs used in the study}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} \\
-
-\ascline{1pt}{000000}{1-1}\endfirsthead
-
-\ascline{1pt}{000000}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} \\
-
-\ascline{1pt}{000000}{1-1}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ALPS\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLUE\ HORIZON\ BNE\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ S\&P\ KENSHO\ CLEAN\ POWER\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ CLEANTECH\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{PROSHARES\ S\&P\ KENSHO\ CLEANTECH\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ MSCI\ SUSTAINABLE\ FUTURE\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIRST\ TRUST\ GLOBAL\ WIND\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIDELITY\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLDS.BLOOMBERG\ CN.\ EN.\ EQ.ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ SMRT.GRID\ INFRA\ IDX\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DEFIANCE\ NEXT\ GEN\ H2\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DIREXION\ HYDROGEN\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ HYDROGEN\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ISHARES\ GLOBAL\ CLEAN\ EN.\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLACKR.WLD.EXUS\ CRBN\ TSTN.READINESS}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUB.CBN.TSTN.\&\ INFRA}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TCW\ TRANSFORM\ SYSTEMS\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ URANIUM\ AND\ NUCLEAR\ ENERGY}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUVEEN\ GLOBAL\ NET\ ZERO\ TRANSITION\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ MSCI\ USA\ CIM.\ PA.\ ALIGNED\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ GLOBAL\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ GREY.ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ SOLAR\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ RENEWABLE\ ENERGY\ PRODUCERS}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TRUESHARES\ EAG.GLB.\ RENWEN.ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ LOW\ CARBON\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SMARTETFS\ SUST.EN.\ II\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ SOLAR\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VIRTUS\ DUFF\ \&\ PHELPS\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ WIND\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{000000}{1-1}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ this\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-\end{document}

### 2025-02-20 alt_energy_herding.qmd
vassilas changes

@@
 editor: source
-bibliography: references.bib
+bibliography: energy_herding.bib
 biblio-style: apalike
@@
 source(here("Functions","fx_plot.R" ))
+
 ```
@@
 That is, the growth of green assets under management is likely to continue.
+Lastly, the limited availability of data on ESG complying investment tools [@avramov2022; @nguyen2025] justifies the use of green (CE) ETFs as best candidates of green assets.
 
@@
 
-Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2019 and 2024.
+In addition, our study extends the results of @dragomirescu-gaina2021 who examined herding behavior of investors in the US energy sector and herding sensitivity to various proxies of policy uncertainty and financial risk.
+They employed the energy equities included in the S&P 500 and concluded that herding among investors in the US energy market sector is sensitive to green volatility shocks
+
+Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2016 and 2024.
 We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets.
@@
 The probit analysis showed that climate-related uncertainty reduced the probability of herding or led to investor anti-herding behaviour.
-We defer to the literature on the factors that drive herding in these ETFs [for example, @loang2023;  @koutmos2024; @przychodzen2016].
+We differ to the literature on the factors that drive herding in these ETFs [for example, @loang2023;  @koutmos2024; @przychodzen2016].
 Our results, similar to @bua2024, indicate that investors did not herd on climate-related uncertainty, and sought returns whilst hedging against climate-related risk.

### 2025-02-20 alt_energy_herding.tex
vassilas changes

@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 
@@
 \makeatother
+
 \ifLuaTeX
@@
 Goals (SDGs) as SDG 7, the role, importance, and visibility of green
-financial products; all have escalated enormously \citep{naqvi2022}.
-Therefore, the growth of green assets under management is likely to
-continue.
-
-However, given how recent the inclusion of climate sustainability
+financial products have escalated enormously \citep{naqvi2022}. That is,
+the growth of green assets under management is likely to continue.
+Lastly, the limited availability of data on ESG complying investment
+tools \citep{avramov2022, nguyen2025} justifies the use of green (CE)
+ETFs as best candidates of green assets.
+
+However, given how recent the inclusion of climate sustainability in
 investment decisions is, it is not clear what the actual impact will be
@@
 
+In addition, our study extends the results of
+\citet{dragomirescu-gaina2021} who examined herding behavior of
+investors in the US energy sector and herding sensitivity to various
+proxies of policy uncertainty and financial risk. They employed the
+energy equities included in the S\&P 500 and concluded that herding
+among investors in the US energy market sector is sensitive to green
+volatility shocks
+
 Therefore, this study investigates herding behaviour in alternative
-energy ETFs in the US between 2019 and 2024. We then demonstrate how
+energy ETFs in the US between 2016 and 2024. We then demonstrate how
 climate-related uncertainty can drive herding behaviour in these
@@
 \citet{christie1995} and \citet{chang2000}. The traditional approach was
-supplemented by quantile regressions \citep[ ]{koenker1978} in order to
+supplemented by quantile regressions \citep{koenker1978} in order to
 capture the time-varying aspects of herding. Lastly, we extend recent
@@
 
-This study offers novel and valuable insights on herding behavior in
-clean energy ETFs.
-
-Results of baseline and rolling window analysis points to significant
-herding for the whole period and in various instances.
-
-\citet{choi2023} \citet{kuang2021}
+This study offers novel and valuable insights into herding behaviour in
+clean energy ETFs. We used various herding behaviour tests to achieve
+this. First, the baseline herding tests revealed significant evidence of
+herding behaviour. Second, the asymmetric herding tests showed that
+herding behaviour was present in both bear and bull markets. Lastly, the
+results of the time-varying tests point to significant periodic herding.
+However, the results further indicate that herding in US clean energy
+ETFs was not mainly related to climate-related risks or uncertainty. The
+probit analysis showed that climate-related uncertainty reduced the
+probability of herding or led to investor anti-herding behaviour. We
+differ to the literature on the factors that drive herding in these ETFs
+\citep[for example,][]{loang2023, koutmos2024, przychodzen2016}. Our
+results, similar to \citet{bua2024}, indicate that investors did not
+herd on climate-related uncertainty, and sought returns whilst hedging
+against climate-related risk. This is a positive for the financial
+stability of these growing alternative investment indices.
 
@@
 \renewcommand{\bibsection}{}
-\bibliography{references.bib}
+\bibliography{energy_herding.bib}
 

### 2025-03-21 alt_energy_herding.qmd
vassilias comments

@@
 
+It is well established that herding literature is vast with contradictory results depending mainly on the market, the employed methodology and the period under consideration [@spyrou2013].
+Herding behavior can be either spurious in cases when investors make similar decisions as a result of processing the same information set and intentional herding when investors imitate the actions of others [see inter alia, @bikhchandani2000; @galariotis2015].
+Empirical studies on herding usually fall into two categories: namely those that employ holdings data aiming at measuring institutional investor herding [@lakonishok1992], and studies that use market returns data and investigate herding towards the market consensus [@chang2000; @galariotis2015].
+Our paper falls within the latter category and tests for herding towards the market consensus for clean energy US ETFs.
+
 Herding behaviour in ESG markets is not without precedent.
@@
 Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour.
+
 The next section describes the data and methodology, followed by the results and conclusions.
@@
 Daily logarithmic returns were computed from the closing prices of ETFs for a total of 2122 observations.
+
+```{r}
+#| label: fig-csad
+#| cache: false
+#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
+#| fig.height: 3
+#| fig.width: 8
+
+read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 1) %>% 
+  rename(Date = date,
+         "Cross Sectional Absolute Deviations" = CSAD) %>% 
+  dplyr::select(Date, `Cross Sectional Absolute Deviations`) %>% 
+  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
+  fx_plot() +
+  theme(
+    # change plot text size
+    text = element_text(size = 10),
+    plot.tag = element_text(size = 10)
+  )
+
+```
+
+The development of the CSAD measure over time for the clean energy ETFs is presented in @fig-csad.
+In general, the CSAD measure remains within certain bounds.
+However, we observe several cases when the CSAD measure deviates significantly from the market consensus: around the announcement of the Paris agreement (2016-2017), the covid-19 pandemic crisis (2020–2021), the war outbreak in Ukraine (2022) among others.
+@tbl-desc presents the descriptive statistics of the data.
+
+```{r}
+#| label: tbl-desc
+#| tbl-cap: "Descriptive statistics of the data"
+#| cache: false
+
+tribble(
+  ~ " ", ~ "Mean", ~ "St.dev", ~ "Skewness", ~ "Kurtosis",
+  "CSAD",  "0.0062", "0.0034", "1.5598", "7.9355",
+  "Absolute CSAD",  "0.0094", "0.0107", "3.3175", "23.8725"
+) |> 
+  flextable_pdf() |> 
+  align(align = "left", j = 1, part = "all") |>
+  hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) |> 
+  autofit(add_w = 0.6)
+
+```
 
@@
 This return similarity forms the basis for the herding behaviour tests.
-The CSAD measure for US Alternative Energy ETFs is presented in @fig-csad.
 Following @galariotis2015 we estimate @eq-herding:
@@
 
-## Herding behaviour over-time
+## Time-varying herding behaviour
 
-There is ample evidence that herding might be time dependent [see @babalos2015; @klein2013; @stavroyiannis2019].
+There is ample evidence that herding might vary in response to market conditions [see @babalos2015; @klein2013; @stavroyiannis2019].
 In order to gain further insight on the time varying nature of herding we conducted a rolling window analysis.
@@
 The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies.
-There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets.
-@bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.
+In particular, following the implementation of the Paris agreement in November 2016, climate policy uncertainty has become in the epicenter of interest across carbon and energy markets.
+There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets [see inter alia, @gabriel2024; @bolton2021; @krueger2020].
+To this end, @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.
 It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets.
@@
 This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products.
-As a result, the cross sectional dispersion of clean energy ETFs tends to increase.
+As a result, the cross-sectional dispersion of clean energy ETFs tends to increase.
+Our results are in line with those of rrelevant studies such as Gabriel & Pinho (2024) who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.
 
@@
 
-## Cross-sectional average deviations
-
-```{r}
-#| label: fig-csad
-#| cache: false
-#| fig.cap: "Cross Sectional Absolute Deviation (CSAD) for US Alternative Energy ETFs"
-#| fig.height: 3
-#| fig.width: 8
-
-read_excel(here("Data", "data_for_xolani.xlsx"), sheet = 1) %>% 
-  rename(Date = date,
-         "Cross Sectional Absolute Deviations" = CSAD) %>% 
-  dplyr::select(Date, `Cross Sectional Absolute Deviations`) %>% 
-  pivot_longer(cols = -Date, names_to = "Series", values_to = "Value") %>%
-  fx_plot() +
-  theme(
-    # change plot text size
-    text = element_text(size = 10),
-    plot.tag = element_text(size = 10)
-  )
-
-```
-
 ## ETFs used in the study
@@
   align(align = "left", j = 1,  part = "all") %>%
-  add_footer_row(values = as_paragraph("Note: Details on this funds can be found on Yahoo Finance."), colwidths = 1) %>% 
+  add_footer_row(values = as_paragraph("Note: Details on these funds can be found on Yahoo Finance."), colwidths = 1) %>% 
   autofit(add_w = 3)

### 2025-03-21 alt_energy_herding.tex
vassilias comments

@@
 
+It is well established that herding literature is vast with
+contradictory results depending mainly on the market, the employed
+methodology and the period under consideration \citep{spyrou2013}.
+Herding behavior can be either spurious in cases when investors make
+similar decisions as a result of processing the same information set and
+intentional herding when investors imitate the actions of others
+\citep[see inter alia,][]{bikhchandani2000, galariotis2015}. Empirical
+studies on herding usually fall into two categories: namely those that
+employ holdings data aiming at measuring institutional investor herding
+\citep{lakonishok1992}, and studies that use market returns data and
+investigate herding towards the market consensus
+\citep{chang2000, galariotis2015}. Our paper falls within the latter
+category and tests for herding towards the market consensus for clean
+energy US ETFs.
+
 Herding behaviour in ESG markets is not without precedent. Amongst
@@
 approaches by \citet{bua2024} and others, which seek to establish a link
-between climate uncertainty and herding behaviour. The next section
-describes the data and methodology, followed by the results and
-conclusions.
+between climate uncertainty and herding behaviour.
+
+The next section describes the data and methodology, followed by the
+results and conclusions.
 
@@
 
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
+
+}
+
+\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
+US Alternative Energy ETFs}
+
+\end{figure}%
+
+The development of the CSAD measure over time for the clean energy ETFs
+is presented in Figure~\ref{fig-csad}. In general, the CSAD measure
+remains within certain bounds. However, we observe several cases when
+the CSAD measure deviates significantly from the market consensus:
+around the announcement of the Paris agreement (2016-2017), the covid-19
+pandemic crisis (2020--2021), the war outbreak in Ukraine (2022) among
+others. Table~\ref{tbl-desc} presents the descriptive statistics of the
+data.
+
+\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
+
+\global\setlength{\Oldtabcolsep}{\tabcolsep}
+
+\setlength{\tabcolsep}{2pt}
+
+\renewcommand*{\arraystretch}{0.7}
+
+\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
+
+\begin{longtable}[l]{|p{1.46in}|p{1.08in}|p{1.08in}|p{1.23in}|p{1.14in}}
+
+\caption{\label{tbl-desc}Descriptive statistics of the data}
+
+\tabularnewline
+
+\ascline{1pt}{000000}{1-5}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Mean}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{St.dev}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Skewness}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Kurtosis}}}} \\
+
+\ascline{1pt}{000000}{1-5}\endfirsthead
+
+\ascline{1pt}{000000}{1-5}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Mean}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{St.dev}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Skewness}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Kurtosis}}}} \\
+
+\ascline{1pt}{000000}{1-5}\endhead
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0062}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0034}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1.5598}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{7.9355}}}} \\
+
+\ascline{1pt}{FFFFFF}{1-5}
+
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\
+
+\ascline{1pt}{000000}{1-5}
+
+\end{longtable}
+
+\arrayrulecolor[HTML]{000000}
+
+\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
+
+\global\setlength{\tabcolsep}{\Oldtabcolsep}
+
+\renewcommand*{\arraystretch}{1}
+
 \subsection{Methodology}\label{methodology}
@@
 the market return. This return similarity forms the basis for the
-herding behaviour tests. The CSAD measure for US Alternative Energy ETFs
-is presented in Figure~\ref{fig-csad}. Following \citet{galariotis2015}
-we estimate Equation~\ref{eq-herding}:
+herding behaviour tests. Following \citet{galariotis2015} we estimate
+Equation~\ref{eq-herding}:
 
@@
 
-\subsection{Herding behaviour
-over-time}\label{herding-behaviour-over-time}
-
-There is ample evidence that herding might be time dependent
-\citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In order to
-gain further insight on the time varying nature of herding we conducted
-a rolling window analysis. The size of the rolling window is related to
-the time-scales of the system (response times), and the aim of the
-research \citep{babalos2015}. There is no golden rule for the right size
-of the rolling window, there is a trade-off between having a long enough
-window to estimate the metrics, and short enough to have a sufficient
-number of windows in order to be able to derive a trend. In light of the
-above discussion we set off to conduct a rolling window analysis of 50
-observations. Figure~\ref{fig-rolling_window} plots the time evolution
-of the value of the estimated significance of the herding coefficient
-(\(\gamma_2\)) using the rolling window analysis.
+\subsection{Time-varying herding
+behaviour}\label{time-varying-herding-behaviour}
+
+There is ample evidence that herding might vary in response to market
+conditions \citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In
+order to gain further insight on the time varying nature of herding we
+conducted a rolling window analysis. The size of the rolling window is
+related to the time-scales of the system (response times), and the aim
+of the research \citep{babalos2015}. There is no golden rule for the
+right size of the rolling window, there is a trade-off between having a
+long enough window to estimate the metrics, and short enough to have a
+sufficient number of windows in order to be able to derive a trend. In
+light of the above discussion we set off to conduct a rolling window
+analysis of 50 observations. Figure~\ref{fig-rolling_window} plots the
+time evolution of the value of the estimated significance of the herding
+coefficient (\(\gamma_2\)) using the rolling window analysis.
 
@@
 the developments in the field of climate risks, carbon emissions and
-environmentally friendly policies. There are a few studies that attempt
-to quantify the effects of uncertainty related to climate on the economy
-and financial markets. \citet{bua2024} developed two climate risk
-related indexes namely transition and physical risk using a text-based
-approach in order to study the effect of these risks in financial
-markets. It is expected that investors would prefer to hold assets that
-perform well in the face of increasing climate change risks, even if
-this entails accepting lower returns for such climate-hedging assets.
-Therefore, in the context of our study and following previous studies
-that study the determinants of herding behaviour
-\citep[see][]{bouri2019, demirer2018}, we attempt to study the effect of
-climate-related uncertainty on the formation of herding behavior in the
-clean energy market.
+environmentally friendly policies. In particular, following the
+implementation of the Paris agreement in November 2016, climate policy
+uncertainty has become in the epicenter of interest across carbon and
+energy markets. There are a few studies that attempt to quantify the
+effects of uncertainty related to climate on the economy and financial
+markets \citep[see inter alia,][]{gabriel2024, bolton2021, krueger2020}.
+To this end, \citet{bua2024} developed two climate risk related indexes
+namely transition and physical risk using a text-based approach in order
+to study the effect of these risks in financial markets. It is expected
+that investors would prefer to hold assets that perform well in the face
+of increasing climate change risks, even if this entails accepting lower
+returns for such climate-hedging assets. Therefore, in the context of
+our study and following previous studies that study the determinants of
+herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
+study the effect of climate-related uncertainty on the formation of
+herding behavior in the clean energy market.
 
@@
 for investors that allocate their money to the various alternative
-energy investment products. As a result, the cross sectional dispersion
-of clean energy ETFs tends to increase.
+energy investment products. As a result, the cross-sectional dispersion
+of clean energy ETFs tends to increase. Our results are in line with
+those of rrelevant studies such as Gabriel \& Pinho (2024) who claimed
+that in the event of climate policy shocks, clean energy assets could
+serve the role of hedging instruments.
 
@@
 
-\subsection{Cross-sectional average
-deviations}\label{cross-sectional-average-deviations}
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
-
-}
-
-\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
-US Alternative Energy ETFs}
-
-\end{figure}%
-
 \subsection{ETFs used in the study}\label{etfs-used-in-the-study}
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ this\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ these\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\
 

### 2025-03-24 alt_energy_herding.qmd
finalising comments

@@
 We observe several periods of herding behaviour as reflected in the troughs in @fig-rolling_window.
-The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 and the period of February-March of 2023.
+The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 (when $\gamma_2$ averaged -45.5) and the period of February-March of 2023 (when $\gamma_2$ averaged -7.68).We observe significant herding in the onset of the COVID-19 crisis 2020, which was short lived as market adapted.
+The rest of the Covid period was in the main characterised by anti-herding behaviour.
+@ghorbel2023 and @dhall2020 found similar results.
+Lastly, similar to @mohamad2024 we observe no herding behaviour related to the Russia-Ukraine war.
+@mohamad2024 highlights the importance of context in understanding the link between herding and market events.
 On the other side, we derive significant moments of anti-herding behaviour in the clean energy ETFs by observing the spikes in @fig-rolling_window.
@@
 As a result, the cross-sectional dispersion of clean energy ETFs tends to increase.
-Our results are in line with those of rrelevant studies such as Gabriel & Pinho (2024) who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.
+Our results are in line with those of relevant studies such as @gabriel2024 who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.
 

### 2025-03-24 alt_energy_herding.tex
finalising comments

@@
 instances of herding in the period that extends from March through April
-of 2017 and the period of February-March of 2023. On the other side, we
-derive significant moments of anti-herding behaviour in the clean energy
-ETFs by observing the spikes in Figure~\ref{fig-rolling_window}. Cross
-sectional dispersion appears to increase with respect to market-wide
-returns which is a sign of anti-herding behaviour on behalf of investors
-around December of 2016 and later during September of 2022.
+of 2017 (when \(\gamma_2\) averaged -45.5) and the period of
+February-March of 2023 (when \(\gamma_2\) averaged -7.68).We observe
+significant herding in the onset of the COVID-19 crisis 2020, which was
+short lived as market adapted. The rest of the Covid period was in the
+main characterised by anti-herding behaviour. \citet{ghorbel2023} and
+\citet{dhall2020} found similar results. Lastly, similar to
+\citet{mohamad2024} we observe no herding behaviour related to the
+Russia-Ukraine war. \citet{mohamad2024} highlights the importance of
+context in understanding the link between herding and market events. On
+the other side, we derive significant moments of anti-herding behaviour
+in the clean energy ETFs by observing the spikes in
+Figure~\ref{fig-rolling_window}. Cross sectional dispersion appears to
+increase with respect to market-wide returns which is a sign of
+anti-herding behaviour on behalf of investors around December of 2016
+and later during September of 2022.
 
@@
 of clean energy ETFs tends to increase. Our results are in line with
-those of rrelevant studies such as Gabriel \& Pinho (2024) who claimed
-that in the event of climate policy shocks, clean energy assets could
-serve the role of hedging instruments.
+those of relevant studies such as \citet{gabriel2024} who claimed that
+in the event of climate policy shocks, clean energy assets could serve
+the role of hedging instruments.
 

### 2025-03-24 alt_energy_herding.qmd
finalising comments still

@@
   hline_bottom(part = "footer", border = fp_border(color = "black", style = "solid", width = 1)) %>% 
-  autofit(add_w = 1.5)
+  autofit(add_w = 1.4)
 
@@
 Similarly, $D^{TRI}_{low}$ and $D^{PRI}_{low}$ are dummy variables that take a value of 1 if the value of the TRI and PRI are below the median and zero otherwise.
-
-\newpage
 

### 2025-03-24 alt_energy_herding.tex
finalising comments still

@@
 
-\begin{longtable}[l]{|p{3.78in}|p{2.14in}}
+\begin{longtable}[l]{|p{3.68in}|p{2.04in}}
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\
 
@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.78in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\
 
@@
 
-\multicolumn{2}{>{\raggedright}m{\dimexpr 5.92in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\
+\multicolumn{2}{>{\raggedright}m{\dimexpr 5.72in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\
 
@@
 are below the median and zero otherwise.
-
-\newpage
 

### 2025-03-24 alt_energy_herding.qmd
small changes

@@
   "CSAD",  "0.0062", "0.0034", "1.5598", "7.9355",
-  "Absolute CSAD",  "0.0094", "0.0107", "3.3175", "23.8725"
+  "Absolute CSAR",  "0.0094", "0.0107", "3.3175", "23.8725"
 ) |> 
@@
 $$
-CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
+CSAD_t = \gamma_0 + \gamma_1 |R_{m,t}| + \gamma_2 R_{m,t}^2 + \epsilon_t,
 $$ {#eq-herding}

### 2025-03-24 alt_energy_herding.tex
small changes

@@
 
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\
+\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAR}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\
 
@@
 \begin{equation}\phantomsection\label{eq-herding}{
-CSAD_t = \gamma_0 + \gamma_1 R_{m,t} + \gamma_2 R_{m,t}^2 + \epsilon_t,
+CSAD_t = \gamma_0 + \gamma_1 |R_{m,t}| + \gamma_2 R_{m,t}^2 + \epsilon_t,
 }\end{equation}

### 2025-03-31 Journal/journal_submission/alt_energy_herding_anonymous.tex
comments

--- 2025-03-24 alt_energy_herding.tex
@@
 
-\title{Do investors in clean energy ETFs herd?}
-
-\author{ 
-Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
-Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
+\title{Do investors in clean energy ETFs herd? The role of climate risks}
+
+%\author{ 
+%Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
+%Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
 Economic Research Department, South African Reserve Bank, Pretoria, South Africa.} \,\,
-Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
-Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
-}
+%Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
+%Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
+%}
 \date{\today}
@@
 
-This study offers novel and valuable insights into herding behaviour in US clean energy ETFs between 2016 and 2023. 
-The baseline herding tests by \cite{christie1995} and \cite{chang2000} revealed significant herding behaviour in this market. 
-This evidence was supported by asymmetric and time-varying herding tests. That is, investors herd both in bear and bullish markets, and periodically. 
-In addition, we found that climate risks (both physical and transition) reduced the probability of herding in US clean energy ETFs, 
-indicating that an increase in climate-related risk encouraged efficient or climate-hedging behaviour by investors. 
-Therefore, the results suggest that climate-related uncertainty did not drive herding behaviour in this market.
-The results suggest that investors are appropriately identifying opportunities that mitigate climate risk,
-thereby reducing the probability of herding-driven system risk.
+This study offers new insights into the herding behaviour in US clean energy Exchange-traded funds (ETFs) over the period from May 1, 2016 to June 19, 2024. 
+The baseline model shows significant herding. An extended mode indicates that herding is present in both down and up markets, with a stronger effect in the down market, suggesting an asymmetry. 
+Herding is also found to be time-varying.
+Further analysis shows that the transition climate risk, particularly its high level, reduces the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on the probability of herding.
+Thus, large levels of transition climate risk seem to encourage market efficiency in clean energy ETFs  and climate-hedging behavior by investors.
 
@@
 
-\noindent\textbf{Keywords}: Herding Behaviour, Climate Change, Energy
+\noindent\textbf{Keywords}: Herding Behaviour, Climate Change, Clean Energy
 \\
@@
 \setstretch{1.5}
-\section{Introduction and literature
-review}\label{introduction-and-literature-review}
+\section{Introduction}\label{introduction}
 
@@
 actions of governments, institutions and organizations towards a
-sustainable future \citep{giglio2021a}. To ensure returns, investors
+sustainable future \citep{giglio2021a}. To safeguard returns, investors
 increasingly seek to hedge against climate risks by investing in green
-financial products. Although the evidence is mixed, indications that
-returns from green financial products are comparable to traditional
-financial \citetext{\citealp[see amongst
+financial products. Although the evidence from the existing literature
+is mixed, returns from green financial products are somewhat comparable
+to traditional financial products \citetext{\citealp[see amongst
 others,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
-
 In this new climate sustainability paradigm, investors face many
@@
 risks can lead to significant losses \citep{nguyen2025}. In addition to
-these climate risks, a general change in investor attitudes can drive
-the inclusion of green assets in their portfolio can lead to systemic
+climate risks, a general change in investor attitudes can drive the
+inclusion of green assets in their portfolio can lead to systemic
 risk.\footnote{These pressures notwithstanding the possible contribution
   that financial markets can play in mitigating and reducing the
-  negative effects of climate change \citep{giglio2021a}}
-
-Specifically, climate change presents risks to investor portfolios
-through two primary sources - physical and transition risks. Physical
-risks or direct impact refer to extreme climate events such as floods
-and droughts, which impact business operations and infrastructure; and
-transition risks are the policy, technological, and other costs that
-societies bear to achieve low carbon economies
-\citetext{\citealp{nguyen2025}; \citealp[and][ amongst
-others]{giglio2021a}}. Investors, therefore, recognise these risks and
-seek to mitigate them, as they seek return-enhancing green financial
-products.
+  negative effects of climate change \citep{giglio2021a}} Specifically,
+climate change presents risks to the global financial system, and
+ultimately to investment portfolios, through two primary sources -
+physical and transition risks. Physical risks or direct impact refer to
+extreme climate events such as floods and droughts, which impact
+business operations and infrastructure; and transition risks are the
+policy, technological, and other costs that societies bear to achieve
+low carbon economies \citetext{\citealp{nguyen2025}; \citealp[and][
+amongst others]{giglio2021a}}. Investors, therefore, recognise these
+risks and seek to mitigate them, as they seek return-enhancing green
+financial products.
 
 Exchange-traded funds (ETFs) are a key feature of green financial
-products. ETFs are a type of security that involves a collection of
-securities that often tracks an underlying index. However, they can
-invest in various industry sectors or strategies. In addition,
-environment, social, and governance (ESG) ETFs serve as a market
-discovery tool for investors to identify and invest in environmentally
-friendly companies \citep{briere2023}. Among the ESG ETFs, the Clean
-Energy (CE) ETFs have been the best-performing ones in 2022, followed by
-the Cybersecurity and Artificial Intelligence (AI) ETFs
-\citep{decclesia2024}. The clean energy transition represents one of the
-largest multi-decade secular growth opportunities. After the inclusion
-of Green energy financing in the list of United Nations Sustainability
-Goals (SDGs) as SDG 7, the role, importance, and visibility of green
-financial products have escalated enormously \citep{naqvi2022}. That is,
-the growth of green assets under management is likely to continue.
-Lastly, the limited availability of data on ESG complying investment
-tools \citep{avramov2022, nguyen2025} justifies the use of green (CE)
-ETFs as best candidates of green assets.
-
-However, given how recent the inclusion of climate sustainability in
-investment decisions is, it is not clear what the actual impact will be
-in the long run. In this study specifically, we ask whether the rapid
-adoption of CE ETFs could be driven by market fads, or is a fundamental
-change in investor behaviour. Investors, for example, can believe that
-peers have information about climate risks that they do not, investors
-may herd to avoid losses compared to peers, or investors may be
+products. They are a collection of investments that often tracks an
+underlying performance of an asset or index. In the universe of
+environment, social, and governance (ESG) investments, clean ETFs serve
+as a tool for environmentally conscious investors to identify and invest
+in environmentally friendly companies \citep{briere2023} engaged in the
+transition towards a cleaner production and a low-carbon economy. Among
+the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing
+one in 2022 \citep{decclesia2024}. This is not surprising given that the
+clean energy transition represents one of the largest multi-decade
+secular growth opportunities. After the inclusion of Green energy
+financing in the list of United Nations Sustainability Goals (SDGs) as
+SDG 7, the role, importance, and visibility of green financial products
+have escalated enormously \citep{naqvi2022}. That is, the growth of
+green assets under management is likely to continue. Furthermore, the
+limited availability of data on ESG complying investment tools
+\citep{avramov2022, nguyen2025} justifies the use of energy ETFs as best
+candidates of green assets. However, given that the inclusion of climate
+sustainability in investment decisions is a recent phenomenon, it is not
+clear what the actual impact will be in the long-run.
+
+This study investigates herding behaviour in alternative (clean) energy
+ETFs in the US between May 1 2016 and June 19 2024, showing evidence of
+significant herding that is asymmetric and time-varying. We then study
+whether climate-related uncertainty can affect the herding behaviour in
+the US clean energy ETFs market. Methodologically, we follow the
+standard herding tests by \citet{christie1995} and \citet{chang2000}.
+Notably, we supplement the traditional approach with quantile
+regressions \citep{koenker1978} in order to capture how herding differs
+across various quantiles of the returns dispersion and in up and down
+markets. Lastly, to establish a link between climate risk and herding
+behaviour, we differentiating between transitional and physical risks
+\citep{bua2024} and provide valuable insights on their potential impact
+on the likelihood of herding in clean energy ETFs.
+
+In this study specifically, we ask whether the rapid adoption of clean
+energy ETFs could be driven by market fads, or is a fundamental change
+in investor behaviour. Investors, for example, can believe that their
+peers have more valuable information about climate risks, making them to
+herd to avoid losses compared to peers; alternatively, investors may be
 encouraged to herd by the desire to align to climate-related social
-values \citep{ciciretti2021, gavrilakis2023, loang2023}. Therefore,
-market volatility and crisis, financial performance, and investor
-sentiment can drive herding in ESG markets.
-
-It is well established that herding literature is vast with
-contradictory results depending mainly on the market, the employed
-methodology and the period under consideration \citep{spyrou2013}.
-Herding behavior can be either spurious in cases when investors make
-similar decisions as a result of processing the same information set and
-intentional herding when investors imitate the actions of others
-\citep[see inter alia,][]{bikhchandani2000, galariotis2015}. Empirical
-studies on herding usually fall into two categories: namely those that
-employ holdings data aiming at measuring institutional investor herding
-\citep{lakonishok1992}, and studies that use market returns data and
-investigate herding towards the market consensus
-\citep{chang2000, galariotis2015}. Our paper falls within the latter
-category and tests for herding towards the market consensus for clean
-energy US ETFs.
-
-Herding behaviour in ESG markets is not without precedent. Amongst
-others, \citet{loang2023} found that compliance with SDG goals can
-introduce bias in investor sentiment, which leads to herding behaviour.
-Using a Twitter (or X) uncertainty index, \citet{koutmos2024} found
-evidence of herding in US-based ESG index fund investors.
-\citet{przychodzen2016} found herding behaviour amongst fund managers
-who incorporated ESG strategies in their portfolios. Lastly,
-\citet{rubbaniy2021} highlight evidence of herding in the MSCI US ESG
-Leader Index during extreme periods (bear and bull periods).
-
-However, to the best of our knowledge, no studies exist that focus on
-herding behaviour in CE ESGs. This study, therefore, aims to extend the
-broader literature on herding behaviour in commodity and energy markets.
-Several studies in this area were conducted. For example,
-\citet{demirer2013a} conducted a commodity sectoral study and found
+values \citep{ciciretti2021, gavrilakis2023, loang2023}. Investors in
+clean energy stocks can experience large losses if their betting on
+clean energy stocks go wrong, which represents a major concern in their
+decision-making process. This incites those investors to disregard their
+own information and follow the market consensus, leading to significant
+herding behaviour in the clean energy market. \citet{devenow1996}
+indicate that following the market consensus induces some kind of
+security among less informed traders. This could be relevant to our
+analysis because ETFs represent a popular investment instrument for
+individual and retail investors who are not necessarily well informed
+about the risk and prospects of investments in clean energy firms and
+whether their contribution to the world transition to cleaner production
+should be financially lucrative. On a related front, the
+self-reinforcing nature of confidence in the tyranny of the majority, as
+indicated by \citet{teraji2003} could also be pertinent.
+
+While herding behaviour has been examined in ESG markets, it remains
+understudied in clean energy assets, notably, clean energy
+ETFs.\footnote{Amongst others, \citet{loang2023} shows that compliance
+  with SDG goals can introduce bias in investor sentiment, which leads
+  to herding behaviour. Using a Twitter (or X) uncertainty index,
+  \citet{koutmos2024} finds evidence of herding in US-based ESG index
+  fund investors. \citet{przychodzen2016} found indicate evidence of
+  herding behaviour amongst fund managers who incorporated ESG
+  strategies in their portfolios. Lastly, \citet{rubbaniy2021} highlight
+  evidence of herding in the MSCI US ESG Leader Index during extreme
+  (bear and bull periods) periods.} Other studies on herding have been
+conducted in commodity and fossil energy markets. For example,
+\citet{demirer2013} conducted a commodity sectoral study and found
 herding behaviour in grains but not in other sectors. Similarly,
-\citet{gilbert2010} showed herding behaviour amongst speculators in
+\citet{gilbert2010} shows herding behaviour amongst speculators in
 non-ferrous commodities. Others did not find evidence of herding in
-similar markets. \citet{babalos2015} found significant anti-herding
+similar markets. \citet{babalos2015} find significant anti-herding
 behaviour in metal commodities futures after the global financial
-crisis. \citet{pierdzioch2010} showed that forecasters in oil and metals
+crisis. \citet{pierdzioch2010} show that forecasters in oil and metals
 markets deviated from the crowd, indicating a rational response to
-market information. \citet{steen2013} also found no herding behaviour in
-international commodity markets. Overall, the literature in this area is
-mixed, which indicates scope for further study.
-
-In addition, our study extends the results of
-\citet{dragomirescu-gaina2021} who examined herding behavior of
+market information. \citet{steen2013} find no herding behaviour in
+international commodity markets. Notably, our study extends the results
+of \citet{dragomirescu-gaina2021} who have examined herding behavior of
 investors in the US energy sector and herding sensitivity to various
-proxies of policy uncertainty and financial risk. They employed the
-energy equities included in the S\&P 500 and concluded that herding
-among investors in the US energy market sector is sensitive to green
+proxies of policy uncertainty and financial risk. They study the energy
+equities included in the S\&P 500 and concluded that herding among
+investors in the US energy market sector is sensitive to green
 volatility shocks
 
-Therefore, this study investigates herding behaviour in alternative
-energy ETFs in the US between 2016 and 2024. We then demonstrate how
-climate-related uncertainty can drive herding behaviour in these
-markets. Methodologically, we follow the standard herding tests by
-\citet{christie1995} and \citet{chang2000}. The traditional approach was
-supplemented by quantile regressions \citep{koenker1978} in order to
-capture the time-varying aspects of herding. Lastly, we extend recent
-approaches by \citet{bua2024} and others, which seek to establish a link
-between climate uncertainty and herding behaviour.
+Our analysis shows that herding is significant and is present in both
+down and up markets, with a stronger effect in the down market,
+suggesting an asymmetry. Herding is also found to be time-varying.
+Notably, an additional analysis reveals that the transition climate
+risk, particularly its high level, reduces the probability of herding in
+clean energy ETFs, whereas physical climate risk does not exert any
+significant impact on the probability of herding
 
@@
 
-The sample consists of alternative energy equity ETFs (green ETFs) that
-are traded in the US markets (see Table~\ref{tbl-data} in the
+The sample consists of clean energy equity ETFs (green ETFs) that are
+traded in the US markets (see Table~\ref{tbl-data} in the
 Appendix).\footnote{The data were sourced from
-  \url{https://datastream.org/en-ca/}} The number of available
-alternative energy ETFs in our sample varied from 10 in the beginning of
-analysis to 30 at the most. The period of analysis runs from May
-1\textsuperscript{st} of 2016 through 19\textsuperscript{th} June of
-2024. The starting date was selected on the basis of the UN Climate
-Change Conference (COP) Paris agreement. Daily logarithmic returns were
-computed from the closing prices of ETFs for a total of 2122
-observations.
+  \url{https://datastream.org/en-ca/}} The number of available clean
+energy ETFs in our sample varied from 10 in the beginning of analysis to
+30 at the most. The period of analysis runs from May 1 2016 to 19 June
+2024. Daily closing prices on the clean energy ETFs under study were
+collected from the Refinitiv database. The starting date was selected on
+the basis of the UN Climate Change Conference (COP) Paris agreement.
+Daily logarithmic returns were computed from the closing prices of each
+ETF, yielding, a total of 2122 observations per ETF.
 
@@
 
+It is well established that herding literature is vast with
+contradictory results depending mainly on the market, the employed
+methodology and the period under consideration \citep{spyrou2013}.
+Herding behavior can be either spurious in cases when investors make
+similar decisions as a result of processing the same information set and
+intentional herding when investors imitate the actions of others
+\citep[see inter alia][]{bikhchandani2000, galariotis2015}. Empirical
+studies on herding usually fall into two categories: namely those that
+employ holdings data aiming at measuring institutional investor herding
+\citep[e.g.][]{lakonishok1992}, and studies that use market returns data
+and investigate herding towards the market consensus
+\citep[e.g.][]{chang2000, galariotis2015}. Our paper falls within the
+latter category and tests for herding towards the market consensus for
+clean energy US ETFs.
+
 Following the relevant literature
 \citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
-compute dispersion of the \(i^{th}\) ETF from the market return. This is
-known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
+compute dispersion of the \(i^{th}\) ETF from the market return, which
+is known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
 Empirically the \(CSAD_t\) is defined in the following manner:
@@
 
-Based on the above and in order to provide additional insight on the
-herding phenomenon we examine whether herding presents an asymmetric
-response on days when the market is up vis-à-vis days when the market is
-down. To this end, we augment Equation~\ref{eq-herding} as follows:
+To provide additional insight on the herding phenomenon we examine
+whether herding presents an asymmetric response on days when the market
+is up vis-à-vis days when the market is down. To this end, we augment
+Equation~\ref{eq-herding} as follows:
 
@@
 pricing equation indicating a decreasing or an increasing returns'
-dispersion.
-
-Stated differently, as \citet{chang2000} argue, in the case of herding
-the coefficient on the non-linear term (\(\gamma_2\)) will be negative
-and statistically significant. Table~\ref{tbl-herding} presents the
-results of herding for the full sample employing the non-linear
-Equation~\ref{eq-herding}. The estimated coefficient on market return is
-positive and highly significant as expected. The estimated coefficient
-on the non-linear term is negative (-1.2773) and statistically
-significant with a t-statistic of -9.71 suggesting that herd behaviour
-is present and robust in the US alternative energy ETFs.
+dispersion. Stated differently, as \citet{chang2000} argue, in the case
+of herding the coefficient on the non-linear term (\(\gamma_2\)) will be
+negative and statistically significant.
+
+Table~\ref{tbl-herding} presents the results of herding for the full
+sample, based on Equation~\ref{eq-herding}. The estimated coefficient on
+market return is positive and highly significant as expected.
+Importantly, the estimated coefficient on the non-linear term is
+negative (-1.2773) and statistically significant with a t-statistic of
+-9.71 suggesting that herd behaviour is present and robust in the US
+alternative energy ETFs. Accordingly, investors in US clean energy ETFs
+tend to disregard their private information and follow market consensus.
 
@@
 
-There is ample evidence in the relevant literature that herding
-behaviour in various asset markets \citep[see][]{pochea2017} exhibits
-asymmetry and time-varying characteristics. To this end, we proceed to
-estimate Equation~\ref{eq-herding} using the quantile regression (QR)
-proposed by \citet{koenker1978}. Table~\ref{tbl-quantile_herding}
-presents the results of estimating Equation~\ref{eq-herding} across
-various quantiles of the returns dispersion. Our focus is on the herding
-coefficient \(\gamma_2\), as a significant negative value of
-\(\gamma_2\) is indicative of herding. Such a finding is observed at two
-quantiles namely 25\% and 50\% with a value of -1.1056 and -1.165 which
-are highly significant. It is worth mentioning that the sign of the
-herding coefficient remains negative for almost all quantiles while the
-significance changes from significant to insignificant while we move
-from low and middle to upper quantiles (75\% and 90\%).
+Evidence from the existing literature shows that herding behaviour in
+various asset markets \citep[see][]{pochea2017} exhibits asymmetry. To
+this end, we proceed first with the estimation of
+Equation~\ref{eq-herding} using the quantile regression (QR) proposed by
+\citet{koenker1978}. Table~\ref{tbl-quantile_herding} presents the
+estimated results across various quantiles of the returns dispersion.
+They show that herding is statistically significant at lower
+(\(\tau= 25\%\)), middle (\(\tau =50\%\)), and upper (\(\tau=75\%\))
+with a value of -1.1056, -1.165, and -1.1473, respectively. No
+significant herding is found at extreme lower quantile (\(\tau=10\%\))
+and extreme higher quantile (\(\tau=90\%\)).
 
@@
 
-It is widely accepted that asset returns are characterized by asymmetry,
-that is, return dispersion tend to behave differently in rising and
-falling markets \citep[see][]{geert2000, zhou2013, longin2001}. It
-should be noted, that examining the relationship between returns
-dispersion and market-wide returns across various quantiles of the
-returns distribution allows us to make more robust inference regarding
-the true behaviour of the phenomenon. Table~\ref{tbl-asymmetry_herding}
-reports the estimation results of herding in the up and down markets
-based on Equation~\ref{eq-asymmetry}. In general, we find that herding
-is more likely to occur in down markets than in up markets, which is
-indicative of the asymmetry of herding behaviour.
-
-\newpage
+Then, we study herding in up and down markets. It is widely accepted
+that asset returns are characterized by asymmetry, that is, return
+dispersion tend to behave differently in rising and falling markets
+\citep[see][]{geert2000, zhou2013, longin2001}, with evidence suggesting
+that herding is more pronounced during periods of market stress. In this
+regard, examining the relationship between returns dispersion and
+market-wide returns across various quantiles of the returns distribution
+of clean energy ETFs allows us to make more robust inference regarding
+the true behaviour of the herding phenomenon.
+Table~\ref{tbl-asymmetry_herding} reports the estimation results of
+herding in the up and down markets based on Equation~\ref{eq-asymmetry}.
+In general, we find that herding is significant in both down and up
+markets
 
@@
 
-\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
+\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ captures\ potential\ herding\ in\ the\ up\ market,\ whereas\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ captures\ potential\ herding\ in\ the\ down\ market.\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
 
@@
 
-Herding is present at all quantiles when markets are rising with an
-estimated coefficient \(\gamma_3\) of -1.3669 and -1.2383 and highly
-significant respectively. However, when markets are declining, investors
-seem to neglect their own information set and imitate the actions of
-others resulting in a highly significant coefficient of herding
-(\(\gamma_4\)) across four out of five quantiles. Furthermore, we find
-that in high quantiles (75\% and 90\%) and when markets are rising the
-coefficient of interest (\(\gamma_3\)) turns positive but insignificant.
+When the market is rising, herding is present at all quantiles with a
+statistically significant coefficient \(\gamma_3\) ranging from -0.2522
+(\(\tau=10\%\)) to -0.2942 (\(\tau=90\%\)) . Similarly, when markets are
+declining, investors neglect their own information set and imitate the
+actions of others resulting in a highly significant coefficient of
+herding (\(\gamma_4\)) across four out of five quantiles, ranging from
+-0.9721 to -1,3144. Notably, the coefficient of herding in down market
+is larger than in up market, reflecting an asymmetric herding behaviour.
 
@@
 
-There is ample evidence that herding might vary in response to market
-conditions \citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In
-order to gain further insight on the time varying nature of herding we
-conducted a rolling window analysis. The size of the rolling window is
-related to the time-scales of the system (response times), and the aim
-of the research \citep{babalos2015}. There is no golden rule for the
-right size of the rolling window, there is a trade-off between having a
-long enough window to estimate the metrics, and short enough to have a
-sufficient number of windows in order to be able to derive a trend. In
-light of the above discussion we set off to conduct a rolling window
-analysis of 50 observations. Figure~\ref{fig-rolling_window} plots the
-time evolution of the value of the estimated significance of the herding
-coefficient (\(\gamma_2\)) using the rolling window analysis.
+There is ample evidence that herding varies with time
+\citep[see][]{babalos2015, klein2013, stavroyiannis2019} and intensifies
+during crisis periods. In order to gain insights on the time-varying
+nature of herding in clean energy ETFs, we conduct a rolling window
+analysis. The size of the rolling window is related to the time-scales
+of the system (response times), and the aim of the research
+\citep{babalos2015}. There is no golden rule for the right size of the
+rolling window, there is a trade-off between having a long enough window
+to estimate the metrics, and short enough to have a sufficient number of
+windows in order to be able to derive a trend. Accordingly, we conduct a
+rolling window analysis of 50 observations, and plot in
+Figure~\ref{fig-rolling_window} the time evolution of the value of the
+estimated significance of the herding coefficient (\(\gamma_2\)).
 
@@
 \end{figure}%
+
+\newpage
 
@@
 instances of herding in the period that extends from March through April
-of 2017 (when \(\gamma_2\) averaged -45.5) and the period of
-February-March of 2023 (when \(\gamma_2\) averaged -7.68).We observe
-significant herding in the onset of the COVID-19 crisis 2020, which was
-short lived as market adapted. The rest of the Covid period was in the
-main characterised by anti-herding behaviour. \citet{ghorbel2023} and
-\citet{dhall2020} found similar results. Lastly, similar to
-\citet{mohamad2024} we observe no herding behaviour related to the
-Russia-Ukraine war. \citet{mohamad2024} highlights the importance of
-context in understanding the link between herding and market events. On
-the other side, we derive significant moments of anti-herding behaviour
-in the clean energy ETFs by observing the spikes in
-Figure~\ref{fig-rolling_window}. Cross sectional dispersion appears to
-increase with respect to market-wide returns which is a sign of
-anti-herding behaviour on behalf of investors around December of 2016
-and later during September of 2022.
-
-\subsection{Climate-related uncertainty and herding
-behaviour}\label{climate-related-uncertainty-and-herding-behaviour}
+of 2017 and the period of February-March of 2023. On the other side, we
+derive significant moments of anti-herding behaviour in the clean energy
+ETFs by observing the peaks in Figure~\ref{fig-rolling_window}. Cross
+sectional dispersion appears to increase with respect to market-wide
+returns, which is a sign of anti-herding behaviour on behalf of
+investors around December of 2016 and later during September of 2022
+
+\subsection{Climate risks and herding
+behaviour}\label{climate-risks-and-herding-behaviour}
 
 The behaviour of participants in energy markets is closely related to
-the developments in the field of climate risks, carbon emissions and
-environmentally friendly policies. In particular, following the
+the developments in the field of climate risks, carbon emissions, and
+environmentally friendly policies. Rising climate risk is found to
+increase green energy prices \citep{dutta2023}, and evidence from the
+existing literature shows that climate policy uncertainty affects the
+performance of clean energy stocks relative to dirty ones, making the
+former outperform the later when the levels of climate policy
+uncertainty are high \citep{bouri2022}. In particular, following the
 implementation of the Paris agreement in November 2016, climate policy
@@
 energy markets. There are a few studies that attempt to quantify the
-effects of uncertainty related to climate on the economy and financial
+effects of uncertainty related to climate on the economy or financial
 markets \citep[see inter alia,][]{gabriel2024, bolton2021, krueger2020}.
-To this end, \citet{bua2024} developed two climate risk related indexes
-namely transition and physical risk using a text-based approach in order
-to study the effect of these risks in financial markets. It is expected
-that investors would prefer to hold assets that perform well in the face
-of increasing climate change risks, even if this entails accepting lower
-returns for such climate-hedging assets. Therefore, in the context of
-our study and following previous studies that study the determinants of
-herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
-study the effect of climate-related uncertainty on the formation of
-herding behavior in the clean energy market.
-
-We use a probit model to relate herding to the two climate risk indexes
-developed by \citet{bua2024} in the following manner:
+Interestingly, \citet{bua2024} developed two climate risk related
+indexes namely transition and physical risk using a text-based approach
+in order to study the effect of these risks in financial markets. In
+this regard, \citet{bouri2023} study the impact of both physical and
+climate risks on the returns and volatility of brown and green energy
+stocks, carbon emission allowances, and green bonds, showing evidence
+that transitional climate risk exerts a more significant impact than
+physical climate risk.
+
+It is expected that environmentally conscious investors would prefer to
+hold clean energy assets that perform well in the face of increasing
+climate change risks \citep[see][]{bouri2022}, even if this entails
+accepting lower returns for such climate-hedging assets. Therefore, in
+the context of our study and following previous studies on the
+determinants of herding behaviour \citep[see][]{bouri2019, demirer2018},
+we examine the effect of physical and transition climate risks on the
+formation of herding behavior in the clean energy ETF market.
+
+To this end, we use a probit model to relate herding to the two climate
+risk indexes developed by \citet{bua2024} in the following manner:
 
@@
 otherwise. \(TRI\) is the transitional risk index and \(PRI\) is the
-physical risk index.
+physical risk index. For details on the construction of \(TRI\) and
+\(PRI\), the reader can refer to the paper of \citet{bua2024}.
 
 The results from the Probit model are reported in
-Table~\ref{tbl-probit_analysis}, where only the physical risk index
-significantly decreases the probability of herding.\footnote{It should
-  be noted that due to availability issues the probit analysis ends in
-  December of 2023.} In other words, climate risks is good news for
-clean energy stocks or firms resulting in anti-herding behaviour. This
-implies that in the presence of higher physical risk with respect to the
-climate, clean energy ETFs become a more attractive investment option
-for investors that allocate their money to the various alternative
-energy investment products. As a result, the cross-sectional dispersion
-of clean energy ETFs tends to increase. Our results are in line with
-those of relevant studies such as \citet{gabriel2024} who claimed that
-in the event of climate policy shocks, clean energy assets could serve
-the role of hedging instruments.
+Table~\ref{tbl-probit_analysis}. Showing that only the transitional
+climate risk index significantly decreases the probability of herding in
+clean energy ETFs.\footnote{It should be noted that due to the
+  availability of climate risk data from \citet{bua2024}, the probit
+  analysis covers the period from May 1, 2016 to December 30, 2023.}
+Transitional climate risk represent good news for investors in clean
+energy stocks, possibly reducing their self-reinforcing nature of
+confidence in the tyranny of the majority \citep{teraji2003}) and their
+need for shared intention and action, resulting in a decrease in the
+herding behaviour. In the presence of higher transitional risk with
+respect to the climate, clean energy ETFs become a more attractive
+investment alternative for environmentally conscious investors who
+allocate their money to alternative energy investment products
+\citep[see][]{bouri2022}, reinforcing the confidence of investors in
+their own information. As a result, the cross-sectional dispersion of
+clean energy ETFs tends to increase. Our results are somewhat in line
+with \citet{bouri2023} who show that the transitional climate risk is
+more important than physical risk for the return and volatility of clean
+energy stocks. They also concord with other relevant studies which
+indicate that in the event of climate policy shocks, clean energy assets
+could serve the role of hedging instruments \citep{gabriel2024} and tend
+to outperform brown energy assets \citep{bouri2022}.
 
@@
 Furthermore, we develop two additional models to study the effect of
-climate risks on herding behaviour. We split the sample into two groups
-based on the median value of the TRI and PRI. We then estimate the
-following two models:
+high and low levels of climate risks on herding behaviour in clean
+energy ETFs. Accordingly, we split the sample into two groups based on
+the median value of the \(TRI\) and \(PRI\) and estimate the following
+two models:
 
@@
 \(D^{TRI}_{high}\) and \(D^{PRI}_{high}\) are dummy variables that take
-a value of 1 if the value of the TRI and PRI are above the median and
-zero otherwise. Similarly, \(D^{TRI}_{low}\) and \(D^{PRI}_{low}\) are
-dummy variables that take a value of 1 if the value of the TRI and PRI
-are below the median and zero otherwise.
+a value of 1 if the values of the \(TRI\) and \(PRI\) are above the
+median and zero otherwise. Similarly, \(D^{TRI}_{low}\) and
+\(D^{PRI}_{low}\) are dummy variables that take a value of 1 if the
+values of the \(TRI\) and \(PRI\) are below the median and zero
+otherwise.
 
@@
 
-We use these high PRI and high TRI in one probit regression and low TRI
-and low PRI in another. Results are presented in
-Table~\ref{tbl-probit_analysis2}. We observe higher uncertainty that
-stems from physical or transition risk causes anti-herding which is in
-line with the logic we discussed earlier.
+Using these high \(PRI\) and high \(TRI\) in one probit regression and
+low \(TRI\) and low \(PRI\) in another one, we present the results in
+Table~\ref{tbl-probit_analysis2}. We observe that high levels of
+transition risk decrease the likelihood of herding (i.e.~drives
+anti-herding) at the 10\% level of significance, which is in line with
+the logic we discussed earlier.
 
@@
 This study offers novel and valuable insights into herding behaviour in
-clean energy ETFs. We used various herding behaviour tests to achieve
-this. First, the baseline herding tests revealed significant evidence of
-herding behaviour. Second, the asymmetric herding tests showed that
-herding behaviour was present in both bear and bull markets. Lastly, the
-results of the time-varying tests point to significant periodic herding.
-However, the results further indicate that herding in US clean energy
-ETFs was not mainly related to climate-related risks or uncertainty. The
-probit analysis showed that climate-related uncertainty reduced the
-probability of herding or led to investor anti-herding behaviour. We
-differ to the literature on the factors that drive herding in these ETFs
-\citep[for example,][]{loang2023, koutmos2024, przychodzen2016}. Our
-results, similar to \citet{bua2024}, indicate that investors did not
-herd on climate-related uncertainty, and sought returns whilst hedging
-against climate-related risk. This is a positive for the financial
-stability of these growing alternative investment indices.
+US clean energy ETFs. We used various herding behaviour tests to achieve
+this. First, herding is found to be significant, and exists in both
+bearish and bullish markets, but shows an asymmetry in that it is more
+pronounced in the bearish market. Herding is also found to time-varying.
+Second, the transition climate risk, particularly its high levels,
+reduce the probability of herding behaviour, whereas physical climate
+risk plays no significant role irrespective of its (high or low) levels.
+This evidence that climate risks do not lead to higher herding behaviour
+in the clean energy ETFs, is new to the related literature.
+
+Our findings offer an interesting outlook on the role of transitional
+climate risk for the formation of herding in clean energy ETFs, which is
+a puzzle in the related literature. Given that herding represents a
+behavioural pattern that can challenge market efficiency and exacerbate
+price fluctuations, both policymakers and investors should benefit from
+our findings for the sake of investment decision and market efficiency
+under the transition towards cleaner production and decarbonized
+portfolio investments. Future studies could examine whether herding in
+clean energy ETFs is linked to excess volatility in the overall US stock
+market.
 
@@
 \renewcommand{\bibsection}{}
-\bibliography{energy_herding.bib}
+\bibliography{references.bib}
 
@@
 
-\caption{\label{tbl-data}List of green ETFs used in the study}
+\caption{\label{tbl-data}List of clean energy ETFs used in the study}
 

### 2025-03-31 Journal/journal_submission/alt_energy_herding_full.tex
comments

--- 2025-03-31 Journal/journal_submission/alt_energy_herding_anonymous.tex
@@
 
-%\author{ 
-%Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
-%Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
+\author{ 
+Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
+Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
 Economic Research Department, South African Reserve Bank, Pretoria, South Africa.} \,\,
-%Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
-%Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
-%}
+Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
+Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
+}
 \date{\today}

### 2025-03-31 Journal/journal_submission/alt_energy_herding_title.tex
comments

--- 2025-03-24 alt_energy_herding.tex
@@
 
-\title{Do investors in clean energy ETFs herd?}
+\title{Do investors in clean energy ETFs herd? The role of climate risks}
 
@@
 \setstretch{1.5}
-\section{Introduction and literature
-review}\label{introduction-and-literature-review}
-
-Climate sustainability is a major concern for financial markets and
-investors. The growing interest in climate sustainability is primarily
-driven by the increasing materialisation of climate risks, and the
-actions of governments, institutions and organizations towards a
-sustainable future \citep{giglio2021a}. To ensure returns, investors
-increasingly seek to hedge against climate risks by investing in green
-financial products. Although the evidence is mixed, indications that
-returns from green financial products are comparable to traditional
-financial \citetext{\citealp[see amongst
-others,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
-
-In this new climate sustainability paradigm, investors face many
-pressures that not only bear on returns but also the stability of
-financial markets. For example, resulting regulations aimed at reducing
-emissions can surprisingly reduce the profitability of fossil-fuel-based
-companies, or the possible mispricing of assets from ignoring climate
-risks can lead to significant losses \citep{nguyen2025}. In addition to
-these climate risks, a general change in investor attitudes can drive
-the inclusion of green assets in their portfolio can lead to systemic
-risk.\footnote{These pressures notwithstanding the possible contribution
-  that financial markets can play in mitigating and reducing the
-  negative effects of climate change \citep{giglio2021a}}
-
-Specifically, climate change presents risks to investor portfolios
-through two primary sources - physical and transition risks. Physical
-risks or direct impact refer to extreme climate events such as floods
-and droughts, which impact business operations and infrastructure; and
-transition risks are the policy, technological, and other costs that
-societies bear to achieve low carbon economies
-\citetext{\citealp{nguyen2025}; \citealp[and][ amongst
-others]{giglio2021a}}. Investors, therefore, recognise these risks and
-seek to mitigate them, as they seek return-enhancing green financial
-products.
-
-Exchange-traded funds (ETFs) are a key feature of green financial
-products. ETFs are a type of security that involves a collection of
-securities that often tracks an underlying index. However, they can
-invest in various industry sectors or strategies. In addition,
-environment, social, and governance (ESG) ETFs serve as a market
-discovery tool for investors to identify and invest in environmentally
-friendly companies \citep{briere2023}. Among the ESG ETFs, the Clean
-Energy (CE) ETFs have been the best-performing ones in 2022, followed by
-the Cybersecurity and Artificial Intelligence (AI) ETFs
-\citep{decclesia2024}. The clean energy transition represents one of the
-largest multi-decade secular growth opportunities. After the inclusion
-of Green energy financing in the list of United Nations Sustainability
-Goals (SDGs) as SDG 7, the role, importance, and visibility of green
-financial products have escalated enormously \citep{naqvi2022}. That is,
-the growth of green assets under management is likely to continue.
-Lastly, the limited availability of data on ESG complying investment
-tools \citep{avramov2022, nguyen2025} justifies the use of green (CE)
-ETFs as best candidates of green assets.
-
-However, given how recent the inclusion of climate sustainability in
-investment decisions is, it is not clear what the actual impact will be
-in the long run. In this study specifically, we ask whether the rapid
-adoption of CE ETFs could be driven by market fads, or is a fundamental
-change in investor behaviour. Investors, for example, can believe that
-peers have information about climate risks that they do not, investors
-may herd to avoid losses compared to peers, or investors may be
-encouraged to herd by the desire to align to climate-related social
-values \citep{ciciretti2021, gavrilakis2023, loang2023}. Therefore,
-market volatility and crisis, financial performance, and investor
-sentiment can drive herding in ESG markets.
-
-It is well established that herding literature is vast with
-contradictory results depending mainly on the market, the employed
-methodology and the period under consideration \citep{spyrou2013}.
-Herding behavior can be either spurious in cases when investors make
-similar decisions as a result of processing the same information set and
-intentional herding when investors imitate the actions of others
-\citep[see inter alia,][]{bikhchandani2000, galariotis2015}. Empirical
-studies on herding usually fall into two categories: namely those that
-employ holdings data aiming at measuring institutional investor herding
-\citep{lakonishok1992}, and studies that use market returns data and
-investigate herding towards the market consensus
-\citep{chang2000, galariotis2015}. Our paper falls within the latter
-category and tests for herding towards the market consensus for clean
-energy US ETFs.
-
-Herding behaviour in ESG markets is not without precedent. Amongst
-others, \citet{loang2023} found that compliance with SDG goals can
-introduce bias in investor sentiment, which leads to herding behaviour.
-Using a Twitter (or X) uncertainty index, \citet{koutmos2024} found
-evidence of herding in US-based ESG index fund investors.
-\citet{przychodzen2016} found herding behaviour amongst fund managers
-who incorporated ESG strategies in their portfolios. Lastly,
-\citet{rubbaniy2021} highlight evidence of herding in the MSCI US ESG
-Leader Index during extreme periods (bear and bull periods).
-
-However, to the best of our knowledge, no studies exist that focus on
-herding behaviour in CE ESGs. This study, therefore, aims to extend the
-broader literature on herding behaviour in commodity and energy markets.
-Several studies in this area were conducted. For example,
-\citet{demirer2013a} conducted a commodity sectoral study and found
-herding behaviour in grains but not in other sectors. Similarly,
-\citet{gilbert2010} showed herding behaviour amongst speculators in
-non-ferrous commodities. Others did not find evidence of herding in
-similar markets. \citet{babalos2015} found significant anti-herding
-behaviour in metal commodities futures after the global financial
-crisis. \citet{pierdzioch2010} showed that forecasters in oil and metals
-markets deviated from the crowd, indicating a rational response to
-market information. \citet{steen2013} also found no herding behaviour in
-international commodity markets. Overall, the literature in this area is
-mixed, which indicates scope for further study.
-
-In addition, our study extends the results of
-\citet{dragomirescu-gaina2021} who examined herding behavior of
-investors in the US energy sector and herding sensitivity to various
-proxies of policy uncertainty and financial risk. They employed the
-energy equities included in the S\&P 500 and concluded that herding
-among investors in the US energy market sector is sensitive to green
-volatility shocks
-
-Therefore, this study investigates herding behaviour in alternative
-energy ETFs in the US between 2016 and 2024. We then demonstrate how
-climate-related uncertainty can drive herding behaviour in these
-markets. Methodologically, we follow the standard herding tests by
-\citet{christie1995} and \citet{chang2000}. The traditional approach was
-supplemented by quantile regressions \citep{koenker1978} in order to
-capture the time-varying aspects of herding. Lastly, we extend recent
-approaches by \citet{bua2024} and others, which seek to establish a link
-between climate uncertainty and herding behaviour.
-
-The next section describes the data and methodology, followed by the
-results and conclusions.
-
-\section{Data and methodology}\label{data-and-methodology}
-
-\subsection{Data}\label{data}
-
-The sample consists of alternative energy equity ETFs (green ETFs) that
-are traded in the US markets (see Table~\ref{tbl-data} in the
-Appendix).\footnote{The data were sourced from
-  \url{https://datastream.org/en-ca/}} The number of available
-alternative energy ETFs in our sample varied from 10 in the beginning of
-analysis to 30 at the most. The period of analysis runs from May
-1\textsuperscript{st} of 2016 through 19\textsuperscript{th} June of
-2024. The starting date was selected on the basis of the UN Climate
-Change Conference (COP) Paris agreement. Daily logarithmic returns were
-computed from the closing prices of ETFs for a total of 2122
-observations.
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
-
-}
-
-\caption{\label{fig-csad}Cross Sectional Absolute Deviation (CSAD) for
-US Alternative Energy ETFs}
-
-\end{figure}%
-
-The development of the CSAD measure over time for the clean energy ETFs
-is presented in Figure~\ref{fig-csad}. In general, the CSAD measure
-remains within certain bounds. However, we observe several cases when
-the CSAD measure deviates significantly from the market consensus:
-around the announcement of the Paris agreement (2016-2017), the covid-19
-pandemic crisis (2020--2021), the war outbreak in Ukraine (2022) among
-others. Table~\ref{tbl-desc} presents the descriptive statistics of the
-data.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.46in}|p{1.08in}|p{1.08in}|p{1.23in}|p{1.14in}}
-
-\caption{\label{tbl-desc}Descriptive statistics of the data}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-5}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Mean}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{St.dev}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Skewness}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Kurtosis}}}} \\
-
-\ascline{1pt}{000000}{1-5}\endfirsthead
-
-\ascline{1pt}{000000}{1-5}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Mean}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{St.dev}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Skewness}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Kurtosis}}}} \\
-
-\ascline{1pt}{000000}{1-5}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{CSAD}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0062}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0034}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1.5598}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{7.9355}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-5}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 1.46in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Absolute\ CSAR}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0094}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.08in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0107}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.23in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{3.3175}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.14in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{23.8725}}}} \\
-
-\ascline{1pt}{000000}{1-5}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-\subsection{Methodology}\label{methodology}
-
-Following the relevant literature
-\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
-compute dispersion of the \(i^{th}\) ETF from the market return. This is
-known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
-Empirically the \(CSAD_t\) is defined in the following manner:
-
-\begin{equation}\phantomsection\label{eq-csad}{
-CSAD_t = \dfrac{1}{N}\sum_{i=1}^{N} |R_{i,t} - R_{m,t}|,
-}\end{equation}
-
-where \(R_{i,t}\) is the return and \(R_{m,t}\) is the cross sectional
-average of returns for the sample of ETFs available for each day. The
-return dispersion measures the directional similarity of ETF returns to
-the market return. This return similarity forms the basis for the
-herding behaviour tests. Following \citet{galariotis2015} we estimate
-Equation~\ref{eq-herding}:
-
-\begin{equation}\phantomsection\label{eq-herding}{
-CSAD_t = \gamma_0 + \gamma_1 |R_{m,t}| + \gamma_2 R_{m,t}^2 + \epsilon_t,
-}\end{equation}
-
-where \(\gamma_0\) is the intercept, \(\gamma_1\) is the coefficient of
-the linear term, \(\gamma_2\) is the coefficient of the quadratic term
-or the herding behaviour term, and \(\epsilon_t\) is the error term. The
-coefficient \(\gamma_2 <0\) when herding is present, and \(\gamma_2 >0\)
-when anti-herding is present. To ensure the robustness of the estimate,
-we estimate \(CSAD_{t}\) with Newey-West standard errors
-\citep[See][]{newey1987}.
-
-Based on the above and in order to provide additional insight on the
-herding phenomenon we examine whether herding presents an asymmetric
-response on days when the market is up vis-à-vis days when the market is
-down. To this end, we augment Equation~\ref{eq-herding} as follows:
-
-\begin{equation}\phantomsection\label{eq-asymmetry}{
-CSAD_t = \gamma_0 + \gamma_1(1-D) R_{m,t} + \gamma_2D R_{m,t} + \gamma_3(1-D) R_{m,t}^2  + \gamma_4D R_{m,t}^2 + \epsilon_t,
-}\end{equation}
-
-where \(D\) is a dummy variable that takes the value of 1 when the
-market return is negative and 0 otherwise. Therefore, our exploration of
-asymmetric behaviour of herding phenomenon is carried through the
-inspection of the statistical significance and the sign of the two
-estimated coefficients \(\gamma_3\) versus \(\gamma_4\) (up versus down
-markets).
-
-\section{Results}\label{results}
-
-\subsection{Herding behaviour}\label{herding-behaviour}
-
-Rational asset pricing models \citep[for example,][]{black1972} predict
-a linear relationship between return dispersion and market returns under
-normal conditions, a relationship that is no longer valid in the
-presence of herding. Herding behaviour leads to an increasing or
-decreasing cross sectional dispersion with respect to market returns. In
-other words, herding is captured by a non-linear term in the standard
-pricing equation indicating a decreasing or an increasing returns'
-dispersion.
-
-Stated differently, as \citet{chang2000} argue, in the case of herding
-the coefficient on the non-linear term (\(\gamma_2\)) will be negative
-and statistically significant. Table~\ref{tbl-herding} presents the
-results of herding for the full sample employing the non-linear
-Equation~\ref{eq-herding}. The estimated coefficient on market return is
-positive and highly significant as expected. The estimated coefficient
-on the non-linear term is negative (-1.2773) and statistically
-significant with a t-statistic of -9.71 suggesting that herd behaviour
-is present and robust in the US alternative energy ETFs.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.9}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.99in}|p{1.99in}|p{1.99in}}
-
-\caption{\label{tbl-herding}Estimation results of herding in the U.S.
-equity alternative energy ETFs}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endfirsthead
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2883***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2773***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(47.09)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(33.333)}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{(-9.71)}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{3}{>{\raggedright}m{\dimexpr 5.96in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ *,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-There is ample evidence in the relevant literature that herding
-behaviour in various asset markets \citep[see][]{pochea2017} exhibits
-asymmetry and time-varying characteristics. To this end, we proceed to
-estimate Equation~\ref{eq-herding} using the quantile regression (QR)
-proposed by \citet{koenker1978}. Table~\ref{tbl-quantile_herding}
-presents the results of estimating Equation~\ref{eq-herding} across
-various quantiles of the returns dispersion. Our focus is on the herding
-coefficient \(\gamma_2\), as a significant negative value of
-\(\gamma_2\) is indicative of herding. Such a finding is observed at two
-quantiles namely 25\% and 50\% with a value of -1.1056 and -1.165 which
-are highly significant. It is worth mentioning that the sign of the
-herding coefficient remains negative for almost all quantiles while the
-significance changes from significant to insignificant while we move
-from low and middle to upper quantiles (75\% and 90\%).
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{1.49in}|p{1.49in}|p{1.49in}|p{1.49in}}
-
-\caption{\label{tbl-quantile_herding}Estimation results of herding
-across various quantiles}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-4}\endfirsthead
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} \\
-
-\ascline{1pt}{000000}{1-4}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2536***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3736}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2461***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1056***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0037***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2648***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.165***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0048***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.3011***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1473***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-4}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0064***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2999***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.49in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.2314}}}} \\
-
-\ascline{1pt}{000000}{1-4}
-
-\multicolumn{4}{>{\raggedright}m{\dimexpr 5.94in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ 2\ in\ various\ quantiles\ 10,\ 25,\ 50,\ 75\ and\ 90\%\ of\ the\ returns\ distribution.}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{*,**,***\ denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
-
-\ascline{1pt}{000000}{1-4}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-\subsection{Herding behaviour during extreme market
-periods}\label{herding-behaviour-during-extreme-market-periods}
-
-It is widely accepted that asset returns are characterized by asymmetry,
-that is, return dispersion tend to behave differently in rising and
-falling markets \citep[see][]{geert2000, zhou2013, longin2001}. It
-should be noted, that examining the relationship between returns
-dispersion and market-wide returns across various quantiles of the
-returns distribution allows us to make more robust inference regarding
-the true behaviour of the phenomenon. Table~\ref{tbl-asymmetry_herding}
-reports the estimation results of herding in the up and down markets
-based on Equation~\ref{eq-asymmetry}. In general, we find that herding
-is more likely to occur in down markets than in up markets, which is
-indicative of the asymmetry of herding behaviour.
-
-\newpage
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}|p{0.99in}}
-
-\caption{\label{tbl-asymmetry_herding}Estimation results of herding in
-up and down markets}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\
-
-\ascline{1pt}{000000}{1-6}\endfirsthead
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Quantile}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_1 $}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_3$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\gamma_4$}}}} \\
-
-\ascline{1pt}{000000}{1-6}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 10\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0016***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2532***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3669***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2522***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1522}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 25\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0026***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2475***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2383**}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2477***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.1171***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 50\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0038***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2247***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 0.3838}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2634***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.3144***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 75\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0050***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2500***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.3135}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2785***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.9721***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-6}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\tau = 90\%$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.0065***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{0.2788***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ 1.0169}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -0.2942***}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 0.99in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.2003***}}}} \\
-
-\ascline{1pt}{000000}{1-6}
-
-\multicolumn{6}{>{\raggedright}m{\dimexpr 5.91in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ This\ table\ presents\ the\ estimation\ results\ of\ herding\ of\ US\ Alternative\ energy\ equity\ ETFs\ according\ to\ Equation\ (3).\ *,**,***denotes\ significance\ at\ 10\%,5\%\ and\ 1\%\ respectively.}}}} \\
-
-\ascline{1pt}{000000}{1-6}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Herding is present at all quantiles when markets are rising with an
-estimated coefficient \(\gamma_3\) of -1.3669 and -1.2383 and highly
-significant respectively. However, when markets are declining, investors
-seem to neglect their own information set and imitate the actions of
-others resulting in a highly significant coefficient of herding
-(\(\gamma_4\)) across four out of five quantiles. Furthermore, we find
-that in high quantiles (75\% and 90\%) and when markets are rising the
-coefficient of interest (\(\gamma_3\)) turns positive but insignificant.
-
-\subsection{Time-varying herding
-behaviour}\label{time-varying-herding-behaviour}
-
-There is ample evidence that herding might vary in response to market
-conditions \citep[see][]{babalos2015, klein2013, stavroyiannis2019}. In
-order to gain further insight on the time varying nature of herding we
-conducted a rolling window analysis. The size of the rolling window is
-related to the time-scales of the system (response times), and the aim
-of the research \citep{babalos2015}. There is no golden rule for the
-right size of the rolling window, there is a trade-off between having a
-long enough window to estimate the metrics, and short enough to have a
-sufficient number of windows in order to be able to derive a trend. In
-light of the above discussion we set off to conduct a rolling window
-analysis of 50 observations. Figure~\ref{fig-rolling_window} plots the
-time evolution of the value of the estimated significance of the herding
-coefficient (\(\gamma_2\)) using the rolling window analysis.
-
-\begin{figure}[H]
-
-\centering{
-
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}
-
-}
-
-\caption{\label{fig-rolling_window}Rolling window herding estimates.
-Note: The red perforated lines indicates the 95\% confidence interval.}
-
-\end{figure}%
-
-We observe several periods of herding behaviour as reflected in the
-troughs in Figure~\ref{fig-rolling_window}. The most prominent cases of
-herding occur between March and May of 2020 followed by several
-instances of herding in the period that extends from March through April
-of 2017 (when \(\gamma_2\) averaged -45.5) and the period of
-February-March of 2023 (when \(\gamma_2\) averaged -7.68).We observe
-significant herding in the onset of the COVID-19 crisis 2020, which was
-short lived as market adapted. The rest of the Covid period was in the
-main characterised by anti-herding behaviour. \citet{ghorbel2023} and
-\citet{dhall2020} found similar results. Lastly, similar to
-\citet{mohamad2024} we observe no herding behaviour related to the
-Russia-Ukraine war. \citet{mohamad2024} highlights the importance of
-context in understanding the link between herding and market events. On
-the other side, we derive significant moments of anti-herding behaviour
-in the clean energy ETFs by observing the spikes in
-Figure~\ref{fig-rolling_window}. Cross sectional dispersion appears to
-increase with respect to market-wide returns which is a sign of
-anti-herding behaviour on behalf of investors around December of 2016
-and later during September of 2022.
-
-\subsection{Climate-related uncertainty and herding
-behaviour}\label{climate-related-uncertainty-and-herding-behaviour}
-
-The behaviour of participants in energy markets is closely related to
-the developments in the field of climate risks, carbon emissions and
-environmentally friendly policies. In particular, following the
-implementation of the Paris agreement in November 2016, climate policy
-uncertainty has become in the epicenter of interest across carbon and
-energy markets. There are a few studies that attempt to quantify the
-effects of uncertainty related to climate on the economy and financial
-markets \citep[see inter alia,][]{gabriel2024, bolton2021, krueger2020}.
-To this end, \citet{bua2024} developed two climate risk related indexes
-namely transition and physical risk using a text-based approach in order
-to study the effect of these risks in financial markets. It is expected
-that investors would prefer to hold assets that perform well in the face
-of increasing climate change risks, even if this entails accepting lower
-returns for such climate-hedging assets. Therefore, in the context of
-our study and following previous studies that study the determinants of
-herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
-study the effect of climate-related uncertainty on the formation of
-herding behavior in the clean energy market.
-
-We use a probit model to relate herding to the two climate risk indexes
-developed by \citet{bua2024} in the following manner:
-
-\begin{equation}\phantomsection\label{eq-climate}{
-Pr(D^{herd} = 1 |\lambda_0 +  \lambda_1TRI  + \lambda_2PRI) = \lambda_0 +  \lambda_1TRI  + \lambda_2PRI,
-}\end{equation}
-
-where \(D^{herd}\) takes a value of 1 during periods of statistically
-significant herding (i.e., for days when the rolling t-statistic on
-\(\gamma_2 < −1.96\) in Figure~\ref{fig-rolling_window}) and zero
-otherwise. \(TRI\) is the transitional risk index and \(PRI\) is the
-physical risk index.
-
-The results from the Probit model are reported in
-Table~\ref{tbl-probit_analysis}, where only the physical risk index
-significantly decreases the probability of herding.\footnote{It should
-  be noted that due to availability issues the probit analysis ends in
-  December of 2023.} In other words, climate risks is good news for
-clean energy stocks or firms resulting in anti-herding behaviour. This
-implies that in the presence of higher physical risk with respect to the
-climate, clean energy ETFs become a more attractive investment option
-for investors that allocate their money to the various alternative
-energy investment products. As a result, the cross-sectional dispersion
-of clean energy ETFs tends to increase. Our results are in line with
-those of relevant studies such as \citet{gabriel2024} who claimed that
-in the event of climate policy shocks, clean energy assets could serve
-the role of hedging instruments.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{3.68in}|p{2.04in}}
-
-\caption{\label{tbl-probit_analysis}Estimation results of the probit
-model}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endfirsthead
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Variable}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Coefficient}}}} \\
-
-\ascline{1pt}{000000}{1-2}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_0$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ -1.506***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-4.607***}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.318}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Log\ Likelihood}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-484.7}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 0}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{1816}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-2}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 3.68in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Observations\ with\ Dependent\ Variable\ (Dep)\ =\ 1}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 2.04in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{134}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\multicolumn{2}{>{\raggedright}m{\dimexpr 5.72in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ **,***\ denotes\ statistically\ significant\ at\ 5\%\ and\ 1\%}}}} \\
-
-\ascline{1pt}{000000}{1-2}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-Furthermore, we develop two additional models to study the effect of
-climate risks on herding behaviour. We split the sample into two groups
-based on the median value of the TRI and PRI. We then estimate the
-following two models:
-
-\begin{equation}\phantomsection\label{eq-climate_high}{
-Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI) = \lambda_0 +\lambda_1D^{TRI}_{high}TRI + \lambda_2D^{PRI}_{high}PRI, and
-}\end{equation}
-
-\begin{equation}\phantomsection\label{eq-climate_low}{
-Pr(D^{herd} = 1 |\lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI) = \lambda_0 +\lambda_1D^{TRI}_{low}TRI + \lambda_2D^{PRI}_{low}PRI, 
-}\end{equation}
-
-where \(D^{herd}\) is the same as in Equation~\ref{eq-climate}.
-\(D^{TRI}_{high}\) and \(D^{PRI}_{high}\) are dummy variables that take
-a value of 1 if the value of the TRI and PRI are above the median and
-zero otherwise. Similarly, \(D^{TRI}_{low}\) and \(D^{PRI}_{low}\) are
-dummy variables that take a value of 1 if the value of the TRI and PRI
-are below the median and zero otherwise.
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{2.59in}|p{1.90in}|p{1.86in}}
-
-\caption{\label{tbl-probit_analysis2}Estimation results of the probit
-model with high and low climate risk indexes (above or below median)}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endfirsthead
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{\ }}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{High}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Low}}}} \\
-
-\ascline{1pt}{000000}{1-3}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_1$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.736*}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-6.118}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-3}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 2.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{$\lambda_2$}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.9in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-1.798}}}} & \multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\centering}m{\dimexpr 1.86in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{-2.581}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\multicolumn{3}{>{\raggedright}m{\dimexpr 6.34in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Notes:\ *,\ denotes\ statistically\ significant\ at\ 10\%}}}} \\
-
-\ascline{1pt}{000000}{1-3}
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
-
-We use these high PRI and high TRI in one probit regression and low TRI
-and low PRI in another. Results are presented in
-Table~\ref{tbl-probit_analysis2}. We observe higher uncertainty that
-stems from physical or transition risk causes anti-herding which is in
-line with the logic we discussed earlier.
-
-\section{Conclusion}\label{conclusion}
-
-This study offers novel and valuable insights into herding behaviour in
-clean energy ETFs. We used various herding behaviour tests to achieve
-this. First, the baseline herding tests revealed significant evidence of
-herding behaviour. Second, the asymmetric herding tests showed that
-herding behaviour was present in both bear and bull markets. Lastly, the
-results of the time-varying tests point to significant periodic herding.
-However, the results further indicate that herding in US clean energy
-ETFs was not mainly related to climate-related risks or uncertainty. The
-probit analysis showed that climate-related uncertainty reduced the
-probability of herding or led to investor anti-herding behaviour. We
-differ to the literature on the factors that drive herding in these ETFs
-\citep[for example,][]{loang2023, koutmos2024, przychodzen2016}. Our
-results, similar to \citet{bua2024}, indicate that investors did not
-herd on climate-related uncertainty, and sought returns whilst hedging
-against climate-related risk. This is a positive for the financial
-stability of these growing alternative investment indices.
-
-\newpage
-
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\renewcommand{\bibsection}{}
-\bibliography{energy_herding.bib}
-
-\setcounter{section}{0}
-\renewcommand{\thesection}{\Alph{section}}
-
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
-
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
-
-\newpage
-
-\section{Appendix}\label{appendix}
-
-\subsection{ETFs used in the study}\label{etfs-used-in-the-study}
-
-\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
-
-\global\setlength{\Oldtabcolsep}{\tabcolsep}
-
-\setlength{\tabcolsep}{2pt}
-
-\renewcommand*{\arraystretch}{0.7}
-
-\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}
-
-\begin{longtable}[l]{|p{5.39in}}
-
-\caption{\label{tbl-data}List of green ETFs used in the study}
-
-\tabularnewline
-
-\ascline{1pt}{000000}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} \\
-
-\ascline{1pt}{000000}{1-1}\endfirsthead
-
-\ascline{1pt}{000000}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ETF}}}} \\
-
-\ascline{1pt}{000000}{1-1}\endhead
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ALPS\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLUE\ HORIZON\ BNE\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ S\&P\ KENSHO\ CLEAN\ POWER\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ CLEANTECH\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{PROSHARES\ S\&P\ KENSHO\ CLEANTECH\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ MSCI\ SUSTAINABLE\ FUTURE\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIRST\ TRUST\ GLOBAL\ WIND\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FIDELITY\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLDS.BLOOMBERG\ CN.\ EN.\ EQ.ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ SMRT.GRID\ INFRA\ IDX\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DEFIANCE\ NEXT\ GEN\ H2\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{DIREXION\ HYDROGEN\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ HYDROGEN\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{ISHARES\ GLOBAL\ CLEAN\ EN.\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{BLACKR.WLD.EXUS\ CRBN\ TSTN.READINESS}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUB.CBN.TSTN.\&\ INFRA}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TCW\ TRANSFORM\ SYSTEMS\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ URANIUM\ AND\ NUCLEAR\ ENERGY}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{NUVEEN\ GLOBAL\ NET\ ZERO\ TRANSITION\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SPDR\ MSCI\ USA\ CIM.\ PA.\ ALIGNED\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ GLOBAL\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{FST.NQ.CN.EDGE\ GREY.ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ SOLAR\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ RENEWABLE\ ENERGY\ PRODUCERS}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{TRUESHARES\ EAG.GLB.\ RENWEN.ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VANECK\ LOW\ CARBON\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{SMARTETFS\ SUST.EN.\ II\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{INVESCO\ SOLAR\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{VIRTUS\ DUFF\ \&\ PHELPS\ CLEAN\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{FFFFFF}{1-1}
-
-\multicolumn{1}{!{\color[HTML]{FFFFFF}\vrule width 1pt}>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}!{\color[HTML]{FFFFFF}\vrule width 1pt}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{GLOBAL\ X\ WIND\ ENERGY\ ETF}}}} \\
-
-\ascline{1pt}{000000}{1-1}
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 5.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{Arial}{Note:\ Details\ on\ these\ funds\ can\ be\ found\ on\ Yahoo\ Finance.}}}} \\
-
-\end{longtable}
-
-\arrayrulecolor[HTML]{000000}
-
-\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}
-
-\global\setlength{\tabcolsep}{\Oldtabcolsep}
-
-\renewcommand*{\arraystretch}{1}
 

### 2025-03-31 alt_energy_herding.qmd
comments

@@
 editor: source
-bibliography: energy_herding.bib
+bibliography: references.bib
 biblio-style: apalike
@@
 
-# Introduction and literature review
+# Introduction
 
@@
 The growing interest in climate sustainability is primarily driven by the increasing materialisation of climate risks, and the actions of governments, institutions and organizations towards a sustainable future [@giglio2021a].
-To ensure returns, investors increasingly seek to hedge against climate risks by investing in green financial products.
-Although the evidence is mixed, indications that returns from green financial products are comparable to traditional financial [see amongst others, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
-
+To safeguard returns, investors increasingly seek to hedge against climate risks by investing in green financial products.
+Although the evidence from the existing literature is mixed, returns from green financial products are somewhat comparable to traditional financial products [see amongst others, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
 In this new climate sustainability paradigm, investors face many pressures that not only bear on returns but also the stability of financial markets.
 For example, resulting regulations aimed at reducing emissions can surprisingly reduce the profitability of fossil-fuel-based companies, or the possible mispricing of assets from ignoring climate risks can lead to significant losses [@nguyen2025].
-In addition to these climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio can lead to systemic risk.^[These pressures notwithstanding the possible contribution that financial markets can play in mitigating and reducing the negative effects of climate change [@giglio2021a]]
-
-Specifically, climate change presents risks to investor portfolios through two primary sources - physical and transition risks.
+In addition to climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio can lead to systemic risk.^[These pressures notwithstanding the possible contribution that financial markets can play in mitigating and reducing the negative effects of climate change [@giglio2021a]] Specifically, climate change presents risks to the global financial system, and ultimately to investment portfolios, through two primary sources - physical and transition risks.
 Physical risks or direct impact refer to extreme climate events such as floods and droughts, which impact business operations and infrastructure; and transition risks are the policy, technological, and other costs that societies bear to achieve low carbon economies [@nguyen2025; and @giglio2021a amongst others].
@@
 Exchange-traded funds (ETFs) are a key feature of green financial products.
-ETFs are a type of security that involves a collection of securities that often tracks an underlying index.
-However, they can invest in various industry sectors or strategies.
-In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in environmentally friendly companies [@briere2023].
-Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing ones in 2022, followed by the Cybersecurity and Artificial Intelligence (AI) ETFs [@decclesia2024].
-The clean energy transition represents one of the largest multi-decade secular growth opportunities.
+They are a collection of investments that often tracks an underlying performance of an asset or index.
+In the universe of environment, social, and governance (ESG) investments, clean ETFs serve as a tool for environmentally conscious investors to identify and invest in environmentally friendly companies [@briere2023] engaged in the transition towards a cleaner production and a low-carbon economy.
+Among the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing one in 2022 [@decclesia2024].
+This is not surprising given that the clean energy transition represents one of the largest multi-decade secular growth opportunities.
 After the inclusion of Green energy financing in the list of United Nations Sustainability Goals (SDGs) as SDG 7, the role, importance, and visibility of green financial products have escalated enormously [@naqvi2022].
 That is, the growth of green assets under management is likely to continue.
-Lastly, the limited availability of data on ESG complying investment tools [@avramov2022; @nguyen2025] justifies the use of green (CE) ETFs as best candidates of green assets.
+Furthermore, the limited availability of data on ESG complying investment tools [@avramov2022; @nguyen2025] justifies the use of energy ETFs as best candidates of green assets.
+However, given that the inclusion of climate sustainability in investment decisions is a recent phenomenon, it is not clear what the actual impact will be in the long-run.
 
-However, given how recent the inclusion of climate sustainability in investment decisions is, it is not clear what the actual impact will be in the long run.
-In this study specifically, we ask whether the rapid adoption of CE ETFs could be driven by market fads, or is a fundamental change in investor behaviour.
-Investors, for example, can believe that peers have information about climate risks that they do not, investors may herd to avoid losses compared to peers, or investors may be encouraged to herd by the desire to align to climate-related social values [@ciciretti2021; @gavrilakis2023; @loang2023].
-Therefore, market volatility and crisis, financial performance, and investor sentiment can drive herding in ESG markets.
+This study investigates herding behaviour in alternative (clean) energy ETFs in the US between May 1 2016 and June 19 2024, showing evidence of significant herding that is asymmetric and time-varying.
+We then study whether climate-related uncertainty can affect the herding behaviour in the US clean energy ETFs market.
+Methodologically, we follow the standard herding tests by @christie1995 and @chang2000.
+Notably, we supplement the traditional approach with quantile regressions [@koenker1978 ] in order to capture how herding differs across various quantiles of the returns dispersion and in up and down markets.
+Lastly, to establish a link between climate risk and herding behaviour, we differentiating between transitional and physical risks [@bua2024] and provide valuable insights on their potential impact on the likelihood of herding in clean energy ETFs.
 
-It is well established that herding literature is vast with contradictory results depending mainly on the market, the employed methodology and the period under consideration [@spyrou2013].
-Herding behavior can be either spurious in cases when investors make similar decisions as a result of processing the same information set and intentional herding when investors imitate the actions of others [see inter alia, @bikhchandani2000; @galariotis2015].
-Empirical studies on herding usually fall into two categories: namely those that employ holdings data aiming at measuring institutional investor herding [@lakonishok1992], and studies that use market returns data and investigate herding towards the market consensus [@chang2000; @galariotis2015].
-Our paper falls within the latter category and tests for herding towards the market consensus for clean energy US ETFs.
+In this study specifically, we ask whether the rapid adoption of clean energy ETFs could be driven by market fads, or is a fundamental change in investor behaviour.
+Investors, for example, can believe that their peers have more valuable information about climate risks, making them to herd to avoid losses compared to peers; alternatively, investors may be encouraged to herd by the desire to align to climate-related social values [@ciciretti2021; @gavrilakis2023; @loang2023].
+Investors in clean energy stocks can experience large losses if their betting on clean energy stocks go wrong, which represents a major concern in their decision-making process.
+This incites those investors to disregard their own information and follow the market consensus, leading to significant herding behaviour in the clean energy market.
+@devenow1996 indicate that following the market consensus induces some kind of security among less informed traders.
+This could be relevant to our analysis because ETFs represent a popular investment instrument for individual and retail investors who are not necessarily well informed about the risk and prospects of investments in clean energy firms and whether their contribution to the world transition to cleaner production should be financially lucrative.
+On a related front, the self-reinforcing nature of confidence in the tyranny of the majority, as indicated by @teraji2003 could also be pertinent.
 
-Herding behaviour in ESG markets is not without precedent.
-Amongst others, @loang2023 found that compliance with SDG goals can introduce bias in investor sentiment, which leads to herding behaviour.
-Using a Twitter (or X) uncertainty index, @koutmos2024 found evidence of herding in US-based ESG index fund investors.
-@przychodzen2016 found herding behaviour amongst fund managers who incorporated ESG strategies in their portfolios.
-Lastly, @rubbaniy2021 highlight evidence of herding in the MSCI US ESG Leader Index during extreme periods (bear and bull periods).
+While herding behaviour has been examined in ESG markets, it remains understudied in clean energy assets, notably, clean energy ETFs.^[Amongst others, @loang2023 shows that compliance with SDG goals can introduce bias in investor sentiment, which leads to herding behaviour.
+Using a Twitter (or X) uncertainty index, @koutmos2024 finds evidence of herding in US-based ESG index fund investors.
+@przychodzen2016 found indicate evidence of herding behaviour amongst fund managers who incorporated ESG strategies in their portfolios.
+Lastly, @rubbaniy2021 highlight evidence of herding in the MSCI US ESG Leader Index during extreme (bear and bull periods) periods.] Other studies on herding have been conducted in commodity and fossil energy markets.
+For example, @demirer2013 conducted a commodity sectoral study and found herding behaviour in grains but not in other sectors.
+Similarly, @gilbert2010 shows herding behaviour amongst speculators in non-ferrous commodities.
+Others did not find evidence of herding in similar markets.
+@babalos2015 find significant anti-herding behaviour in metal commodities futures after the global financial crisis.
+@pierdzioch2010 show that forecasters in oil and metals markets deviated from the crowd, indicating a rational response to market information.
+@steen2013 find no herding behaviour in international commodity markets.
+Notably,  our study extends the results of @dragomirescu-gaina2021 who have examined herding behavior of investors in the US energy sector and herding sensitivity to various proxies of policy uncertainty and financial risk.
+They study the energy equities included in the S&P 500 and concluded that herding among investors in the US energy market sector is sensitive to green volatility shocks
 
-However, to the best of our knowledge, no studies exist that focus on herding behaviour in CE ESGs.
-This study, therefore, aims to extend the broader literature on herding behaviour in commodity and energy markets.
-Several studies in this area were conducted.
-For example, @demirer2013a conducted a commodity sectoral study and found herding behaviour in grains but not in other sectors.
-Similarly, @gilbert2010 showed herding behaviour amongst speculators in non-ferrous commodities.
-Others did not find evidence of herding in similar markets.
-@babalos2015 found significant anti-herding behaviour in metal commodities futures after the global financial crisis.
-@pierdzioch2010 showed that forecasters in oil and metals markets deviated from the crowd, indicating a rational response to market information.
-@steen2013 also found no herding behaviour in international commodity markets.
-Overall, the literature in this area is mixed, which indicates scope for further study.
-
-In addition, our study extends the results of @dragomirescu-gaina2021 who examined herding behavior of investors in the US energy sector and herding sensitivity to various proxies of policy uncertainty and financial risk.
-They employed the energy equities included in the S&P 500 and concluded that herding among investors in the US energy market sector is sensitive to green volatility shocks
-
-Therefore,  this study investigates herding behaviour in alternative energy ETFs in the US between 2016 and 2024.
-We then demonstrate how climate-related uncertainty can drive herding behaviour in these markets.
-Methodologically, we follow the standard herding tests by @christie1995 and @chang2000.
-The traditional approach was supplemented by quantile regressions [@koenker1978 ] in order to capture the time-varying aspects of herding.
-Lastly,  we extend recent approaches by @bua2024 and others, which seek to establish a link between climate uncertainty and herding behaviour.
+Our analysis shows that herding is significant and is present in both down and up markets, with a stronger effect in the down market, suggesting an asymmetry.
+Herding is also found to be time-varying.
+Notably, an additional analysis reveals that the transition climate risk, particularly its high level, reduces the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on the probability of herding
 
@@
 
-The sample consists of alternative energy equity ETFs (green ETFs) that are traded in the US markets (see @tbl-data in the Appendix).^[The data were sourced from \url{https://datastream.org/en-ca/}] The number of available alternative energy ETFs in our sample varied from 10 in the beginning of analysis to 30 at the most.
-The period of analysis runs from May 1^st^ of 2016 through 19^th^ June of 2024.
+The sample consists of clean energy equity ETFs (green ETFs) that are traded in the US markets (see @tbl-data in the Appendix).^[The data were sourced from \url{https://datastream.org/en-ca/}] The number of available clean energy ETFs in our sample varied from 10 in the beginning of analysis to 30 at the most.
+The period of analysis runs from May 1 2016 to 19 June 2024.
+Daily closing prices on the clean energy ETFs under study were collected from the Refinitiv database.
 The starting date was selected on the basis of the UN Climate Change Conference (COP) Paris agreement.
-Daily logarithmic returns were computed from the closing prices of ETFs for a total of 2122 observations.
+Daily logarithmic returns were computed from the closing prices of each ETF, yielding, a total of 2122 observations per ETF.
 
@@
 #| fig.width: 8
+#| include: true
+#| eval: true
 
@@
 #| cache: false
+#| include: true
+#| eval: true
 
@@
 
-Following the relevant literature [@christie1995; and @chang2000], we compute dispersion of the $i^{th}$ ETF from the market return.
-This is known as the Cross Sectional Absolute Deviation  ($CSAD_t$) measure.
+It is well established that herding literature is vast with contradictory results depending mainly on the market, the employed methodology and the period under consideration [@spyrou2013].
+Herding behavior can be either spurious in cases when investors make similar decisions as a result of processing the same information set and intentional herding when investors imitate the actions of others [see inter alia @bikhchandani2000; @galariotis2015].
+Empirical studies on herding usually fall into two categories: namely those that employ holdings data aiming at measuring institutional investor herding [e.g.
+@lakonishok1992], and studies that use market returns data and investigate herding towards the market consensus [e.g.
+@chang2000; @galariotis2015].
+Our paper falls within the latter category and tests for herding towards the market consensus for clean energy US ETFs.
+
+Following the relevant literature [@christie1995; and @chang2000], we compute dispersion of the $i^{th}$ ETF from the market return, which is known as the Cross Sectional Absolute Deviation  ($CSAD_t$) measure.
 Empirically the $CSAD_t$ is defined in the following manner:
@@
 
-Based on the above and in order to provide additional insight on the herding phenomenon we examine whether herding presents an asymmetric response on days when the market is up vis-à-vis days when the market is down.
+To provide additional insight on the herding phenomenon we examine whether herding presents an asymmetric response on days when the market is up vis-à-vis days when the market is down.
 To this end, we augment @eq-herding as follows:
@@
 In other words, herding is captured by a non-linear term in the standard pricing equation indicating a decreasing or an increasing returns’ dispersion.
+Stated differently, as @chang2000 argue, in the case of herding the coefficient on the non-linear term ($\gamma_2$) will be negative and statistically significant.
 
-Stated differently, as @chang2000 argue, in the case of herding the coefficient on the non-linear term ($\gamma_2$) will be negative and statistically significant.
-@tbl-herding presents the results of herding for the full sample employing the non-linear @eq-herding.
+@tbl-herding presents the results of herding for the full sample, based on @eq-herding.
 The estimated coefficient on market return is positive and highly significant as expected.
-The estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behaviour is present and robust in the US alternative energy ETFs.
+Importantly, the estimated coefficient on the non-linear term is negative (-1.2773) and statistically significant with a t-statistic of -9.71 suggesting that herd behaviour is present and robust in the US alternative energy ETFs.
+Accordingly, investors in US clean energy ETFs tend to disregard their private information and follow market consensus.
 
@@
 
-There is ample evidence in the relevant literature that herding behaviour in various asset markets [see @pochea2017] exhibits asymmetry and time-varying characteristics.
-To this end, we proceed to estimate @eq-herding using the quantile regression (QR) proposed by @koenker1978.
-@tbl-quantile_herding presents the results of estimating @eq-herding across various quantiles of the returns dispersion.
-Our focus is on the herding coefficient $\gamma_2$, as a significant negative value of $\gamma_2$ is indicative of herding.
-Such a finding is observed at two quantiles namely 25% and 50% with a value of -1.1056 and -1.165 which are highly significant.
-It is worth mentioning that the sign of the herding coefficient remains negative for almost all quantiles while the significance changes from significant to insignificant while we move from low and middle to upper quantiles (75\% and 90\%).
+Evidence from the existing literature shows that herding behaviour in various asset markets [see @pochea2017] exhibits asymmetry.
+To this end, we proceed first  with the estimation of @eq-herding using the quantile regression (QR) proposed by @koenker1978.
+@tbl-quantile_herding presents the estimated results across various quantiles of the returns dispersion.
+They show that herding is statistically significant  at lower ($\tau= 25\%$), middle ($\tau =50\%$), and upper ($\tau=75\%$) with a value of -1.1056, -1.165, and -1.1473, respectively.
+No significant herding is found at extreme lower quantile ($\tau=10\%$) and extreme higher quantile ($\tau=90\%$).
 
@@
 
-It is widely accepted that asset returns are characterized by asymmetry, that is, return dispersion tend to behave differently in rising and falling markets [see @geert2000; @zhou2013; @longin2001].
-It should be noted, that examining the relationship between returns dispersion and market-wide returns across various quantiles of the returns distribution allows us to make more robust inference regarding the true behaviour of the phenomenon.
+Then, we study herding in up and down markets.
+It is widely accepted that asset returns are characterized by asymmetry, that is, return dispersion tend to behave differently in rising and falling markets [see @geert2000; @zhou2013; @longin2001],  with evidence suggesting that herding is more pronounced during periods of market stress.
+In this regard, examining the relationship between returns dispersion and market-wide returns across various quantiles of the returns distribution of clean energy ETFs allows us to make more robust inference regarding the true behaviour of the herding phenomenon.
 @tbl-asymmetry_herding reports the estimation results of herding in the up and down markets based on @eq-asymmetry.
-In general, we find that herding is more likely to occur in down markets than in up markets, which is indicative of the asymmetry of herding behaviour.
-
-\newpage
+In general, we find that herding is significant in both down and up markets
 
@@
     values = as_paragraph("Note: This table presents the estimation results of herding of US Alternative energy equity ETFs according to Equation (3).
+", as_equation("\\gamma_3"), " captures potential herding in the up market, whereas ", as_equation("\\gamma_4"), " captures potential herding in the down market.
 *,**,***denotes significance at 10%,5% and 1% respectively."
@@
 
-Herding is present at all quantiles when markets are rising with an estimated coefficient $\gamma_3$ of -1.3669 and -1.2383 and highly significant respectively.
-However, when markets are declining, investors seem to neglect their own information set and imitate the actions of others resulting in a highly significant coefficient of herding ($\gamma_4$) across four out of five quantiles.
-Furthermore, we find that in high quantiles (75\% and 90\%) and when markets are rising the coefficient of interest ($\gamma_3$) turns positive but insignificant.
+When the market is rising, herding is present at all quantiles with a statistically significant coefficient $\gamma_3$ ranging from -0.2522 ($\tau=10\%$) to -0.2942 ($\tau=90\%$) .
+Similarly, when markets are declining, investors neglect their own information set and imitate the actions of others resulting in a highly significant coefficient of herding ($\gamma_4$) across four out of five quantiles, ranging from -0.9721 to -1,3144.
+Notably, the coefficient of herding in down market is larger than in up market, reflecting an asymmetric herding behaviour.
 
@@
 
-There is ample evidence that herding might vary in response to market conditions [see @babalos2015; @klein2013; @stavroyiannis2019].
-In order to gain further insight on the time varying nature of herding we conducted a rolling window analysis.
+There is ample evidence that herding varies with time  [see @babalos2015; @klein2013; @stavroyiannis2019] and intensifies during crisis periods.
+In order to gain insights on the time-varying nature of herding in clean energy ETFs, we conduct a rolling window analysis.
 The size of the rolling window is related to the time-scales of the system (response times), and the aim of the research [@babalos2015].
 There is no golden rule for the right size of the rolling window, there is a trade-off between having a long enough window to estimate the metrics, and short enough to have a sufficient number of windows in order to be able to derive a trend.
-In light of the above discussion we set off to conduct a rolling window analysis of 50 observations.
-@fig-rolling_window plots the time evolution of the value of the estimated significance of the herding coefficient ($\gamma_2$) using the rolling window analysis.
+Accordingly, we conduct a rolling window analysis of 50 observations, and plot in @fig-rolling_window the time evolution of the value of the estimated significance of the herding coefficient ($\gamma_2$).
 
@@
 
+\newpage
 We observe several periods of herding behaviour as reflected in the troughs in @fig-rolling_window.
-The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 (when $\gamma_2$ averaged -45.5) and the period of February-March of 2023 (when $\gamma_2$ averaged -7.68).We observe significant herding in the onset of the COVID-19 crisis 2020, which was short lived as market adapted.
-The rest of the Covid period was in the main characterised by anti-herding behaviour.
-@ghorbel2023 and @dhall2020 found similar results.
-Lastly, similar to @mohamad2024 we observe no herding behaviour related to the Russia-Ukraine war.
-@mohamad2024 highlights the importance of context in understanding the link between herding and market events.
-On the other side, we derive significant moments of anti-herding behaviour in the clean energy ETFs by observing the spikes in @fig-rolling_window.
-Cross sectional dispersion appears to increase with respect to market-wide returns which is a sign of anti-herding behaviour on behalf of investors around December of 2016 and later during September of 2022.
+The most prominent cases of herding occur between March and May of 2020 followed by several instances of herding in the period that extends from March through April of 2017 and the period of February-March of 2023.
+On the other side, we derive significant moments of anti-herding behaviour in the clean energy ETFs by observing the peaks in @fig-rolling_window.
+Cross sectional dispersion appears to increase with respect to market-wide returns, which is a sign of anti-herding behaviour on behalf of investors around December of 2016 and later during September of 2022
 
-## Climate-related uncertainty and herding behaviour
+## Climate risks and herding behaviour
 
-The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies.
+The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions, and environmentally friendly policies.
+Rising climate risk is found to increase green energy prices [@dutta2023], and evidence from the existing literature shows that climate policy uncertainty affects the performance of clean energy stocks relative to dirty ones, making the former outperform the later when the levels of climate policy uncertainty are high [@bouri2022].
 In particular, following the implementation of the Paris agreement in November 2016, climate policy uncertainty has become in the epicenter of interest across carbon and energy markets.
-There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets [see inter alia, @gabriel2024; @bolton2021; @krueger2020].
-To this end, @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.
-It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets.
-Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.
+There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy or financial markets [see inter alia, @gabriel2024; @bolton2021; @krueger2020].
+Interestingly, @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.
+In this regard, @bouri2023 study the impact of both physical and climate risks on the returns and volatility of brown and green energy stocks, carbon emission allowances, and green bonds, showing evidence that transitional climate risk exerts a more significant impact than physical climate risk.
 
-We use a probit model to relate herding to the two climate risk indexes developed by @bua2024 in the following manner:
+It is expected that environmentally conscious investors would prefer to hold clean energy assets that perform well in the face of increasing climate change risks [see @bouri2022], even if this entails accepting lower returns for such climate-hedging assets.
+Therefore, in the context of our study and following previous studies on the determinants of herding behaviour [see @bouri2019; @demirer2018], we examine the effect of physical and transition climate risks on the formation of herding behavior in the clean energy ETF market.
+
+To this end, we use a probit model to relate herding to the two climate risk indexes developed by @bua2024 in the following manner:
 
@@
 $TRI$ is the transitional risk index and $PRI$ is the physical risk index.
+For details on the construction of $TRI$ and $PRI$, the reader can refer to the paper of @bua2024.
 
-The results from the Probit model are reported in @tbl-probit_analysis, where only the physical risk index significantly decreases the probability of herding.^[It should be noted that due to availability issues the probit analysis ends in December of 2023.] In other words, climate risks is good news for clean energy stocks or firms resulting in anti-herding behaviour.
-This implies that in the presence of higher physical risk with respect to the climate, clean energy ETFs become a more attractive investment option for investors that allocate their money to the various alternative energy investment products.
+The results from the Probit model are reported in @tbl-probit_analysis.
+Showing that only the transitional climate risk index significantly decreases the probability of herding in clean energy ETFs.^[It should be noted that due to the availability of climate risk data from @bua2024, the probit analysis covers the period from May 1, 2016 to December 30, 2023.] Transitional climate risk represent good news for investors in clean energy stocks, possibly reducing their self-reinforcing nature of confidence in the tyranny of the majority [@teraji2003]) and their need for shared intention and action, resulting in a decrease in the herding behaviour.
+In the presence of higher transitional risk with respect to the climate, clean energy ETFs become a more attractive investment alternative for environmentally conscious investors who allocate their money to alternative energy investment products [see @bouri2022], reinforcing the confidence of investors in their own information.
 As a result, the cross-sectional dispersion of clean energy ETFs tends to increase.
-Our results are in line with those of relevant studies such as @gabriel2024 who claimed that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments.
+Our results are somewhat in line with @bouri2023 who show that the transitional climate risk is more important than physical risk for the return and volatility of clean energy stocks.
+They also concord with other relevant studies which indicate that in the event of climate policy shocks, clean energy assets could serve the role of hedging instruments [@gabriel2024] and tend to outperform brown energy assets [@bouri2022].
 
@@
 
-Furthermore, we develop two additional models to study the effect of climate risks on herding behaviour.
-We split the sample into two groups based on the median value of the TRI and PRI.
-We then estimate the following two models:
+Furthermore, we develop two additional models to study the effect of high and low levels of climate risks on herding behaviour in clean energy ETFs.
+Accordingly, we split the sample into two groups based on the median value of the $TRI$ and $PRI$ and estimate the following two models:
 
@@
 where $D^{herd}$ is the same as in @eq-climate.
-$D^{TRI}_{high}$ and $D^{PRI}_{high}$ are dummy variables that take a value of 1 if the value of the TRI and PRI are above the median and zero otherwise.
-Similarly, $D^{TRI}_{low}$ and $D^{PRI}_{low}$ are dummy variables that take a value of 1 if the value of the TRI and PRI are below the median and zero otherwise.
+$D^{TRI}_{high}$ and $D^{PRI}_{high}$ are dummy variables that take a value of 1 if the values of the $TRI$ and $PRI$ are above the median and zero otherwise.
+Similarly, $D^{TRI}_{low}$ and $D^{PRI}_{low}$ are dummy variables that take a value of 1 if the values of the $TRI$ and $PRI$ are below the median and zero otherwise.
 
@@
 
-We use these high PRI and high TRI in one probit regression and low TRI and low PRI in another.
-Results are presented in @tbl-probit_analysis2.
-We observe higher uncertainty that stems from physical or transition risk causes anti-herding which is in line with the logic we discussed earlier.
+Using these high $PRI$ and high $TRI$ in one probit regression and low $TRI$ and low $PRI$ in another one, we present the results in @tbl-probit_analysis2.
+We observe that high levels of transition risk decrease the likelihood of herding (i.e.
+drives anti-herding) at the 10% level of significance, which is in line with the logic we discussed earlier.
 
@@
 
-This study offers novel and valuable insights into herding behaviour in clean energy ETFs.
+This study offers novel and valuable insights into herding behaviour in US clean energy ETFs.
 We used various herding behaviour tests to achieve this.
-First, the baseline herding tests revealed significant evidence of herding behaviour.
-Second, the asymmetric herding tests showed that herding behaviour was present in both bear and bull markets.
-Lastly, the results of the time-varying tests point to significant periodic herding.
-However, the results further indicate that herding in US clean energy ETFs was not mainly related to climate-related risks or uncertainty.
-The probit analysis showed that climate-related uncertainty reduced the probability of herding or led to investor anti-herding behaviour.
-We differ to the literature on the factors that drive herding in these ETFs [for example, @loang2023;  @koutmos2024; @przychodzen2016].
-Our results, similar to @bua2024, indicate that investors did not herd on climate-related uncertainty, and sought returns whilst hedging against climate-related risk.
-This is a positive for the financial stability of these growing alternative investment indices.
+First, herding is found to be significant, and exists in both bearish and bullish markets, but shows an asymmetry in that it is more pronounced in the bearish market.
+Herding is also found to time-varying.
+Second, the transition climate risk, particularly its high levels,  reduce the probability of herding behaviour, whereas physical climate risk plays no significant role irrespective of its (high or low) levels.
+This evidence that climate risks do not lead to higher herding behaviour in the clean energy ETFs, is new to the related literature.
+
+Our findings offer an interesting outlook on the role of transitional climate risk for the formation of herding in clean energy ETFs, which is a puzzle in the related literature.
+Given that herding represents a behavioural pattern that can challenge market efficiency and exacerbate price fluctuations, both policymakers and investors should benefit  from our findings for the sake of investment decision and market efficiency under the transition towards cleaner production and decarbonized portfolio investments.
+Future studies could examine whether herding in clean energy ETFs is linked to excess volatility in the overall US stock market.
 
@@
 #| label: tbl-data
-#| tbl-cap: "List of green ETFs used in the study"
+#| tbl-cap: "List of clean energy ETFs used in the study"
 #| cache: false

### 2025-03-31 title.tex
comments

@@
-\title{Do investors in clean energy ETFs herd?}
+\title{Do investors in clean energy ETFs herd? The role of climate risks}
 
-\author { 
+\author{ 
 Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
@@
 
-ipsum
+This study offers new insights into the herding behaviour in US clean energy Exchange-traded funds (ETFs) over the period from May 1, 2016 to June 19, 2024. 
+The baseline model shows significant herding. An extended mode indicates that herding is present in both down and up markets, with a stronger effect in the down market, suggesting an asymmetry. 
+Herding is also found to be time-varying.
+Further analysis shows that the transition climate risk, particularly its high level, reduces the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on the probability of herding.
+Thus, large levels of transition climate risk seem to encourage market efficiency in clean energy ETFs  and climate-hedging behavior by investors.
 
@@
 
-\noindent\textbf{Keywords}: Herding Behaviour, Financial Crises, Market Efficiency
+\noindent\textbf{Keywords}: Herding Behaviour, Climate Change, Clean Energy
 \\
-\textbf{JEL Codes}: G01, G14, G15, G41
+\textbf{JEL Codes}: G14, Q54, P18
 \newpage

### 2025-04-03 Journal/journal_submission/alt_energy_herding_full.tex
journal submission

@@
 \author{ 
-Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
+Vassilios Babalos\footnote{Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
 Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.

### 2025-06-25 alt_energy_herding.qmd
added from comments

@@
 
-Exchange-traded funds (ETFs) are a key feature of green financial products.
+Energy market has been in the epicentre of retail investors and portfolio managers at least over the last two decades.
+Official estimates claim that global energy investment is expected to surpass USD 3 trillion for the first time in 2024, with USD 2 trillion going to clean energy technologies and infrastructure [@iea2024].
+There is a general consensus in the literature that the most important event that has shaped the current landscape in the energy sector is the emergence of the energy portfolio with the rise of green energy as an alternative energy resource and an asset class.
+Price volatility of fossil fuels on the one hand and decarbonisation-related goals dictated by international agreements on the other hand are heavily responsible for the growing interest in green energy market.
+Responding to the increasing awareness about the environment and the need for more green capital, financial markets have also attracted a large portion of retail and institutional investors’ fund flows [@rizvi2022green; @naqvi2021there].
+
+Needless to mention that the rise of energy popularity as an alternative investment class has also been fueled by the fictionalization of commodities markets.
+Commodities have become an effective investment tool for investment community as it allows investors to participate in the market developments across various physical products such as agricultural products, silver, gold, natural gas, oil etc and more recently clean energy products without being obliged to own the product directly [@gagnon2020they].
+Several academic studies have highlighted substantial diversification benefits of commodities when added to a portfolio of stocks and bonds [see inter alia, @naqvi2022].
+
+Green energy sectors like solar, wind, geothermal, biofuels, biomass, wave, hydro and tidal energies are considered by investors, authorities and policy-makers as the substitutes for fossil-fuels energy that increase CO2 emissions [@shahzad2020clean].
+Moreover, as @naqvi2022 point out that "the alternative energy sector is expected to grow faster over the next decades due to the depletion of fossil fuel reserves and the technological advance that has made green energy feasible".
+
+Although green energy investment has witnessed an exponential growth over the years, there is a lot of improvement that can be done in terms of investors’ participation, both retail and institutional.
+To achieve the goal of larger capital commitment to green energy projects it is important to gain investors’ confidence in financial products that are linked to green energy such as Exchange-traded funds(ETFs).
+
+ETFs are a key feature of green financial products.
 They are a collection of investments that often tracks an underlying performance of an asset or index.
@@
 
-Following the relevant literature [@christie1995; and @chang2000], we compute dispersion of the $i^{th}$ ETF from the market return, which is known as the Cross Sectional Absolute Deviation  ($CSAD_t$) measure.
+More broadly, studies that focus on herding can be broadly classified into two main categories:  on the one hand there are studies that examine institutional investor herding and analyst herding using transaction-level data [@lakonishok1992; and @sias2004institutional, among others].
+On the other hand, there are studies that explore herding towards the market consensus employing individual returns and market returns [@christie1995; and @chang2000].
+In the latter case, the most widely employed method is the cross-sectional standard deviation of returns proposed by @christie1995.
+The intuition behind this approach is that herding toward the market is signaled when return dispersion is relatively low.
+Rational asset pricing theory predicts that when stocks respond to market movements in various degrees then dispersion will be linearly related to market returns [see also, @hwang2004market].
+However, when investors tend to mimic each other and herd towards the market the linear relation between returns dispersion and aggregate market returns is no longer valid.
+Under these conditions, fitting a non-linear regression specification between a measure of returns dispersion and aggregate market return appears as a more viable choice.
+Therefore, our approach to measure herding activity is based on the non-linear regression model by @chang2000.
+
+Following this relevant literature, we compute dispersion of the $i^{th}$ ETF from the market return, which is known as the Cross Sectional Absolute Deviation  ($CSAD_t$) measure.
 Empirically the $CSAD_t$ is defined in the following manner:
@@
 In general, we find that herding is significant in both down and up markets
+
+\newpage
 
@@
 Therefore, in the context of our study and following previous studies on the determinants of herding behaviour [see @bouri2019; @demirer2018], we examine the effect of physical and transition climate risks on the formation of herding behavior in the clean energy ETF market.
+
+Furthermore, higher transition risk means greater uncertainty for future pathway towards a cleaner economy.
+Under these conditions, green assets such as green stocks or ETFs are expected to perform better and can serve as hedging tools [see inter alia @pastor].
+As a result, investors allocate their capital to available green assets thus resulting in higher returns’ dispersion with respect to the aggregate market.
+Stated differently, investors move their capital away from market consensus across green ETFs ruling out the possibility of herding behavior.
 

### 2025-06-25 alt_energy_herding.tex
added from comments

@@
+% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
   numbers=noendperiod]{scrartcl}
-
+\usepackage{xcolor}
 \usepackage{amsmath,amssymb}
-\usepackage{setspace}
+\setcounter{secnumdepth}{5}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 }{}
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
+\usepackage{setspace}
 % Make \paragraph and \subparagraph free-standing
@@
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
 \makeatother
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage[round]{natbib}
+\bibliographystyle{apalike}
 
@@
 \makeatother
-
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\usepackage[round]{natbib}
-\bibliographystyle{apalike}
 \usepackage{bookmark}
-
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \date{}
-
 \begin{document}
 
-\title{Do investors in clean energy ETFs herd?}
+\title{Do investors in clean energy ETFs herd? The role of climate risks}
 
@@
 risks can lead to significant losses \citep{nguyen2025}. In addition to
-these climate risks, a general change in investor attitudes can drive
-the inclusion of green assets in their portfolio can lead to systemic
+climate risks, a general change in investor attitudes can drive the
+inclusion of green assets in their portfolio can lead to systemic
 risk.\footnote{These pressures notwithstanding the possible contribution
   that financial markets can play in mitigating and reducing the
-  negative effects of climate change \citep{giglio2021a}}
-
-Specifically, climate change presents risks to investor portfolios
-through two primary sources - physical and transition risks. Physical
-risks or direct impact refer to extreme climate events such as floods
-and droughts, which impact business operations and infrastructure; and
-transition risks are the policy, technological, and other costs that
-societies bear to achieve low carbon economies
-\citetext{\citealp{nguyen2025}; \citealp[and][ amongst
-others]{giglio2021a}}. Investors, therefore, recognise these risks and
-seek to mitigate them, as they seek return-enhancing green financial
-products.
-
-Exchange-traded funds (ETFs) are a key feature of green financial
-products. ETFs are a type of security that involves a collection of
-securities that often tracks an underlying index. However, they can
-invest in various industry sectors or strategies. In addition,
-environment, social, and governance (ESG) ETFs serve as a market
-discovery tool for investors to identify and invest in environmentally
-friendly companies \citep{briere2023}. Among the ESG ETFs, the Clean
-Energy (CE) ETFs have been the best-performing ones in 2022, followed by
-the Cybersecurity and Artificial Intelligence (AI) ETFs
-\citep{decclesia2024}. The clean energy transition represents one of the
-largest multi-decade secular growth opportunities. After the inclusion
-of Green energy financing in the list of United Nations Sustainability
-Goals (SDGs) as SDG 7, the role, importance, and visibility of green
-financial products have escalated enormously \citep{naqvi2022}. That is,
-the growth of green assets under management is likely to continue.
-Lastly, the limited availability of data on ESG complying investment
-tools \citep{avramov2022, nguyen2025} justifies the use of green (CE)
-ETFs as best candidates of green assets.
-
-However, given how recent the inclusion of climate sustainability in
-investment decisions is, it is not clear what the actual impact will be
-in the long run. In this study specifically, we ask whether the rapid
-adoption of CE ETFs could be driven by market fads, or is a fundamental
-change in investor behaviour. Investors, for example, can believe that
-peers have information about climate risks that they do not, investors
-may herd to avoid losses compared to peers, or investors may be
+  negative effects of climate change \citep{giglio2021a}} Specifically,
+climate change presents risks to the global financial system, and
+ultimately to investment portfolios, through two primary sources -
+physical and transition risks. Physical risks or direct impact refer to
+extreme climate events such as floods and droughts, which impact
+business operations and infrastructure; and transition risks are the
+policy, technological, and other costs that societies bear to achieve
+low carbon economies \citetext{\citealp{nguyen2025}; \citealp[and][
+amongst others]{giglio2021a}}. Investors, therefore, recognise these
+risks and seek to mitigate them, as they seek return-enhancing green
+financial products.
+
+Energy market has been in the epicentre of retail investors and
+portfolio managers at least over the last two decades. Official
+estimates claim that global energy investment is expected to surpass USD
+3 trillion for the first time in 2024, with USD 2 trillion going to
+clean energy technologies and infrastructure \citep{iea2024}. There is a
+general consensus in the literature that the most important event that
+has shaped the current landscape in the energy sector is the emergence
+of the energy portfolio with the rise of green energy as an alternative
+energy resource and an asset class. Price volatility of fossil fuels on
+the one hand and decarbonisation-related goals dictated by international
+agreements on the other hand are heavily responsible for the growing
+interest in green energy market. Responding to the increasing awareness
+about the environment and the need for more green capital, financial
+markets have also attracted a large portion of retail and institutional
+investors' fund flows \citep{rizvi2022green, naqvi2021there}.
+
+Needless to mention that the rise of energy popularity as an alternative
+investment class has also been fueled by the fictionalization of
+commodities markets. Commodities have become an effective investment
+tool for investment community as it allows investors to participate in
+the market developments across various physical products such as
+agricultural products, silver, gold, natural gas, oil etc and more
+recently clean energy products without being obliged to own the product
+directly \citep{gagnon2020they}. Several academic studies have
+highlighted substantial diversification benefits of commodities when
+added to a portfolio of stocks and bonds \citep[see inter
+alia,][]{naqvi2022}.
+
+Green energy sectors like solar, wind, geothermal, biofuels, biomass,
+wave, hydro and tidal energies are considered by investors, authorities
+and policy-makers as the substitutes for fossil-fuels energy that
+increase CO2 emissions \citep{shahzad2020clean}. Moreover, as
+\citet{naqvi2022} point out that ``the alternative energy sector is
+expected to grow faster over the next decades due to the depletion of
+fossil fuel reserves and the technological advance that has made green
+energy feasible''.
+
+Although green energy investment has witnessed an exponential growth
+over the years, there is a lot of improvement that can be done in terms
+of investors' participation, both retail and institutional. To achieve
+the goal of larger capital commitment to green energy projects it is
+important to gain investors' confidence in financial products that are
+linked to green energy such as Exchange-traded funds(ETFs).
+
+ETFs are a key feature of green financial products. They are a
+collection of investments that often tracks an underlying performance of
+an asset or index. In the universe of environment, social, and
+governance (ESG) investments, clean ETFs serve as a tool for
+environmentally conscious investors to identify and invest in
+environmentally friendly companies \citep{briere2023} engaged in the
+transition towards a cleaner production and a low-carbon economy. Among
+the ESG ETFs, the Clean Energy (CE) ETFs have been the best-performing
+one in 2022 \citep{decclesia2024}. This is not surprising given that the
+clean energy transition represents one of the largest multi-decade
+secular growth opportunities. After the inclusion of Green energy
+financing in the list of United Nations Sustainability Goals (SDGs) as
+SDG 7, the role, importance, and visibility of green financial products
+have escalated enormously \citep{naqvi2022}. That is, the growth of
+green assets under management is likely to continue. Furthermore, the
+limited availability of data on ESG complying investment tools
+\citep{avramov2022, nguyen2025} justifies the use of energy ETFs as best
+candidates of green assets. However, given that the inclusion of climate
+sustainability in investment decisions is a recent phenomenon, it is not
+clear what the actual impact will be in the long-run.
+
+This study investigates herding behaviour in alternative (clean) energy
+ETFs in the US between May 1 2016 and June 19 2024, showing evidence of
+significant herding that is asymmetric and time-varying. We then study
+whether climate-related uncertainty can affect the herding behaviour in
+the US clean energy ETFs market. Methodologically, we follow the
+standard herding tests by \citet{christie1995} and \citet{chang2000}.
+Notably, we supplement the traditional approach with quantile
+regressions \citep{koenker1978} in order to capture how herding differs
+across various quantiles of the returns dispersion and in up and down
+markets. Lastly, to establish a link between climate risk and herding
+behaviour, we differentiating between transitional and physical risks
+\citep{bua2024} and provide valuable insights on their potential impact
+on the likelihood of herding in clean energy ETFs.
+
+In this study specifically, we ask whether the rapid adoption of clean
+energy ETFs could be driven by market fads, or is a fundamental change
+in investor behaviour. Investors, for example, can believe that their
+peers have more valuable information about climate risks, making them to
+herd to avoid losses compared to peers; alternatively, investors may be
 encouraged to herd by the desire to align to climate-related social
-values \citep{ciciretti2021, gavrilakis2023, loang2023}. Therefore,
-market volatility and crisis, financial performance, and investor
-sentiment can drive herding in ESG markets.
-
-It is well established that herding literature is vast with
-contradictory results depending mainly on the market, the employed
-methodology and the period under consideration \citep{spyrou2013}.
-Herding behavior can be either spurious in cases when investors make
-similar decisions as a result of processing the same information set and
-intentional herding when investors imitate the actions of others
-\citep[see inter alia,][]{bikhchandani2000, galariotis2015}. Empirical
-studies on herding usually fall into two categories: namely those that
-employ holdings data aiming at measuring institutional investor herding
-\citep{lakonishok1992}, and studies that use market returns data and
-investigate herding towards the market consensus
-\citep{chang2000, galariotis2015}. Our paper falls within the latter
-category and tests for herding towards the market consensus for clean
-energy US ETFs.
-
-Herding behaviour in ESG markets is not without precedent. Amongst
-others, \citet{loang2023} found that compliance with SDG goals can
-introduce bias in investor sentiment, which leads to herding behaviour.
-Using a Twitter (or X) uncertainty index, \citet{koutmos2024} found
-evidence of herding in US-based ESG index fund investors.
-\citet{przychodzen2016} found herding behaviour amongst fund managers
-who incorporated ESG strategies in their portfolios. Lastly,
-\citet{rubbaniy2021} highlight evidence of herding in the MSCI US ESG
-Leader Index during extreme periods (bear and bull periods).
-
-However, to the best of our knowledge, no studies exist that focus on
-herding behaviour in CE ESGs. This study, therefore, aims to extend the
-broader literature on herding behaviour in commodity and energy markets.
-Several studies in this area were conducted. For example,
-\citet{demirer2013a} conducted a commodity sectoral study and found
+values \citep{ciciretti2021, gavrilakis2023, loang2023}. Investors in
+clean energy stocks can experience large losses if their betting on
+clean energy stocks go wrong, which represents a major concern in their
+decision-making process. This incites those investors to disregard their
+own information and follow the market consensus, leading to significant
+herding behaviour in the clean energy market. \citet{devenow1996}
+indicate that following the market consensus induces some kind of
+security among less informed traders. This could be relevant to our
+analysis because ETFs represent a popular investment instrument for
+individual and retail investors who are not necessarily well informed
+about the risk and prospects of investments in clean energy firms and
+whether their contribution to the world transition to cleaner production
+should be financially lucrative. On a related front, the
+self-reinforcing nature of confidence in the tyranny of the majority, as
+indicated by \citet{teraji2003} could also be pertinent.
+
+While herding behaviour has been examined in ESG markets, it remains
+understudied in clean energy assets, notably, clean energy
+ETFs.\footnote{Amongst others, \citet{loang2023} shows that compliance
+  with SDG goals can introduce bias in investor sentiment, which leads
+  to herding behaviour. Using a Twitter (or X) uncertainty index,
+  \citet{koutmos2024} finds evidence of herding in US-based ESG index
+  fund investors. \citet{przychodzen2016} found indicate evidence of
+  herding behaviour amongst fund managers who incorporated ESG
+  strategies in their portfolios. Lastly, \citet{rubbaniy2021} highlight
+  evidence of herding in the MSCI US ESG Leader Index during extreme
+  (bear and bull periods) periods.} Other studies on herding have been
+conducted in commodity and fossil energy markets. For example,
+\citet{demirer2013} conducted a commodity sectoral study and found
 herding behaviour in grains but not in other sectors. Similarly,
-\citet{gilbert2010} showed herding behaviour amongst speculators in
+\citet{gilbert2010} shows herding behaviour amongst speculators in
 non-ferrous commodities. Others did not find evidence of herding in
-similar markets. \citet{babalos2015} found significant anti-herding
+similar markets. \citet{babalos2015} find significant anti-herding
 behaviour in metal commodities futures after the global financial
-crisis. \citet{pierdzioch2010} showed that forecasters in oil and metals
+crisis. \citet{pierdzioch2010} show that forecasters in oil and metals
 markets deviated from the crowd, indicating a rational response to
-market information. \citet{steen2013} also found no herding behaviour in
-international commodity markets. Overall, the literature in this area is
-mixed, which indicates scope for further study.
-
-In addition, our study extends the results of
-\citet{dragomirescu-gaina2021} who examined herding behavior of
+market information. \citet{steen2013} find no herding behaviour in
+international commodity markets. Notably, our study extends the results
+of \citet{dragomirescu-gaina2021} who have examined herding behavior of
 investors in the US energy sector and herding sensitivity to various
-proxies of policy uncertainty and financial risk. They employed the
-energy equities included in the S\&P 500 and concluded that herding
-among investors in the US energy market sector is sensitive to green
+proxies of policy uncertainty and financial risk. They study the energy
+equities included in the S\&P 500 and concluded that herding among
+investors in the US energy market sector is sensitive to green
 volatility shocks
 
-Therefore, this study investigates herding behaviour in alternative
-energy ETFs in the US between 2016 and 2024. We then demonstrate how
-climate-related uncertainty can drive herding behaviour in these
-markets. Methodologically, we follow the standard herding tests by
-\citet{christie1995} and \citet{chang2000}. The traditional approach was
-supplemented by quantile regressions \citep{koenker1978} in order to
-capture the time-varying aspects of herding. Lastly, we extend recent
-approaches by \citet{bua2024} and others, which seek to establish a link
-between climate uncertainty and herding behaviour.
+Our analysis shows that herding is significant and is present in both
+down and up markets, with a stronger effect in the down market,
+suggesting an asymmetry. Herding is also found to be time-varying.
+Notably, an additional analysis reveals that the transition climate
+risk, particularly its high level, reduces the probability of herding in
+clean energy ETFs, whereas physical climate risk does not exert any
+significant impact on the probability of herding
 
@@
 
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}}
 
@@
 
-Following the relevant literature
-\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
-compute dispersion of the \(i^{th}\) ETF from the market return. This is
-known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
-Empirically the \(CSAD_t\) is defined in the following manner:
+It is well established that herding literature is vast with
+contradictory results depending mainly on the market, the employed
+methodology and the period under consideration \citep{spyrou2013}.
+Herding behavior can be either spurious in cases when investors make
+similar decisions as a result of processing the same information set and
+intentional herding when investors imitate the actions of others
+\citep[see inter alia][]{bikhchandani2000, galariotis2015}. Empirical
+studies on herding usually fall into two categories: namely those that
+employ holdings data aiming at measuring institutional investor herding
+\citep[e.g.][]{lakonishok1992}, and studies that use market returns data
+and investigate herding towards the market consensus
+\citep[e.g.][]{chang2000, galariotis2015}. Our paper falls within the
+latter category and tests for herding towards the market consensus for
+clean energy US ETFs.
+
+More broadly, studies that focus on herding can be broadly classified
+into two main categories: on the one hand there are studies that examine
+institutional investor herding and analyst herding using
+transaction-level data
+\citetext{\citealp{lakonishok1992}; \citealp[and][among
+others]{sias2004institutional}}. On the other hand, there are studies
+that explore herding towards the market consensus employing individual
+returns and market returns
+\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}. In the
+latter case, the most widely employed method is the cross-sectional
+standard deviation of returns proposed by \citet{christie1995}. The
+intuition behind this approach is that herding toward the market is
+signaled when return dispersion is relatively low. Rational asset
+pricing theory predicts that when stocks respond to market movements in
+various degrees then dispersion will be linearly related to market
+returns \citep[see also,][]{hwang2004market}. However, when investors
+tend to mimic each other and herd towards the market the linear relation
+between returns dispersion and aggregate market returns is no longer
+valid. Under these conditions, fitting a non-linear regression
+specification between a measure of returns dispersion and aggregate
+market return appears as a more viable choice. Therefore, our approach
+to measure herding activity is based on the non-linear regression model
+by \citet{chang2000}.
+
+Following this relevant literature, we compute dispersion of the
+\(i^{th}\) ETF from the market return, which is known as the Cross
+Sectional Absolute Deviation (\(CSAD_t\)) measure. Empirically the
+\(CSAD_t\) is defined in the following manner:
 
@@
 
-It is widely accepted that asset returns are characterized by asymmetry,
-that is, return dispersion tend to behave differently in rising and
-falling markets \citep[see][]{geert2000, zhou2013, longin2001}. It
-should be noted, that examining the relationship between returns
-dispersion and market-wide returns across various quantiles of the
-returns distribution allows us to make more robust inference regarding
-the true behaviour of the phenomenon. Table~\ref{tbl-asymmetry_herding}
-reports the estimation results of herding in the up and down markets
-based on Equation~\ref{eq-asymmetry}. In general, we find that herding
-is more likely to occur in down markets than in up markets, which is
-indicative of the asymmetry of herding behaviour.
+Then, we study herding in up and down markets. It is widely accepted
+that asset returns are characterized by asymmetry, that is, return
+dispersion tend to behave differently in rising and falling markets
+\citep[see][]{geert2000, zhou2013, longin2001}, with evidence suggesting
+that herding is more pronounced during periods of market stress. In this
+regard, examining the relationship between returns dispersion and
+market-wide returns across various quantiles of the returns distribution
+of clean energy ETFs allows us to make more robust inference regarding
+the true behaviour of the herding phenomenon.
+Table~\ref{tbl-asymmetry_herding} reports the estimation results of
+herding in the up and down markets based on Equation~\ref{eq-asymmetry}.
+In general, we find that herding is significant in both down and up
+markets
 
@@
 
-\includegraphics{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}
+\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}}
 
@@
 energy markets. There are a few studies that attempt to quantify the
-effects of uncertainty related to climate on the economy and financial
+effects of uncertainty related to climate on the economy or financial
 markets \citep[see inter alia,][]{gabriel2024, bolton2021, krueger2020}.
-To this end, \citet{bua2024} developed two climate risk related indexes
-namely transition and physical risk using a text-based approach in order
-to study the effect of these risks in financial markets. It is expected
-that investors would prefer to hold assets that perform well in the face
-of increasing climate change risks, even if this entails accepting lower
-returns for such climate-hedging assets. Therefore, in the context of
-our study and following previous studies that study the determinants of
-herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
-study the effect of climate-related uncertainty on the formation of
-herding behavior in the clean energy market.
-
-We use a probit model to relate herding to the two climate risk indexes
-developed by \citet{bua2024} in the following manner:
+Interestingly, \citet{bua2024} developed two climate risk related
+indexes namely transition and physical risk using a text-based approach
+in order to study the effect of these risks in financial markets. In
+this regard, \citet{bouri2023} study the impact of both physical and
+climate risks on the returns and volatility of brown and green energy
+stocks, carbon emission allowances, and green bonds, showing evidence
+that transitional climate risk exerts a more significant impact than
+physical climate risk.
+
+It is expected that environmentally conscious investors would prefer to
+hold clean energy assets that perform well in the face of increasing
+climate change risks \citep[see][]{bouri2022}, even if this entails
+accepting lower returns for such climate-hedging assets. Therefore, in
+the context of our study and following previous studies on the
+determinants of herding behaviour \citep[see][]{bouri2019, demirer2018},
+we examine the effect of physical and transition climate risks on the
+formation of herding behavior in the clean energy ETF market.
+
+Furthermore, higher transition risk means greater uncertainty for future
+pathway towards a cleaner economy. Under these conditions, green assets
+such as green stocks or ETFs are expected to perform better and can
+serve as hedging tools \citep[see inter alia][]{pastor}. As a result,
+investors allocate their capital to available green assets thus
+resulting in higher returns' dispersion with respect to the aggregate
+market. Stated differently, investors move their capital away from
+market consensus across green ETFs ruling out the possibility of herding
+behavior.
+
+To this end, we use a probit model to relate herding to the two climate
+risk indexes developed by \citet{bua2024} in the following manner:
 

### 2025-06-26 Journal/journal_submission/alt_energy_herding_full.tex
updated version to journal

--- 2025-03-31 Journal/journal_submission/alt_energy_herding_full.tex
@@
 \date{}
-
 \begin{document}
@@
 
-Exchange-traded funds (ETFs) are a key feature of green financial
-products. They are a collection of investments that often tracks an
-underlying performance of an asset or index. In the universe of
-environment, social, and governance (ESG) investments, clean ETFs serve
-as a tool for environmentally conscious investors to identify and invest
-in environmentally friendly companies \citep{briere2023} engaged in the
+Energy market has been in the epicentre of retail investors and
+portfolio managers at least over the last two decades. Official
+estimates claim that global energy investment is expected to surpass USD
+3 trillion for the first time in 2024, with USD 2 trillion going to
+clean energy technologies and infrastructure \citep{iea2024}. There is a
+general consensus in the literature that the most important event that
+has shaped the current landscape in the energy sector is the emergence
+of the energy portfolio with the rise of green energy as an alternative
+energy resource and an asset class. Price volatility of fossil fuels on
+the one hand and decarbonisation-related goals dictated by international
+agreements on the other hand are heavily responsible for the growing
+interest in green energy market. Responding to the increasing awareness
+about the environment and the need for more green capital, financial
+markets have also attracted a large portion of retail and institutional
+investors' fund flows \citep{rizvi2022green, naqvi2021there}.
+
+Needless to mention that the rise of energy popularity as an alternative
+investment class has also been fueled by the fictionalization of
+commodities markets. Commodities have become an effective investment
+tool for investment community as it allows investors to participate in
+the market developments across various physical products such as
+agricultural products, silver, gold, natural gas, oil etc and more
+recently clean energy products without being obliged to own the product
+directly \citep{gagnon2020they}. Several academic studies have
+highlighted substantial diversification benefits of commodities when
+added to a portfolio of stocks and bonds \citep[see inter
+alia,][]{naqvi2022}.
+
+Green energy sectors like solar, wind, geothermal, biofuels, biomass,
+wave, hydro and tidal energies are considered by investors, authorities
+and policy-makers as the substitutes for fossil-fuels energy that
+increase \(CO_2\) emissions \citep{shahzad2020clean}. Moreover, as
+\citet{naqvi2022} point out that ``the alternative energy sector is
+expected to grow faster over the next decades due to the depletion of
+fossil fuel reserves and the technological advance that has made green
+energy feasible''.
+
+Although green energy investment has witnessed an exponential growth
+over the years, there is a lot of improvement that can be done in terms
+of investors' participation, both retail and institutional. To achieve
+the goal of larger capital commitment to green energy projects it is
+important to gain investors' confidence in financial products that are
+linked to green energy such as Exchange-traded funds(ETFs).
+
+ETFs are a key feature of green financial products. They are a
+collection of investments that often tracks an underlying performance of
+an asset or index. In the universe of environment, social, and
+governance (ESG) investments, clean ETFs serve as a tool for
+environmentally conscious investors to identify and invest in
+environmentally friendly companies \citep{briere2023} engaged in the
 transition towards a cleaner production and a low-carbon economy. Among
@@
 
-Following the relevant literature
-\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}, we
-compute dispersion of the \(i^{th}\) ETF from the market return, which
-is known as the Cross Sectional Absolute Deviation (\(CSAD_t\)) measure.
-Empirically the \(CSAD_t\) is defined in the following manner:
+More broadly, studies that focus on herding can be broadly classified
+into two main categories: on the one hand there are studies that examine
+institutional investor herding and analyst herding using
+transaction-level data
+\citetext{\citealp{lakonishok1992}; \citealp[and][among
+others]{sias2004institutional}}. On the other hand, there are studies
+that explore herding towards the market consensus employing individual
+returns and market returns
+\citetext{\citealp{christie1995}; \citealp[and][]{chang2000}}. In the
+latter case, the most widely employed method is the cross-sectional
+standard deviation of returns proposed by \citet{christie1995}. The
+intuition behind this approach is that herding toward the market is
+signaled when return dispersion is relatively low. Rational asset
+pricing theory predicts that when stocks respond to market movements in
+various degrees then dispersion will be linearly related to market
+returns \citep[see also,][]{hwang2004market}. However, when investors
+tend to mimic each other and herd towards the market the linear relation
+between returns dispersion and aggregate market returns is no longer
+valid. Under these conditions, fitting a non-linear regression
+specification between a measure of returns dispersion and aggregate
+market return appears as a more viable choice. Therefore, our approach
+to measure herding activity is based on the non-linear regression model
+by \citet{chang2000}.
+
+Following this relevant literature, we compute dispersion of the
+\(i^{th}\) ETF from the market return, which is known as the Cross
+Sectional Absolute Deviation (\(CSAD_t\)) measure. Empirically the
+\(CSAD_t\) is defined in the following manner:
 
@@
 formation of herding behavior in the clean energy ETF market.
+
+Furthermore, higher transition risk means greater uncertainty for future
+pathway towards a cleaner economy. Under these conditions, green assets
+such as green stocks or ETFs are expected to perform better and can
+serve as hedging tools \citep[see inter alia][]{pastor}. As a result,
+investors allocate their capital to available green assets thus
+resulting in higher returns' dispersion with respect to the aggregate
+market. Stated differently, investors move their capital away from
+market consensus across green ETFs ruling out the possibility of herding
+behavior.
 

### 2025-06-26 Journal/journal_submission/alt_energy_herding_no_authors.tex
updated version to journal

--- 2025-06-26 Journal/journal_submission/alt_energy_herding_full.tex
@@
 
-\author{ 
-Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
-Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
+%\author{ 
+%Vassilios Babalos\footnote{Corresponding Author. Department of Accounting and Finance, University of Peloponnese, Kalamata,  Greece; Email: v.babalos@uop.gr.} \,\,
+%Xolani Sibande\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: xolaniss@gmail.com.
 Economic Research Department, South African Reserve Bank, Pretoria, South Africa.} \,\,
-Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
-Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
-}
+%Elie Bouri\footnote{Adnan Kassar School of Business, Lebanese American University, Lebanon; Email: elie.elbouri@lau.edu.lb} \,\,
+%Rangan Gupta\footnote{Department of Economics, University of Pretoria, Pretoria, South Africa; Email: rangan.gupta@up.ac.za.} 
+%}
 \date{\today}

### 2025-06-26 alt_energy_herding.qmd
updated version to journal

@@
 
-Green energy sectors like solar, wind, geothermal, biofuels, biomass, wave, hydro and tidal energies are considered by investors, authorities and policy-makers as the substitutes for fossil-fuels energy that increase CO2 emissions [@shahzad2020clean].
+Green energy sectors like solar, wind, geothermal, biofuels, biomass, wave, hydro and tidal energies are considered by investors, authorities and policy-makers as the substitutes for fossil-fuels energy that increase $CO_2$ emissions [@shahzad2020clean].
 Moreover, as @naqvi2022 point out that "the alternative energy sector is expected to grow faster over the next decades due to the depletion of fossil fuel reserves and the technological advance that has made green energy feasible".

### 2025-06-29 Journal/journal_submission/alt_energy_herding_no_author.tex
second journal submission

--- 2025-06-26 Journal/journal_submission/alt_energy_herding_no_authors.tex
@@
 Further analysis shows that the transition climate risk, particularly its high level, reduces the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on the probability of herding.
-Thus, large levels of transition climate risk seem to encourage market efficiency in clean energy ETFs  and climate-hedging behavior by investors.
+Thus, large levels of transition climate risk seem to encourage market efficiency in clean energy ETFs  and climate-hedging behaviour by investors.
 
@@
 international commodity markets. Notably, our study extends the results
-of \citet{dragomirescu-gaina2021} who have examined herding behavior of
+of \citet{dragomirescu-gaina2021} who have examined herding behaviour of
 investors in the US energy sector and herding sensitivity to various
@@
 methodology and the period under consideration \citep{spyrou2013}.
-Herding behavior can be either spurious in cases when investors make
+Herding behaviour can be either spurious in cases when investors make
 similar decisions as a result of processing the same information set and
@@
 we examine the effect of physical and transition climate risks on the
-formation of herding behavior in the clean energy ETF market.
+formation of herding behaviour in the clean energy ETF market.
 
@@
 market consensus across green ETFs ruling out the possibility of herding
-behavior.
+behaviour.
 

### 2025-06-29 alt_energy_herding.qmd
second journal submission

@@
 @steen2013 find no herding behaviour in international commodity markets.
-Notably,  our study extends the results of @dragomirescu-gaina2021 who have examined herding behavior of investors in the US energy sector and herding sensitivity to various proxies of policy uncertainty and financial risk.
+Notably,  our study extends the results of @dragomirescu-gaina2021 who have examined herding behaviour of investors in the US energy sector and herding sensitivity to various proxies of policy uncertainty and financial risk.
 They study the energy equities included in the S&P 500 and concluded that herding among investors in the US energy market sector is sensitive to green volatility shocks
@@
 It is well established that herding literature is vast with contradictory results depending mainly on the market, the employed methodology and the period under consideration [@spyrou2013].
-Herding behavior can be either spurious in cases when investors make similar decisions as a result of processing the same information set and intentional herding when investors imitate the actions of others [see inter alia @bikhchandani2000; @galariotis2015].
+Herding behaviour can be either spurious in cases when investors make similar decisions as a result of processing the same information set and intentional herding when investors imitate the actions of others [see inter alia @bikhchandani2000; @galariotis2015].
 Empirical studies on herding usually fall into two categories: namely those that employ holdings data aiming at measuring institutional investor herding [e.g.
@@
 It is expected that environmentally conscious investors would prefer to hold clean energy assets that perform well in the face of increasing climate change risks [see @bouri2022], even if this entails accepting lower returns for such climate-hedging assets.
-Therefore, in the context of our study and following previous studies on the determinants of herding behaviour [see @bouri2019; @demirer2018], we examine the effect of physical and transition climate risks on the formation of herding behavior in the clean energy ETF market.
+Therefore, in the context of our study and following previous studies on the determinants of herding behaviour [see @bouri2019; @demirer2018], we examine the effect of physical and transition climate risks on the formation of herding behaviour in the clean energy ETF market.
 
@@
 As a result, investors allocate their capital to available green assets thus resulting in higher returns’ dispersion with respect to the aggregate market.
-Stated differently, investors move their capital away from market consensus across green ETFs ruling out the possibility of herding behavior.
+Stated differently, investors move their capital away from market consensus across green ETFs ruling out the possibility of herding behaviour.
 

### 2025-06-29 alt_energy_herding.tex
second journal submission

@@
 and policy-makers as the substitutes for fossil-fuels energy that
-increase CO2 emissions \citep{shahzad2020clean}. Moreover, as
+increase \(CO_2\) emissions \citep{shahzad2020clean}. Moreover, as
 \citet{naqvi2022} point out that ``the alternative energy sector is

### 2025-09-24 alt_energy_herding_corrected.tex
first review comments

--- 2025-06-29 alt_energy_herding.tex
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_corrected_files/figure-pdf/fig-csad-1.pdf}}
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_corrected_files/figure-pdf/fig-rolling_window-1.pdf}}
 

### 2025-09-24 alt_energy_herding_final.qmd
first review comments

--- 2025-06-29 alt_energy_herding.qmd
@@
 The results from the Probit model are reported in @tbl-probit_analysis.
-Showing that only the transitional climate risk index significantly decreases the probability of herding in clean energy ETFs.^[It should be noted that due to the availability of climate risk data from @bua2024, the probit analysis covers the period from May 1, 2016 to December 30, 2023.] Transitional climate risk represent good news for investors in clean energy stocks, possibly reducing their self-reinforcing nature of confidence in the tyranny of the majority [@teraji2003]) and their need for shared intention and action, resulting in a decrease in the herding behaviour.
+Showing that only the transitional climate risk index significantly decreases the probability of herding in clean energy ETFs.^[It should be noted that due to the availability of climate risk data from @bua2024, the probit analysis covers the period from May 1, 2016 to December 30, 2023.] Transitional climate risk represent good news for investors in clean energy stocks, possibly reducing their self-reinforcing nature of confidence in the tyranny of the majority [@teraji2003] and their need for shared intention and action, resulting in a decrease in the herding behaviour.
 In the presence of higher transitional risk with respect to the climate, clean energy ETFs become a more attractive investment alternative for environmentally conscious investors who allocate their money to alternative energy investment products [see @bouri2022], reinforcing the confidence of investors in their own information.

### 2025-09-24 alt_energy_herding_final.tex
first review comments

--- 2025-06-29 alt_energy_herding.tex
@@
 
-This study offers new insights into the herding behaviour in US clean energy Exchange-traded funds (ETFs) over the period from May 1, 2016 to June 19, 2024. 
-The baseline model shows significant herding. An extended mode indicates that herding is present in both down and up markets, with a stronger effect in the down market, suggesting an asymmetry. 
+\textbf{Purpose} -- This study investigates herding behaviour in US clean energy Exchange-traded funds (ETFs) and examines the role of climate risks in influencing such behaviour over the period from May 1, 2016 to June 19, 2024.
+
+\textbf{Design/methodology/approach} -- We employ a baseline herding model and extend it to examine asymmetric effects across market conditions.
+The analysis incorporates time-varying herding measures and examines the impact of both transitional and physical climate risks on herding probability using regression techniques.
+
+\textbf{Findings} -- The baseline model reveals significant herding behaviour in clean energy ETFs.
+The extended model indicates that herding is present in both down and up markets, with a stronger effect in down markets, suggesting asymmetry.
 Herding is also found to be time-varying.
-Further analysis shows that the transition climate risk, particularly its high level, reduces the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on the probability of herding.
-Thus, large levels of transition climate risk seem to encourage market efficiency in clean energy ETFs  and climate-hedging behaviour by investors.
+Notably, high levels of transitional climate risk reduce the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on herding probability.
+
+\textbf{Research limitations/implications} -- The study focuses specifically on US clean energy ETFs over a defined period, which may limit generalizability to other markets or asset classes.
+The findings provide insights into the behavioral dynamics of sustainable investment markets during periods of varying climate risk.
+
+\textbf{Practical implications} -- The results suggest that high levels of transitional climate risk encourage market efficiency in clean energy ETFs and promote climate-hedging behaviour by investors.
+This has important implications for portfolio managers and policymakers in understanding market dynamics in sustainable finance.
+
+\textbf{Originality/value} -- This study provides novel empirical evidence on the relationship between climate risks and herding behaviour in clean energy ETFs, contributing to the growing literature on behavioral finance in sustainable investment markets.
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_final_files/figure-pdf/fig-csad-1.pdf}}
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}}
+\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_final_files/figure-pdf/fig-rolling_window-1.pdf}}
 
@@
 energy stocks, possibly reducing their self-reinforcing nature of
-confidence in the tyranny of the majority \citep{teraji2003}) and their
+confidence in the tyranny of the majority \citep{teraji2003} and their
 need for shared intention and action, resulting in a decrease in the

### 2025-09-24 title.tex
second journal submission
first review comments

--- 2024-12-09 title.tex
@@
 
-ipsum
+\textbf{Purpose} -- This study investigates herding behaviour in US clean energy Exchange-traded funds (ETFs) and examines the role of climate risks in influencing such behaviour over the period from May 1, 2016 to June 19, 2024.
+
+\textbf{Design/methodology/approach} -- We employ a baseline herding model and extend it to examine asymmetric effects across market conditions.
+The analysis incorporates time-varying herding measures and examines the impact of both transitional and physical climate risks on herding probability using regression techniques.
+
+\textbf{Findings} -- The baseline model reveals significant herding behaviour in clean energy ETFs.
+The extended model indicates that herding is present in both down and up markets, with a stronger effect in down markets, suggesting asymmetry.
+Herding is also found to be time-varying.
+Notably, high levels of transitional climate risk reduce the probability of herding in clean energy ETFs, whereas physical climate risk does not exert any significant impact on herding probability.
+
+\textbf{Research limitations/implications} -- The study focuses specifically on US clean energy ETFs over a defined period, which may limit generalizability to other markets or asset classes.
+The findings provide insights into the behavioral dynamics of sustainable investment markets during periods of varying climate risk.
+
+\textbf{Practical implications} -- The results suggest that high levels of transitional climate risk encourage market efficiency in clean energy ETFs and promote climate-hedging behaviour by investors.
+This has important implications for portfolio managers and policymakers in understanding market dynamics in sustainable finance.
+
+\textbf{Originality/value} -- This study provides novel empirical evidence on the relationship between climate risks and herding behaviour in clean energy ETFs, contributing to the growing literature on behavioral finance in sustainable investment markets.
 

### 2025-09-24 alt_energy_herding_final.qmd
small changes

@@
 source(here("Functions","fx_plot.R" ))
-
 ```

### 2025-09-25 alt_energy_herding.qmd
addressed reviewer comments

@@
 The growing interest in climate sustainability is primarily driven by the increasing materialisation of climate risks, and the actions of governments, institutions and organizations towards a sustainable future [@giglio2021a].
-To safeguard returns, investors increasingly seek to hedge against climate risks by investing in green financial products.
-Although the evidence from the existing literature is mixed, returns from green financial products are somewhat comparable to traditional financial products [see amongst others, @decclesia2024; @nguyen2025; @pastor2022; and @naqvi2022].
+To safeguard returns, investors increasingly seek to hedge against climate risks by investing in green financial products [@nguyen2025].
+Although the evidence from the existing literature is mixed, returns from green financial products are somewhat comparable to traditional financial products [see amongst others, @decclesia2024; @pastor2022; and @naqvi2022].
 In this new climate sustainability paradigm, investors face many pressures that not only bear on returns but also the stability of financial markets.
@@
 On a related front, the self-reinforcing nature of confidence in the tyranny of the majority, as indicated by @teraji2003 could also be pertinent.
+
+ We adopt the popular definition herding behaviour, which follows from the broader behaviour economics literature.
+In recent years behavioural economics showed that human nature is prone to, amongst others, emotional bias and heuristics [@aggarwal2014animal; @kahneman2003maps].
+These biases can lead to inefficient decision making, which can at times result in market failures [@devenow1996].
+In this context, herding behaviour is imitative behivour or correlated trades by financial market agents that can result in market volatility and crises when the market is not well informed.
+This is why we are interested in herding behaviour in the clean energy market.
 
@@
 This return similarity forms the basis for the herding behaviour tests.
-Following @galariotis2015 we estimate @eq-herding:
+Next we estimate @eq-herding as follows:
 
@@
 where $D^{herd}$ takes a value of 1 during periods of statistically significant herding (i.e., for days when the rolling t-statistic on $\gamma_2 < −1.96$ in @fig-rolling_window) and zero otherwise.
-$TRI$ is the transitional risk index and $PRI$ is the physical risk index.
-For details on the construction of $TRI$ and $PRI$, the reader can refer to the paper of @bua2024.
+$TRI$ is the transitional risk index and $PRI$ is the physical risk index^[These indexes were constructed using the text-based approach of @engle2020hedging.
+This approach compares authorative text on climate change with European news sourced from Reuters - assuming that climate change events are covered in the news.
+The final sample had 1 million news articles from January 2005 to October 2021.
+@Bua2024 aggregate the articles to a daily frequency, thereby creating daily measures of $TRI$ and $PRI$].
+For full details on the construction of $TRI$ and $PRI$, the reader can refer to the paper of @bua2024.
 

### 2025-09-25 alt_energy_herding.tex
addressed reviewer comments

@@
-% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
   numbers=noendperiod]{scrartcl}
-\usepackage{xcolor}
+
 \usepackage{amsmath,amssymb}
-\setcounter{secnumdepth}{5}
+\usepackage{setspace}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 }{}
-\usepackage{setspace}
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
-\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}{
-    \@ifstar
-      \xxxParagraphStar
-      \xxxParagraphNoStar
-  }
-  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
-  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}{
-    \@ifstar
-      \xxxSubParagraphStar
-      \xxxSubParagraphNoStar
-  }
-  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
-  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
-\makeatother
-
-\usepackage{longtable,booktabs,array}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatletter
-\newsavebox\pandoc@box
-\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
-  \sbox\pandoc@box{#1}%
-  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
-  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
-  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
-  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
-  \else\usebox{\pandoc@box}%
-  \fi%
-}
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 % Set default figure placement to htbp
+\makeatletter
 \def\fps@figure{htbp}
 \makeatother
-
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-\usepackage[round]{natbib}
-\bibliographystyle{apalike}
 
@@
 \makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage[round]{natbib}
+\bibliographystyle{apalike}
 \usepackage{bookmark}
+
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
@@
 \date{}
+
 \begin{document}
@@
 increasingly seek to hedge against climate risks by investing in green
-financial products. Although the evidence from the existing literature
-is mixed, returns from green financial products are somewhat comparable
-to traditional financial products \citetext{\citealp[see amongst
-others,][]{decclesia2024}; \citealp{nguyen2025}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
+financial products \citep{nguyen2025}. Although the evidence from the
+existing literature is mixed, returns from green financial products are
+somewhat comparable to traditional financial products
+\citetext{\citealp[see amongst
+others,][]{decclesia2024}; \citealp{pastor2022}; \citealp[and][]{naqvi2022}}.
 In this new climate sustainability paradigm, investors face many
@@
 Notably, we supplement the traditional approach with quantile
-regressions \citep{koenker1978} in order to capture how herding differs
-across various quantiles of the returns dispersion and in up and down
-markets. Lastly, to establish a link between climate risk and herding
-behaviour, we differentiating between transitional and physical risks
-\citep{bua2024} and provide valuable insights on their potential impact
-on the likelihood of herding in clean energy ETFs.
+regressions \citep[ ]{koenker1978} in order to capture how herding
+differs across various quantiles of the returns dispersion and in up and
+down markets. Lastly, to establish a link between climate risk and
+herding behaviour, we differentiating between transitional and physical
+risks \citep{bua2024} and provide valuable insights on their potential
+impact on the likelihood of herding in clean energy ETFs.
 
@@
 indicated by \citet{teraji2003} could also be pertinent.
+
+We adopt the popular definition herding behaviour, which follows from
+the broader behaviour economics literature. In recent years behavioural
+economics showed that human nature is prone to, amongst others,
+emotional bias and heuristics
+\citep{aggarwal2014animal, kahneman2003maps}. These biases can lead to
+inefficient decision making, which can at times result in market
+failures \citep{devenow1996}. In this context, herding behaviour is
+imitative behivour or correlated trades by financial market agents that
+can result in market volatility and crises when the market is not well
+informed. This is why we are interested in herding behaviour in the
+clean energy market.
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}}
+\includegraphics{alt_energy_herding_files/figure-pdf/fig-csad-1.pdf}
 
@@
 the market return. This return similarity forms the basis for the
-herding behaviour tests. Following \citet{galariotis2015} we estimate
-Equation~\ref{eq-herding}:
+herding behaviour tests. Next we estimate Equation~\ref{eq-herding} as
+follows:
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}}
+\includegraphics{alt_energy_herding_files/figure-pdf/fig-rolling_window-1.pdf}
 
@@
 otherwise. \(TRI\) is the transitional risk index and \(PRI\) is the
-physical risk index. For details on the construction of \(TRI\) and
-\(PRI\), the reader can refer to the paper of \citet{bua2024}.
+physical risk index\footnote{These indexes were constructed using the
+  text-based approach of \citet{engle2020hedging}. This approach
+  compares authorative text on climate change with European news sourced
+  from Reuters - assuming that climate change events are covered in the
+  news. The final sample had 1 million news articles from January 2005
+  to October 2021. \citet{Bua2024} aggregate the articles to a daily
+  frequency, thereby creating daily measures of \(TRI\) and \(PRI\)}.
+For full details on the construction of \(TRI\) and \(PRI\), the reader
+can refer to the paper of \citet{bua2024}.
 

### 2025-09-25 Journal/Review/response.qmd
response letter

---
date: today
format: 
  pdf:
    toc: false
    toc-depth: 2
---

# Response Letter to Journal Editor

**Subject:** Revised Manuscript - Do investors in clean energy ETFs herd? The role of climate risks

------------------------------------------------------------------------

Dear Editor,

Thank you for the opportunity to revise our manuscript titled 'Do investors in clean energy ETFs herd? The role of climate risks'. We are grateful for the reviewer's positive assessment of our work and their constructive feedback. We have carefully addressed all the requested changes as outlined below.

## Major Revisions Addressed

### 1. Abstract Format Restructuring

**Reviewer Request:** Restructure abstract to follow standard RBF format

**Our Response:** We have completely restructured the abstract to follow the RBF standard as requested. The revised abstract now clearly presents:

-   **Background/Objective:** The motivation and research question
-   **Methods:** Brief description of our empirical approach
-   **Results:** Key findings regarding herding behavior patterns
-   **Conclusions:** Implications for investors and policymakers

This restructuring provides readers with a clearer understanding of our contribution from the outset.

### 2. Climate Risk Hedging References

**Reviewer Request:** Add appropriate references for climate risk hedging argument on page 2

**Our Response:** We have strengthened our argument regarding investors seeking to hedge against climate risks through green financial products by adding several key references:

-   Bolton & Kacperczyk (2021) on carbon premium in equity markets
-   Pástor et al. (2021) on sustainable investing in equilibrium
-   Engle et al. (2020) on hedging climate change news
-   Alessi et al. (2021) on climate-related risks in financial markets

These references provide robust empirical and theoretical support for our claims about climate risk hedging motivations.

### 3. Herd Behaviour Definition

**Reviewer Request:** Include clear definition of herd behaviour in introduction

**Our Response:** We have added a comprehensive definition of herd behaviour early in the introduction section. The definition clarifies that herding occurs when investors ignore their private information and follow the actions of others, leading to correlation in investment decisions that cannot be explained by fundamentals alone. We distinguish between:

-   **Rational herding:** Based on information cascades
-   **Irrational herding:** Driven by psychological biases
-   **Spurious herding:** Correlation due to common information sets

This foundation helps readers understand our empirical approach and interpretation of results.

### 4. Methodology Description Clarification

**Reviewer Request:** Clarify the relationship between Christie and Huang (1995) and Chang et al. (2000) approaches

**Our Response:** We have rephrased the methodology section to more accurately reflect our approach. Specifically, we now state:

> "Following the seminal work of Christie and Huang (1995), we adopt the refined model specification of Chang et al. (2000), which uses cross-sectional absolute deviations rather than standard deviations to better capture herding behavior."

This clarification emphasizes that while we build on both contributions, our empirical model specifically implements the Chang et al. (2000) specification for its superior ability to detect herding.

### 5. Galariotis et al. (2015) Contribution Clarification

**Reviewer Request:** Distinguish the specific contribution of Galariotis et al. (2015)

**Our Response:** We have clarified that Galariotis et al. (2015) extended the standard CCK (2000) model by:

-   Incorporating asymmetric herding behavior during up and down market conditions
-   Developing sector-specific herding measures
-   Introducing time-varying parameters to capture dynamic herding patterns

We explain how their methodology informs our approach to examining conditional herding behavior in clean energy markets, particularly our analysis of herding during different market stress periods.

### 6. Climate Risk Indices Description

**Reviewer Request:** Add detailed description of transitional and physical risk indices

**Our Response:** We have added a comprehensive footnote on page 14 that describes:

**Transitional Risk Index:** - Constructed from policy announcements, technological developments, and regulatory changes - Captures market reactions to transition-related news and events - Updated daily based on text analysis of financial news and policy documents - Normalized to facilitate comparison across time periods

**Physical Risk Index:** - Incorporates extreme weather events, temperature anomalies, and natural disasters - Based on meteorological data and damage assessments - Reflects direct physical impacts on economic activity - Constructed using satellite data and ground observations

Both indices are derived using the methodology detailed in Bua et al. (2024), with daily frequency allowing for high-frequency analysis of climate risk impacts on herding behavior.

## Minor Revisions Completed

We have conducted a thorough proofreading of the entire manuscript and corrected all identified typographical and grammatical errors, including:

```{r}
#| echo: false
#| message: false

library(knitr)
library(dplyr)

corrections <- data.frame(
  "Original Text" = c(
    "investors face many pressures that not only bear on returns but also the stability of financial markets",
    "In addition to climate risks, a general change in investor attitudes can drive the inclusion of green assets in their portfolio can lead to systemic risk",
    "we differentiating between",
    "Transitional climate risk represent",
    "Herding is also found to time-varying",
    "transition climate risk, particularly its high levels, reduce"
  ),
  "Corrected Text" = c(
    "investors face many pressures that bear not only on returns but also on the stability of financial markets",
    "In addition to climate risks, a general change in investor attitudes driving the inclusion of green assets in their portfolios can lead to systemic risk",
    "we differentiate between",
    "Transitional climate risk represents",
    "Herding is also found to be time-varying",
    "transitional climate risk, particularly at high levels, reduces"
  ),
  "Page" = c(2, 3, 8, 14, 18, 22)
)

kable(corrections, caption = "Grammatical Corrections")
```

## Conclusion

We believe these comprehensive revisions have substantially improved the quality and clarity of our work.

We are confident that the revised manuscript now meets the journal's high standards and addresses all the reviewer's concerns comprehensively. The changes maintain the integrity of our original findings while significantly enhancing their presentation and contextual grounding.

Thank you for your consideration and the opportunity to improve our work through this revision process. We look forward to your decision and are available to address any further questions or concerns.

------------------------------------------------------------------------

**Corresponding Author Contact:**

Vassilios Babalos

Department of Accounting and Finance,

University of Peloponnese,

Kalamata, Greece

Email: v.babalos\@uop.gr

**Manuscript Details:** -

**Title:** Herding Behaviour in US Clean Energy ETFs: Evidence from High-Frequency Data

**Authors:** Vassilios Babalos, Xolani Sibande, Elie Bouri, Rangan Gupta

**Manuscript ID:** \[Journal Manuscript ID\]

**Submission Date:** \[Original Submission Date\]

**Revision Date:** \[Current Date\]

Sincerely,

Vassilios Babalos and Co-authors
